### 2016-02-23 paper.tex
adding previous work

\title{Decentralised location proof system}

\documentclass[12pt]{article}

\begin{document}
\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}

\section{Previous work}
Location proof systems are expected to be accurate and tamper-proof. For this reason, existing solutions have chosen to use a central authority to issue proofs \cite{brassil, luo, khan}.

Hardware techniques \cite{brassil} operate by supplementing existing WiFi access points with \textit{femtocells} (small cellular antennae that connect to the mobile carrier via the Internet). Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data via Wi-Fi. This solution requires investment in additional hardware to supplement existing WiFi access points. It also requires access to mobile providers user database to identify users locations.

Other proof systems \cite{luo} deploy software on Wi-Fi access points. Access points taking part in the location proof network become part of a 'group' with a shared group signature. Mobile nodes can request a location proof from an access point, who signs it with the group signature. Access points provide location proofs to nodes without ever learning the node's identity, thus protecting user's privacy. However, due to the system’s reliance on the group signature structure, access points become a target for attack. Compromising an access point would allow an attacker to create false location proofs.

\cite{luo} considers a number of threats in their architecture:
\begin{itemize}
	\item \textbf{Dishonest users.} A dishonest user tries to obtain location proofs that certify her presence at some place at a particular time even if she was not there. Dishonest users may achieve this goal by colluding with malicious intruders.
	\item \textbf{Malicious intruders.} A malicious intruder is not interested in obtaining location proofs for her own use but offers to help other users to get location proofs on their behalf in exchange for other benefits like money.
	\item \textbf{Curious APs and applications.} A curious AP tries to learn a user’s identity while the user is acquiring a location proof from the AP. Similarly, a curious application tries to learn more location information from a location proof than it really needs.
	\item \textbf{Malicious applications.} A malicious application obtains location proofs from its users and then tries to take advantage of these proofs to get unauthorised access to other applications.
	\item \textbf{Active and passive eavesdroppers.} An eavesdropper records and maybe modifies communication between users, proof- ssuers, or applications.
\end{itemize}

Distributed P2P location proof systems also exist \cite{khan}. A central authority is used and acts as a certificate authority, issuing a unique ID to each person using the system. Unique identity is proved by users by providing SSN, driver’s licence, or passport documents. This removes the threat of a Sybil attack, but makes the central authority a clear target for attack. The system uses three parties to provide location proofs; a mobile user who requests a proof, a fixed location authority, and a mobile user who acts as a witness. The system becomes vulnerable in the case where all three users collude, but is otherwise quite an interesting approach.

\cite{khan} also outlines a number of possible attacks on their system:
\begin{itemize}
	\item \textbf{False presence:} A malicious user can create a fake location proof on his own, without being physically present at the location. The fake proof is supposed to resemble an actual proof, which the user could have actually collected from a valid location authority.
	\item \textbf{False timestamping (backdating, future dating):} In a backdating attack, the user and the location authority colludes to create a proof for a past time. Conversely, in future dating, the location authority and a user colludes to generate a proof with a future timestamp.
	\item \textbf{Implication:} A location authority and/or a witnesses can falsely accuse a user of his presence at a certain location. In this case, the malicious location authority and witness colludes to generate a false proof of presence for the user.
	\item \textbf{False assertion:} A user can collude with a witness, and generate a falsely asserted location proof. The truth value in such a fake proof is reinstated with the assertion received from the other user.
	\item \textbf{Denial of presence:} A user can visit a location and at a later time, deny his presence at that location. In such a case, the user actually denies the validity of a certain location proof that has been been generated upon his presence at that particular location.
	\item \textbf{Proof switching:} The user is expected to have full access to all storage facilities on his mobile device. Hence, the user utilizes the legitimate proof and manipulates the information to create a false proof for a different location.
	\item \textbf{Relay attack:} A user can use a proxy to relay the requests and collect a location proof. Alternatively, a location authority can maliciously relay assertion requests with the witness not being present at the site.
	\item \textbf{Sybil attack:} A Sybil attack occurs when a single user generates multiple presence and identities [29]. A user can launch a Sybil attack by generating multiple identities representing a user and a witness and provide false endorsements for location proofs.
	\item \textbf{Denial of witness’s presence:} At the time of proof verification, the user can claim the absence of witnesses at the site or falsely claim an assertion to be counterfeit. The user and the location authority may also collude and claim the non-availability of witnesses.
	\item \textbf{Privacy violation:} An attacker may capture an asserted location proof generated for a user, and discover the identity of the user and/or the witness.
\end{itemize}

'OTIT' \cite{otit}, a model for designing secure location provenance, can be used to compare existing location proof systems. This model defines the following requirements necessary for designing any secure location provenance scheme: Chronological, Order Preserving, Vereifiable, Tamper Evident, Privacy Preserved, Selective In-Sequence Privacy, Privacy Protected Chronology, and Convenience \& Derivability.

\section{Results}

\section{Conclusions}

\begin{thebibliography}{9}

\bibitem{brassil}
  J. Brassil, P.K. Manadhata,
  ``Verifying the Location of a Mobile Device User'',
  Proc. of MobiSec 2012,
  June 2012.

\bibitem{luo}
  Luo, W., Hengartner, U.,
  ``Proving your Location without giving up your Privacy'',
  Proceedings of the Eleventh Workshop on Mobile Computing Systems \& Applications,
  HotMobile 2010, Annapolis, Maryland, February 22 - 23, pp. 7–12. ACM,
  New York (2010)

\bibitem{khan}
  R. Khan, S. Zawoad, M. M. Haque, and R. Hasan,
  ```Who, When, and Where?' Location Proof Assertion for Mobile Devices'',
  Proceedings of the 28th Annual IFIP WG 11.3 Working Conference on Data and Applications Security and Privacy, ser. DBSec. IFIP,
  July 2014.

\bibitem{otit}
  Khan, R., Zawoad, S., Haque, M., Hasan, R.
  ``OTIT: Towards secure provenance modeling for location proofs'',
  Proc. of ASIACCS. ACM (2014)

\end{thebibliography}

\end{document}

### 2016-02-23 paper.tex
adding main work on core idea

@@
 Unique identity is proved by users by providing SSN, driver’s licence, or passport documents.
-This removes the threat of a Sybil attack, but makes the central authority a clear target for attack.
+This removes the threat of a Sybil attack \cite{sybil}, but makes the central authority a clear target for attack.
 The system uses three parties to provide location proofs; a mobile user who requests a proof, a fixed location authority, and a mobile user who acts as a witness.
@@
 This model defines the following requirements necessary for designing any secure location provenance scheme: Chronological, Order Preserving, Vereifiable, Tamper Evident, Privacy Preserved, Selective In-Sequence Privacy, Privacy Protected Chronology, and Convenience \& Derivability.
+
+\section{Decentralised location proof system}
+This location proof system is comprised of a network of mobile nodes, capable of anonymously providing and receiving an alibi to/from other nodes on the network.
+
+When two nodes are in close physical proximity, they initiate a transaction with each other over a short range, ad-hoc network such as bluetooth.
+To create this transaction, they must agree on their current GPS coordinates and the current time.
+Once both nodes reach agreement on these parameters, they each create an encrypted transaction that claims their current time and location.
+This transaction must also contain references to both the alibi's identity, and the index of the node’s most recent transaction.
+Both nodes then publish their own transaction, indexed using their identity, onto a public append-only bulletin board/blockchain.
+
+A node can give verifiers permission to verify its location.
+The node will give the verifier access to the keys used to encrypt each of the node’s $n$ most recent transactions.
+After finding and decrypting the transactions, the 3rd party will decide based whether or not to accept the node's claimed location as truth.
+
+\subsection{Identities}
+In order to preserve user's privacy, a user will only ever use an identity for one transaction, before generating a new one.
+This prevents malicious users from watching the public blockchain for a known identity and tracking it.
+However, to prevent identity theft, it is important for the verifier to be able to prove that a node was the original creator of each identity.
+This is achieved using a public/private key pair for each node.
+
+When a node is created, it generates (or is provided with?) a certificate (or key pair).
+To maintain anonymoty, the node will use the public key to encrypt some nonces to create identities, and use these identify itself in a transaction.
+During the verification stage, the node will provide the verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions.
+The verifier calculates the node's identities using the public key and nonces, and retrieves the relevant transactions from the public blockchain.
+The verifier will also ensure that the node owns the private key associated with the provided public key, to prevent identity theft.
+
+\subsection{Transactions}
+During a transaction between two nodes, a number of different items must be shared and calculated.
+The first step in a transaction is for both nodes to agree upon a GPS location and current time.
+Nodes likely won't have the exact same GPS coordinates or time, but once the values don;t differ by more than some constant $\epsilon$, the nodes will continue with the transaction.
+
+After nodes agree upon the parameters of the transaction, they exchange their key packets with each other.
+A key packet is a list of the nodes $m$ most recent identities, along with the keys needed to decrypt them.
+This allows the verifier to check the credibility of each alibi the node seeking verification has collected.
+
+The following transaction data will be published onto the blockchain by node A:
+
+$T_{An} = ID_{An} | K_{A1n}(ID_{An-1}) | K_{A2n}(ts, loc, ID_{An}, ID_{An-1}, KP_{Bm})$
+
+\begin{itemize}
+	\item[] $\mathbf{ID_{An}}$: The current ID of node $A$.
+	\item[] $\mathbf{K_{A1n}(ID_{An-1})}$: Node $A$'s previous identity.
+This creates a backward link between $A$'s transactions, used to preserve the ``privacy protected chronology'' property of OTIT \cite{otit}.
+This is encrypted with a symmetric key $K_{A1n}$ to stop curious users monitoring the blockchain to track other users.
+	\item[] $\mathbf{K_{A2n}}$: Node $A$'s second current symmetric key at transaction $n$, used to encrypt the body of the transaction.
+This is separate from $K_{A1n}$ to preserve ``privacy protected chronology'' and ''selective in-sequence privacy'' \cite{otit}.
+	\item[] $\mathbf{ts}$: The agreed timestamp.
+	\item[] $\mathbf{loc}$: The agreed GPS coordinates.
+	\item[] $\mathbf{ID_{An} and ID_(An-1)}$:  Node $A$'s current identity and most recent identity respectively, encrypted with $K_{An}$.
+These are used to prevent a possible identity theft attack whereby a malicious man-in-the-middle may try to alter the ID attached to the transaction.
+	\item[] $\mathbf{KP_{Bm}}$: Node $B$'s key packet at transaction $m$ (relative to $B$).
+This contains $B$'s $n$ most recent transaction keys, so any verifier that node $A$ requests will be able to validate the credibility of alibi $B$ by decrypting his transactions.
+\end{itemize}
+
+The key packet is more than simply a list of keys that $B$ has used to encrypt his transactions; in order to preserve the ``privacy preserved'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt.
+For this reason, the transaction backwards-chaining may need to be broken.
+For example, if node $B$ doesn't want to reveal transaction $T_{Bm-3}$, he would reveal the following key packet:
+
+$KP_{Bm} = (\{ID_{Bm}, K_{Bm}\}, K_{Bm-1}, K_{Bm-2}, \{ID_{Bm-4}, K_{Bm-4}\}, K_{Bm-5}, \ldots, K_{Bm-n})$
+\\
+\\
+\indent
+In this case, $ID_{Bm-4}$ is needed along with $K_{Bm-4}$ so the verifier knows at which ID the privacy-protected chain will become unprotected, and can be decrypted.
+
+\subsection{Verification}
+The verification stage is the most algorithmically complex part of the system.
+It is performed by the verifier.
+Given the keys for a node's $n$ most recent transactions, the verifier will walk chronologically backwards along the public location proof chain.
+At each transaction encountered, the search will fork along the proof history path of both parties involved in that transaction, and continue until all available transactions have been exhausted.
+
+The goal of the verification stage is to either accept or reject the location that the user is claiming.
+There are a huge number of factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain verifiers, and kept secret to improve reliability.
+Some simple example factors may include:
+\begin{itemize}
+	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, then the node is likely attempting a poorly-constructed Sybil attack, and the verifier will reject his verification request.
+	\item \textbf{Alibi reuse:} if the verifier can prove that alibi’s are being reused frequently, then it will reject the verification request.
+	\begin{itemize}
+		\item Due to transaction anonymity, the verifier may not always be able to tell if two alibi's are the same person or not.
+e.g.
+node $A$ could use node $B$ as an alibi, then wait for $B$ to complete $n$ more transactions, then use node $B$ again.
+		\item This is not a viable attack on the verification system.
+Depending on the size of $n$, enough time may pass between both uses of node $B$ as an alibi that the transactions are no longer relevant.
+	\end{itemize}
+\end{itemize}
+
+\subsection{Sybil attack}
+Currently there is no provably correct way of preventing a Sybil attack, where a single physical node may create multiple \textit{pseudoidentities} \cite{sybil}.
+A suitably powerful node, or motivated attacker, could create enough pseudonyms to create a subnetwork of nodes, each creating malicious transactions with each other.
+This would allow an attacker to falsify a believable location proof.
+
+A web of trust may be used to establish a trust rating between known nodes in the network.
+When two nodes meet and create a transaction, they will also publish a separate entry into the blockchain, signing each others keys.
+When a verifier is walking the location proof graph of a node seeking verification, it will establish a trust rating for each alibi node it encounters.
+Anomolies in the trust rating (for example if the trust ratings for most alibis are dependent on a small subset of nodes) will reveal attempted Sybil attacks, and the verifier can choose to reject the proof request.
+\textbf{How can this be done without revealing the public keys of each node involved in a transaction (thus opening them up for tracking)?}.
 
@@
 
+\bibitem{sybil}
+  Douceur, J.R.,
+  ``The sybil attack'',
+  Druschel, P., Kaashoek, M.F., Rowstron, A. (eds.) IPTPS 2002. LNCS, vol. 2429, pp. 251–260,
+  Springer, Heidelberg (2002)
+
 \end{thebibliography}

### 2016-02-29 paper.tex
adding sybil paper

@@
 \subsection{Sybil attack}
-Currently there is no provably correct way of preventing a Sybil attack, where a single physical node may create multiple \textit{pseudoidentities} \cite{sybil}.
+This system is vulnerable to a Sybil attack, where a single physical node may create multiple \textit{pseudoidentities} \cite{sybil}.
 A suitably powerful node, or motivated attacker, could create enough pseudonyms to create a subnetwork of nodes, each creating malicious transactions with each other.
@@
 
-A web of trust may be used to establish a trust rating between known nodes in the network.
-When two nodes meet and create a transaction, they will also publish a separate entry into the blockchain, signing each others keys.
-When a verifier is walking the location proof graph of a node seeking verification, it will establish a trust rating for each alibi node it encounters.
-Anomolies in the trust rating (for example if the trust ratings for most alibis are dependent on a small subset of nodes) will reveal attempted Sybil attacks, and the verifier can choose to reject the proof request.
-\textbf{How can this be done without revealing the public keys of each node involved in a transaction (thus opening them up for tracking)?}.
+It has been proven that a central certificate authority is the only method of preventing a Sybil attack \cite{sybil}.
+Other measures, such as web of trust, increase the difficulty involved in performing an attack, but the system remains vulnerable to a motivated attacker.
 

### 2016-03-06 paper.tex
improving design chapter

@@
 \documentclass[12pt]{article}
+
+\usepackage{tikz}
+\usetikzlibrary{calc,arrows}
+\usepackage{enumitem}
 
@@
 
-\section{Decentralised location proof system}
-This location proof system is comprised of a network of mobile nodes, capable of anonymously providing and receiving an alibi to/from other nodes on the network.
+\newpage
+\section{Design}
+The location proof system we propose allows mobile nodes to create location proofs for each other after physically meeting.
+When two nodes are in close physical proximity, they initiate a transaction over a short range, ad-hoc network such as bluetooth.
 
-When two nodes are in close physical proximity, they initiate a transaction with each other over a short range, ad-hoc network such as bluetooth.
-To create this transaction, they must agree on their current GPS coordinates and the current time.
-Once both nodes reach agreement on these parameters, they each create an encrypted transaction that claims their current time and location.
-This transaction must also contain references to both the alibi's identity, and the index of the node’s most recent transaction.
-Both nodes then publish their own transaction, indexed using their identity, onto a public append-only bulletin board/blockchain.
+To create a transaction, two nodes anonymously agree upon their location and current time over a short-range network.
+Once both nodes agree upon these parameters, they each create an encrypted, privacy-protecting transaction logging their location and the alibi used to create the transaction.
+This transaction is published onto a public, append-only bulletin board known as a \textit{blockchain}.
+Once given permission and decryption keys from a node, a \textit{verifier} can determine whether or not the node is present at its claimed location.
 
-A node can give verifiers permission to verify its location.
-The node will give the verifier access to the keys used to encrypt each of the node’s $n$ most recent transactions.
-After finding and decrypting the transactions, the 3rd party will decide based whether or not to accept the node's claimed location as truth.
+Any node acting as an alibi in a transaction will share details of its most recent transactions with the other node in the transaction.
+This allows the verifier to be given permission to check the authenticity of all recent alibi's, and each of the alibi's recent alibi's, etc.
+Only the owner of the transaction can give permission to a verifier to check its location history, by providing the verifier with the keys needed to decrypt the transactions.
 
@@
 \subsection{Transactions}
-During a transaction between two nodes, a number of different items must be shared and calculated.
-The first step in a transaction is for both nodes to agree upon a GPS location and current time.
-Nodes likely won't have the exact same GPS coordinates or time, but once the values don;t differ by more than some constant $\epsilon$, the nodes will continue with the transaction.
+During a transaction between two nodes, a number of different items must be shared and calculated. Figure \ref{fig:transaction} describes an honest, successful transaction.
 
-After nodes agree upon the parameters of the transaction, they exchange their key packets with each other.
-A key packet is a list of the nodes $m$ most recent identities, along with the keys needed to decrypt them.
-This allows the verifier to check the credibility of each alibi the node seeking verification has collected.
+\begin{figure}[h]
+\resizebox {\columnwidth} {!} {\input{diagrams/transaction.tex}}
+\caption{Honest, successful transaction}
+\label{fig:transaction}
+\end{figure}
 
-The following transaction data will be published onto the blockchain by node A:
+When a node is initialised, it must begin to record two \textit{Key Lists} for itself.
+A \textit{Key List} is a list of encryption keys previously used for transactions.
+For example, $KL_{A1}[n]$ and $KL_{A2}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively.
+These \textit{Key Lists} and are assumed to have been at least initialised (if not already populated) before the transaction described in Figure \ref{fig:transaction} begins.
 
-$T_{An} = ID_{An} | K_{A1n}(ID_{An-1}) | K_{A2n}(ts, loc, ID_{An}, ID_{An-1}, KP_{Bm})$
+After creating an ad-hoc bluetooth network between nodes $A$ and $B$, the first step in the transaction is for both nodes to share their IDs, and agree upon a GPS location and current time.
+Nodes likely won't share the exact same GPS coordinates or time, but once the values don't differ by more than some small constant $\epsilon$, the nodes will continue with the transaction.
+If node $A$ claims a GPS location or timestamp that differs from what node $B$ senses by more than $\epsilon$, node $B$ will abort the transaction.
 
-\begin{itemize}
-	\item[] $\mathbf{ID_{An}}$: The current ID of node $A$.
-	\item[] $\mathbf{K_{A1n}(ID_{An-1})}$: Node $A$'s previous identity.
-This creates a backward link between $A$'s transactions, used to preserve the ``privacy protected chronology'' property of OTIT \cite{otit}.
-This is encrypted with a symmetric key $K_{A1n}$ to stop curious users monitoring the blockchain to track other users.
-	\item[] $\mathbf{K_{A2n}}$: Node $A$'s second current symmetric key at transaction $n$, used to encrypt the body of the transaction.
-This is separate from $K_{A1n}$ to preserve ``privacy protected chronology'' and ''selective in-sequence privacy'' \cite{otit}.
-	\item[] $\mathbf{ts}$: The agreed timestamp.
-	\item[] $\mathbf{loc}$: The agreed GPS coordinates.
-	\item[] $\mathbf{ID_{An} and ID_(An-1)}$:  Node $A$'s current identity and most recent identity respectively, encrypted with $K_{An}$.
-These are used to prevent a possible identity theft attack whereby a malicious man-in-the-middle may try to alter the ID attached to the transaction.
-	\item[] $\mathbf{KP_{Bm}}$: Node $B$'s key packet at transaction $m$ (relative to $B$).
-This contains $B$'s $n$ most recent transaction keys, so any verifier that node $A$ requests will be able to validate the credibility of alibi $B$ by decrypting his transactions.
+After nodes agree upon the parameters of the transaction, they exchange their previous ID, along with their \textit{Key Packets}.
+A \textit{Key Packet} is a list of keys used in a node's $n$ most recent transactions, along with the transaction ID's if necessary.
+This allows node $A$ to decrypt node $B$'s $m$ most recent transactions, therefore providing an alibi for node $A$.
+
+\subsubsection{Transaction creation}
+Once nodes have exchanged \textit{Key Packets}, their communication is finished and they can close their ad-hoc channel.
+Each node creates a new transaction object, $T$, to publish onto the public blockchain.
+The following transaction data will be calculated by node $A$, after communicating with node $B$:
+\\
+
+$T_{An} = KL_{AT}[n](ts|loc|ID_{An}|KP_{Bm})$
+\\
+
+Where:
+\begin{itemize}[noitemsep,topsep=0pt]
+	\item[] $\mathbf{n}$ is node $A$'s current transaction number (i.e. $A$ has published $n-1$ transactions before now).
+	\item[] $\mathbf{ts}$ is the timestamp of the transaction, as recorded by node $A$.
+	\item[] $\mathbf{loc}$ is the GPS coordinates of the transaction, as recorded by node $A$.
+	\item[] $\mathbf{KL_{AT}}$ is one of $A$'s \textit{Key Lists}, used to encrypt transactions.
 \end{itemize}
 
+\subsubsection{Publishing to the blockchain}
+After creating $T_{An}$, node $A$ needs to publish it to the public blockchain.
+The data published must be identifiablein order to provide a verifier with some way of identifying specific transactions.
+Nodes will use their current ID as the identifier for the transaction.
+
+Backwards-chaining is an important part of verifiability.
+The verifier must be able to prove that the proof chain provided by the node has not had its order altered.
+The transaction must therefore be accompanied by a link to the node's chronologically previous transaction.
+This link must be encrypted, otherwise a malicious user monitoring the public blockchain could monitor a user's transaction publishing activity.
+$A$'s copy of the transaction log $P_{An}$ will therefore be in the form:
+
+$P_An = ID_{An}|KL_{AL}[n](ID_{An-1})|T_{An}$
+
+To publish $P_{An}$, $A$ must send $P_{An}$ to a miner node, who will add it to its \textit{pending transaction} queue, and send it to other miners in the network to add it to their queues as well.
+The transaction will then be signed into the next block in the blockchain.
+
+\subsubsection{Key Packets}
 The key packet is more than simply a list of keys that $B$ has used to encrypt his transactions; in order to preserve the ``privacy preserved'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt.
-For this reason, the transaction backwards-chaining may need to be broken.
-For example, if node $B$ doesn't want to reveal transaction $T_{Bm-3}$, he would reveal the following key packet:
+However, in order to simultaneously preserve OTIT's ``provacy protected chronology'' property, the transaction backwards-chaining must not be broken.
+This is why two separate \textit{Key Lists} are maintained; $KL_{A1}$ is used to encrypt the backwards-chaining link, while $KL_{A2}$ encrypts the transaction data.
+For example, if node $B$ doesn't want to reveal transaction $T_{Bm-1}$, he would reveal the following key packet:
+\\
 
-$KP_{Bm} = (\{ID_{Bm}, K_{Bm}\}, K_{Bm-1}, K_{Bm-2}, \{ID_{Bm-4}, K_{Bm-4}\}, K_{Bm-5}, \ldots, K_{Bm-n})$
-\\
-\\
-\indent
-In this case, $ID_{Bm-4}$ is needed along with $K_{Bm-4}$ so the verifier knows at which ID the privacy-protected chain will become unprotected, and can be decrypted.
+\noindent
+$KP_{Bm} = (\{KL_{BL}[m], KL_{BT}[m]\}, KL_{BL}[m-1], \{KL_{BL}[m-2], KL_{BT}[m-2]\}, \ldots, \{KL_{BL}[m-n], KL_{BT}[m-n]\})$
+
+\null
+In this case, $KL_{BT}[m-1]$ has not been included with $KL_{BL}[m-1]$, in order to protect the privacy of this transaction.
+This may be needed, for example, if node $B$ doesn't want to allow anyone to decrypt any transactions he has created withing 5Km of his home, in order to protect his privacy.
 
@@
 
+\bibitem{location-spoof}
+  N. O. Tippenhauer, K. B. Rasmussen, C. Popper, and S. Capkun,
+  ``iPhone and iPod location spoofing: Attacks on public WLAN-based positioning systems'',
+  SysSec Technical Report,
+  ETH Zurich, April, 2008
+
 \end{thebibliography}

### 2016-03-09 paper.tex
improving design section

@@
 \usepackage{enumitem}
+\usepackage{float}
 
@@
 
-When a node is created, it generates (or is provided with?) a certificate (or key pair).
+% add nonces and PK verification to the verify_request diagram! and discuss them below!
+
+When a node is created, it generates a key pair.
 To maintain anonymoty, the node will use the public key to encrypt some nonces to create identities, and use these identify itself in a transaction.
@@
 A \textit{Key List} is a list of encryption keys previously used for transactions.
-For example, $KL_{A1}[n]$ and $KL_{A2}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively.
+For example, $KL_{AT}[n]$ and $KL_{AL}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively.
 These \textit{Key Lists} and are assumed to have been at least initialised (if not already populated) before the transaction described in Figure \ref{fig:transaction} begins.
@@
 	\item[] $\mathbf{KL_{AT}}$ is one of $A$'s \textit{Key Lists}, used to encrypt transactions.
+	\item[] $\mathbf{KP_{Bm}}$ is $B$'s \textit{Key Packet} at time $m$. Its exact contents are discussed in more detail in section \ref{sssec:key_packets}
 \end{itemize}
@@
 
-$P_An = ID_{An}|KL_{AL}[n](ID_{An-1})|T_{An}$
+$P_{An} = ID_{An}|KL_{AL}[n](ID_{An-1})|T_{An}$
 
@@
 
-\subsubsection{Key Packets}
+\subsubsection{Key Packets} \label{sssec:key_packets}
 The key packet is more than simply a list of keys that $B$ has used to encrypt his transactions; in order to preserve the ``privacy preserved'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt.
@@
 \noindent
-$KP_{Bm} = (\{KL_{BL}[m], KL_{BT}[m]\}, KL_{BL}[m-1], \{KL_{BL}[m-2], KL_{BT}[m-2]\}, \ldots, \{KL_{BL}[m-n], KL_{BT}[m-n]\})$
+${KP_{Bm} = (\{KL_{BL}[m], KL_{BT}[m]\}, KL_{BL}[m-1], \{KL_{BL}[m-2], KL_{BT}[m-2]\})}$
 
@@
 \subsection{Verification}
-The verification stage is the most algorithmically complex part of the system.
-It is performed by the verifier.
-Given the keys for a node's $n$ most recent transactions, the verifier will walk chronologically backwards along the public location proof chain.
-At each transaction encountered, the search will fork along the proof history path of both parties involved in that transaction, and continue until all available transactions have been exhausted.
+\begin{minipage}{0.5\linewidth}
+In the verification stage, a node tries to prove its location to a Verifier 3rd party, e.g.
+a bank.
+To do this, the node sends the Verifier a number of parameters, as shown in Figure \ref{fig:verify_request}:
+\begin{itemize}[noitemsep,topsep=0pt]
+	\item[] $\mathbf{ID_{An-1}}$ is the ID of $A$'s most recently published transaction.
+	\item[] $\mathbf{KP_{An-1}}$ is $A$'s key packet from transaction $n-1$, and includes keys for as many transactions as $A$ feels is apropriate in order to receive verification.
+	\item[] $\mathbf{loc}$ is $A$'s current claimed location for which it is seeking verification.
+	\item[] $\mathbf{NP_{An-1}}$ is $A$'s \textit{Nonce Packet}, a list of the nonces used to generate $A$'s most recent IDs, from $n-1$.	
+\end{itemize}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{0.5\linewidth}
+\begin{figure}[H]
+\input{diagrams/verify_request.tex}
+\caption{Verification request}
+\label{fig:verify_request}
+\end{figure}
+\end{minipage}
 
-The goal of the verification stage is to either accept or reject the location that the user is claiming.
-There are a huge number of factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain verifiers, and kept secret to improve reliability.
+The goal of the verification stage is for the Verifier to either accept or reject the location that the user is claiming.
+Given $ID_{An-1}$ and $KP_{An-1}$, a Verifier is able to retrieve $A$'s previous transactions, and the transactions of all of its alibi's.
+
+The Verifier uses $NP_{An-1}$ and $K^{+}_A$ to prove that node $A$ was the author of all of the transactions he claims to be.
+This prevents a collusion attack whereby nodes could share common transactions between different proof chains.
+When walking chronologically backwards along $A$'s proof chain, the 3rd party will ensure that the ID used in transaction $m$ on the proof chain matches $K^{+}_A(NP_{An-1}[m])$.
+
+There are a huge number of possible factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain verifiers, and kept secret to improve reliability and avoid gaming.
 Some simple example factors may include:

### 2016-03-10 paper.tex
adding transaction aborting, fixing some errors with diagrams

@@
 \subsection{Transactions}
-During a transaction between two nodes, a number of different items must be shared and calculated. Figure \ref{fig:transaction} describes an honest, successful transaction.
+During a transaction between two nodes, a number of different items must be shared and calculated.
+Figure \ref{fig:transaction} describes an honest, successful transaction, assuming an ad-hoc bluetooth network has already been set up between nodes $A$ and $B$.
 
@@
 
+Where:
+\begin{itemize}[noitemsep,topsep=0pt]
+	\item[] $\mathbf{NL_A[n]}$ is the $n$th nonce in $A$'s \textit{Nonce List}, which is used to generate $ID_{An}$.
+\end{itemize}
+
+\null
 When a node is initialised, it must begin to record two \textit{Key Lists} for itself.
@@
 $A$'s copy of the transaction log $P_{An}$ will therefore be in the form:
+\\
 
@@
 
+\null
 To publish $P_{An}$, $A$ must send $P_{An}$ to a miner node, who will add it to its \textit{pending transaction} queue, and send it to other miners in the network to add it to their queues as well.
@@
 
-\noindent
 ${KP_{Bm} = (\{KL_{BL}[m], KL_{BT}[m]\}, KL_{BL}[m-1], \{KL_{BL}[m-2], KL_{BT}[m-2]\})}$
@@
 This may be needed, for example, if node $B$ doesn't want to allow anyone to decrypt any transactions he has created withing 5Km of his home, in order to protect his privacy.
+
+\subsubsection{Aborting transactions}
+A node may decide to abort a transaction if it thinks it is in contact with a malicious node.
+In figure \ref{fig:aborted_transaction}, node $A$ encounters a malicious node $M$, who tries to spoof its identity with $A$.
+Node $A$ will abort the transaction once it notices that $|ts_A-ts_M| < \epsilon_{ts}$, or $|loc_A-loc_M| < \epsilon_{loc}$.
+
+To abort the transaction, $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain.
+This means that even if $M$ fabricates some data from $A$ and publishes a transaction onto the blockchain, the matching transaction from $A$ will not be present.
+Any transaction on the blockchain that does not reference the transaction of the alibi used to create it will be disregarded by any Verifiers.
+
+\begin{figure}[h]
+\resizebox {\columnwidth} {!} {\input{diagrams/aborted_transaction.tex}}
+\caption{An aborted transaction due to malicious node $M$}
+\label{fig:aborted_transaction}
+\end{figure}
 

### 2016-03-17 thesis/background.tex
adding initial thesis files

\section{Background}
\subsection{Proving your location}
As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, the security that existed by requiring physical interaction between humans to transfer sensitive data is lost.

\subsection{Ad-hoc networks}

\subsection{Blockchain}

\subsection{Centralised location proof systems}
Location proof systems are expected to be accurate and tamper-proof. For this reason, existing solutions have chosen to use a central authority to issue proofs, or to regulate proof issuance \cite{brassil, luo, khan}.

A hardware technique \cite{brassil} operates by supplementing existing WiFi access points with \textit{femtocells}. A femtocell is a small cellular antenna that connects to a mobile carrier via the Internet. Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data via Wi-Fi. This solution requires investment in additional hardware to supplement existing WiFi access points, and requires access to mobile providers' user database to identify users locations.

The use of a centralised system, like that described by Brassil et al. \cite{brassil}, creates security, privacy and vulnerability issues. An attacker who succeeds in compromising the security of the central server can violate the privacy of the users of the system, and potentially track their location. The central system architecture is also vulnerable, in the sense that a resource availability attack such as a DDoS attack could render the central architecture unavailable, making location verification unavailable.

Luo et al. propose a system that uses Wi-Fi access points (\textit{AP's}) to allow users to create location proofs \cite{luo}. In their system, each access point has a \textit{group signature} and can sign location proofs for requesting users. Users can request a location proof from any access point, and receive a proof encrypted by the AP with the group signature, as shown in figure \ref{fig:luo_transaction}. This can then be submitted to a Verifier.

\begin{figure}[H]
\begin{center}
\resizebox {0.6\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
\end{center}
\caption{Adopted from Luo et al. \cite{luo}}
\label{fig:luo_transaction}
\end{figure}

This kind of system creates \textit{proactive} location proofs. A proactive location proof is one which is created before it is needed. The user creates application-independent location proofs, and can use them at a later time with any application(s) he chooses.

### 2016-03-17 thesis/introduction.tex
adding initial thesis files

\section{Introduction}
\subsection{Project and Motivation}
Location verification is the process of verifying whether or not a mobile node (computer) is physically present at the location it claims to be. Existing location verification systems attept to provide this service using centralised, trusted ``authoritive'' nodes to provide proof of a mobile node's location. These approaches require investment in infrastructure, and are subject to data breaches and denial of service attacks. This project aims to present a \textit{decentralised} solution to this problem, in which there is no ``authoritive source'' trusted and relied upon to provide and store location information.

This project will focus on obtaining location proofs by using other untrusted mobile nodes as \textit{alibi's}. Proofs will be created over an ad-hoc peer-to-peer network, encrypted, and published on a public append-only bulletin board, known as a \textit{blockchain}. The decentralised nature of the system means that there is no single point of failure, and no one entity controlling the security of every node's location proofs.

### 2016-03-17 thesis/thesis.tex
adding initial thesis files

--- 2016-03-06 paper.tex
@@
 
-\documentclass[12pt]{article}
+\documentclass[12pt,titlepage]{article}
 
@@
 \usepackage{enumitem}
+\usepackage{float}
+
+\author{Conor Taylor}
+\date{
+	B.A.(Mod.) Computer Science\\
+	Final Year Project, April 2016\\
+	Supervisor: Stephen Barrett
+}
 
@@
 
-\section{Introduction}
-
-\section{Previous work}
-Location proof systems are expected to be accurate and tamper-proof. For this reason, existing solutions have chosen to use a central authority to issue proofs \cite{brassil, luo, khan}.
-
-Hardware techniques \cite{brassil} operate by supplementing existing WiFi access points with \textit{femtocells} (small cellular antennae that connect to the mobile carrier via the Internet).
-Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data via Wi-Fi.
-This solution requires investment in additional hardware to supplement existing WiFi access points.
-It also requires access to mobile providers user database to identify users locations.
-
-Other proof systems \cite{luo} deploy software on Wi-Fi access points.
-Access points taking part in the location proof network become part of a 'group' with a shared group signature.
-Mobile nodes can request a location proof from an access point, who signs it with the group signature.
-Access points provide location proofs to nodes without ever learning the node's identity, thus protecting user's privacy.
-However, due to the system’s reliance on the group signature structure, access points become a target for attack.
-Compromising an access point would allow an attacker to create false location proofs.
-
-\cite{luo} considers a number of threats in their architecture:
-\begin{itemize}
-	\item \textbf{Dishonest users.} A dishonest user tries to obtain location proofs that certify her presence at some place at a particular time even if she was not there.
-Dishonest users may achieve this goal by colluding with malicious intruders.
-	\item \textbf{Malicious intruders.} A malicious intruder is not interested in obtaining location proofs for her own use but offers to help other users to get location proofs on their behalf in exchange for other benefits like money.
-	\item \textbf{Curious APs and applications.} A curious AP tries to learn a user’s identity while the user is acquiring a location proof from the AP.
-Similarly, a curious application tries to learn more location information from a location proof than it really needs.
-	\item \textbf{Malicious applications.} A malicious application obtains location proofs from its users and then tries to take advantage of these proofs to get unauthorised access to other applications.
-	\item \textbf{Active and passive eavesdroppers.} An eavesdropper records and maybe modifies communication between users, proof- ssuers, or applications.
-\end{itemize}
-
-Distributed P2P location proof systems also exist \cite{khan}.
-A central authority is used and acts as a certificate authority, issuing a unique ID to each person using the system.
-Unique identity is proved by users by providing SSN, driver’s licence, or passport documents.
-This removes the threat of a Sybil attack \cite{sybil}, but makes the central authority a clear target for attack.
-The system uses three parties to provide location proofs; a mobile user who requests a proof, a fixed location authority, and a mobile user who acts as a witness.
-The system becomes vulnerable in the case where all three users collude, but is otherwise quite an interesting approach.
-
-\cite{khan} also outlines a number of possible attacks on their system:
-\begin{itemize}
-	\item \textbf{False presence:} A malicious user can create a fake location proof on his own, without being physically present at the location.
-The fake proof is supposed to resemble an actual proof, which the user could have actually collected from a valid location authority.
-	\item \textbf{False timestamping (backdating, future dating):} In a backdating attack, the user and the location authority colludes to create a proof for a past time.
-Conversely, in future dating, the location authority and a user colludes to generate a proof with a future timestamp.
-	\item \textbf{Implication:} A location authority and/or a witnesses can falsely accuse a user of his presence at a certain location.
-In this case, the malicious location authority and witness colludes to generate a false proof of presence for the user.
-	\item \textbf{False assertion:} A user can collude with a witness, and generate a falsely asserted location proof.
-The truth value in such a fake proof is reinstated with the assertion received from the other user.
-	\item \textbf{Denial of presence:} A user can visit a location and at a later time, deny his presence at that location.
-In such a case, the user actually denies the validity of a certain location proof that has been been generated upon his presence at that particular location.
-	\item \textbf{Proof switching:} The user is expected to have full access to all storage facilities on his mobile device.
-Hence, the user utilizes the legitimate proof and manipulates the information to create a false proof for a different location.
-	\item \textbf{Relay attack:} A user can use a proxy to relay the requests and collect a location proof.
-Alternatively, a location authority can maliciously relay assertion requests with the witness not being present at the site.
-	\item \textbf{Sybil attack:} A Sybil attack occurs when a single user generates multiple presence and identities [29].
-A user can launch a Sybil attack by generating multiple identities representing a user and a witness and provide false endorsements for location proofs.
-	\item \textbf{Denial of witness’s presence:} At the time of proof verification, the user can claim the absence of witnesses at the site or falsely claim an assertion to be counterfeit.
-The user and the location authority may also collude and claim the non-availability of witnesses.
-	\item \textbf{Privacy violation:} An attacker may capture an asserted location proof generated for a user, and discover the identity of the user and/or the witness.
-\end{itemize}
-
-'OTIT' \cite{otit}, a model for designing secure location provenance, can be used to compare existing location proof systems.
-This model defines the following requirements necessary for designing any secure location provenance scheme: Chronological, Order Preserving, Vereifiable, Tamper Evident, Privacy Preserved, Selective In-Sequence Privacy, Privacy Protected Chronology, and Convenience \& Derivability.
+\input{introduction.tex}
+\newpage
+\input{background.tex}
 
 \newpage
-\section{Design}
-The location proof system we propose allows mobile nodes to create location proofs for each other after physically meeting.
-When two nodes are in close physical proximity, they initiate a transaction over a short range, ad-hoc network such as bluetooth.
-
-To create a transaction, two nodes anonymously agree upon their location and current time over a short-range network.
-Once both nodes agree upon these parameters, they each create an encrypted, privacy-protecting transaction logging their location and the alibi used to create the transaction.
-This transaction is published onto a public, append-only bulletin board known as a \textit{blockchain}.
-Once given permission and decryption keys from a node, a \textit{verifier} can determine whether or not the node is present at its claimed location.
-
-Any node acting as an alibi in a transaction will share details of its most recent transactions with the other node in the transaction.
-This allows the verifier to be given permission to check the authenticity of all recent alibi's, and each of the alibi's recent alibi's, etc.
-Only the owner of the transaction can give permission to a verifier to check its location history, by providing the verifier with the keys needed to decrypt the transactions.
-
-\subsection{Identities}
-In order to preserve user's privacy, a user will only ever use an identity for one transaction, before generating a new one.
-This prevents malicious users from watching the public blockchain for a known identity and tracking it.
-However, to prevent identity theft, it is important for the verifier to be able to prove that a node was the original creator of each identity.
-This is achieved using a public/private key pair for each node.
-
-When a node is created, it generates (or is provided with?) a certificate (or key pair).
-To maintain anonymoty, the node will use the public key to encrypt some nonces to create identities, and use these identify itself in a transaction.
-During the verification stage, the node will provide the verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions.
-The verifier calculates the node's identities using the public key and nonces, and retrieves the relevant transactions from the public blockchain.
-The verifier will also ensure that the node owns the private key associated with the provided public key, to prevent identity theft.
-
-\subsection{Transactions}
-During a transaction between two nodes, a number of different items must be shared and calculated. Figure \ref{fig:transaction} describes an honest, successful transaction.
-
-\begin{figure}[h]
-\resizebox {\columnwidth} {!} {\input{diagrams/transaction.tex}}
-\caption{Honest, successful transaction}
-\label{fig:transaction}
-\end{figure}
-
-When a node is initialised, it must begin to record two \textit{Key Lists} for itself.
-A \textit{Key List} is a list of encryption keys previously used for transactions.
-For example, $KL_{A1}[n]$ and $KL_{A2}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively.
-These \textit{Key Lists} and are assumed to have been at least initialised (if not already populated) before the transaction described in Figure \ref{fig:transaction} begins.
-
-After creating an ad-hoc bluetooth network between nodes $A$ and $B$, the first step in the transaction is for both nodes to share their IDs, and agree upon a GPS location and current time.
-Nodes likely won't share the exact same GPS coordinates or time, but once the values don't differ by more than some small constant $\epsilon$, the nodes will continue with the transaction.
-If node $A$ claims a GPS location or timestamp that differs from what node $B$ senses by more than $\epsilon$, node $B$ will abort the transaction.
-
-After nodes agree upon the parameters of the transaction, they exchange their previous ID, along with their \textit{Key Packets}.
-A \textit{Key Packet} is a list of keys used in a node's $n$ most recent transactions, along with the transaction ID's if necessary.
-This allows node $A$ to decrypt node $B$'s $m$ most recent transactions, therefore providing an alibi for node $A$.
-
-\subsubsection{Transaction creation}
-Once nodes have exchanged \textit{Key Packets}, their communication is finished and they can close their ad-hoc channel.
-Each node creates a new transaction object, $T$, to publish onto the public blockchain.
-The following transaction data will be calculated by node $A$, after communicating with node $B$:
-\\
-
-$T_{An} = KL_{AT}[n](ts|loc|ID_{An}|KP_{Bm})$
-\\
-
-Where:
-\begin{itemize}[noitemsep,topsep=0pt]
-	\item[] $\mathbf{n}$ is node $A$'s current transaction number (i.e. $A$ has published $n-1$ transactions before now).
-	\item[] $\mathbf{ts}$ is the timestamp of the transaction, as recorded by node $A$.
-	\item[] $\mathbf{loc}$ is the GPS coordinates of the transaction, as recorded by node $A$.
-	\item[] $\mathbf{KL_{AT}}$ is one of $A$'s \textit{Key Lists}, used to encrypt transactions.
-\end{itemize}
-
-\subsubsection{Publishing to the blockchain}
-After creating $T_{An}$, node $A$ needs to publish it to the public blockchain.
-The data published must be identifiablein order to provide a verifier with some way of identifying specific transactions.
-Nodes will use their current ID as the identifier for the transaction.
-
-Backwards-chaining is an important part of verifiability.
-The verifier must be able to prove that the proof chain provided by the node has not had its order altered.
-The transaction must therefore be accompanied by a link to the node's chronologically previous transaction.
-This link must be encrypted, otherwise a malicious user monitoring the public blockchain could monitor a user's transaction publishing activity.
-$A$'s copy of the transaction log $P_{An}$ will therefore be in the form:
-
-$P_An = ID_{An}|KL_{AL}[n](ID_{An-1})|T_{An}$
-
-To publish $P_{An}$, $A$ must send $P_{An}$ to a miner node, who will add it to its \textit{pending transaction} queue, and send it to other miners in the network to add it to their queues as well.
-The transaction will then be signed into the next block in the blockchain.
-
-\subsubsection{Key Packets}
-The key packet is more than simply a list of keys that $B$ has used to encrypt his transactions; in order to preserve the ``privacy preserved'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt.
-However, in order to simultaneously preserve OTIT's ``provacy protected chronology'' property, the transaction backwards-chaining must not be broken.
-This is why two separate \textit{Key Lists} are maintained; $KL_{A1}$ is used to encrypt the backwards-chaining link, while $KL_{A2}$ encrypts the transaction data.
-For example, if node $B$ doesn't want to reveal transaction $T_{Bm-1}$, he would reveal the following key packet:
-\\
-
-\noindent
-$KP_{Bm} = (\{KL_{BL}[m], KL_{BT}[m]\}, KL_{BL}[m-1], \{KL_{BL}[m-2], KL_{BT}[m-2]\}, \ldots, \{KL_{BL}[m-n], KL_{BT}[m-n]\})$
-
-\null
-In this case, $KL_{BT}[m-1]$ has not been included with $KL_{BL}[m-1]$, in order to protect the privacy of this transaction.
-This may be needed, for example, if node $B$ doesn't want to allow anyone to decrypt any transactions he has created withing 5Km of his home, in order to protect his privacy.
-
-\subsection{Verification}
-The verification stage is the most algorithmically complex part of the system.
-It is performed by the verifier.
-Given the keys for a node's $n$ most recent transactions, the verifier will walk chronologically backwards along the public location proof chain.
-At each transaction encountered, the search will fork along the proof history path of both parties involved in that transaction, and continue until all available transactions have been exhausted.
-
-The goal of the verification stage is to either accept or reject the location that the user is claiming.
-There are a huge number of factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain verifiers, and kept secret to improve reliability.
-Some simple example factors may include:
-\begin{itemize}
-	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, then the node is likely attempting a poorly-constructed Sybil attack, and the verifier will reject his verification request.
-	\item \textbf{Alibi reuse:} if the verifier can prove that alibi’s are being reused frequently, then it will reject the verification request.
-	\begin{itemize}
-		\item Due to transaction anonymity, the verifier may not always be able to tell if two alibi's are the same person or not.
-e.g.
-node $A$ could use node $B$ as an alibi, then wait for $B$ to complete $n$ more transactions, then use node $B$ again.
-		\item This is not a viable attack on the verification system.
-Depending on the size of $n$, enough time may pass between both uses of node $B$ as an alibi that the transactions are no longer relevant.
-	\end{itemize}
-\end{itemize}
-
-\subsection{Sybil attack}
-This system is vulnerable to a Sybil attack, where a single physical node may create multiple \textit{pseudoidentities} \cite{sybil}.
-A suitably powerful node, or motivated attacker, could create enough pseudonyms to create a subnetwork of nodes, each creating malicious transactions with each other.
-This would allow an attacker to falsify a believable location proof.
-
-It has been proven that a central certificate authority is the only method of preventing a Sybil attack \cite{sybil}.
-Other measures, such as web of trust, increase the difficulty involved in performing an attack, but the system remains vulnerable to a motivated attacker.
-
-\section{Results}
-
-\section{Conclusions}
-
 \begin{thebibliography}{9}

### 2016-03-22 paper.tex
adding initial evaluation section with OTIT conformance comparison

@@
 \usepackage{float}
+\usepackage{enumitem}
+
+\setlist{parsep=0pt,listparindent=\parindent}
 
@@
 
-\subsection{Transactions}
+\subsection{Transactions} \label{sec:transactions}
 During a transaction between two nodes, a number of different items must be shared and calculated.
@@
 For example, $KL_{AT}[n]$ and $KL_{AL}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively.
-These \textit{Key Lists} and are assumed to have been at least initialised (if not already populated) before the transaction described in Figure \ref{fig:transaction} begins.
+These \textit{Key Lists} and are assumed to have been initialised and populated before the transaction described in Figure \ref{fig:transaction} begins.
 
@@
 
-$P_{An} = ID_{An}|KL_{AL}[n](ID_{An-1})|T_{An}$
+$P_{An} = ID_{An}|KL_{AL}[n](ID_{An-1}|ts_A)|T_{An}$
 
@@
 \subsubsection{Key Packets} \label{sssec:key_packets}
-The key packet is more than simply a list of keys that $B$ has used to encrypt his transactions; in order to preserve the ``privacy preserved'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt.
-However, in order to simultaneously preserve OTIT's ``provacy protected chronology'' property, the transaction backwards-chaining must not be broken.
-This is why two separate \textit{Key Lists} are maintained; $KL_{A1}$ is used to encrypt the backwards-chaining link, while $KL_{A2}$ encrypts the transaction data.
+The key packet is more than simply a list of keys that $B$ has used to encrypt his transactions; in order to preserve the ``selective in-sequence privacy'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt.
+However, in order to simultaneously preserve OTIT's ``privacy protected chronology'' property, the transaction backwards-chaining must not be broken.
+This is why two separate \textit{Key Lists} are maintained; $KL_{AL}$ is used to encrypt the backwards-chaining link, while $KL_{AT}$ encrypts the transaction data.
 For example, if node $B$ doesn't want to reveal transaction $T_{Bm-1}$, he would reveal the following key packet:
@@
 
-\section{Results}
+\newpage
+\section{Evaluation}
+In this paper, we have presented a model for a location proof system which aims to preserve privacy and prevent false proofs from being created.
+
+\subsection{OTIT conformance}
+We can compare our model to OTIT \cite{otit}, a list of features and requirements necessary for designing any secure location proof scheme. OTIT presents 8 such requirements:
+\begin{enumerate}
+\item[] \textbf{Chronological}: The chronological property of OTIT ensures that transactions are published in the order they were created.
+In our system we do not enforce this property at the time of transaction publication.
+This is to avoid revealing any transaction information to the miner nodes, therefore preserving the privacy of the transaction owner.
+Instead, we enforce this property at the time of verification.
+The chronological link created by adding $KL_{AT}(ID_{A-1}|ts_A)$ to the transaction will allow Verifier nodes to prove that the transaction is chronologically ordered, preserving OTIT's ``Chronological'' property.
+
+\item[] \textbf{Order preserving}: This property states that the order of transactions cannot be modified after they are created.
+In our system, a blockchain is used to store transactions.
+In a blockchain, new blocks are added in a linear, chronological order, and cannot be modified so long as the majority of miners in the network are honest \cite{blueprint}.
+Therefore the transactions stored in these blocks satisfy the ``Order preserving'' property of OTIT.
+% in the dissertation i can discuss ordering within a block here (and go into detail about the merkle root etc)
+
+\item[] \textbf{Verifiable}: This states that the proof, and the order or proofs, should be verifiable by a trusted auditor.
+In our case, a Verifier node is an auditor trusted by the mobile node seeking verification.
+A Verifier node may be operated by a bank, government, or any entity wishing to make use of our location proof system.
+
+Our system inherently satisfies this property of OTIT, as Verifier nodes are required to verify or reject a mobile node's claimed location.
+This is done by examining the mobile node's chronological link of transactions, and recursing for each alibi used for each transaction along the chronological link until the Verifier can conclude if the transaction chain is valid or not.
+
+\item[] \textbf{Tamper evident}: Our system is tamper evident.
+If a malicious node creates a successful transaction with an honest node, but modifies the transaction data before publishing, a Verifier node will reject the malicious transaction.
+This rejection will be on the grounds that the matching transaction, published by the honest node, contains contradictory data.
+
+We assume the underlying security of the blockchain, so any malicious miner nodes will not be able to tamper with existing transaction data providing that the majority of CPU power in the mining system is owned by honest miners \cite{bitcoin}.
+Therefore the tamper evident property is satisfied.
+
+\item[] \textbf{Privacy preserved}: This states that the user should have control over his level of privacy exposure when using the system.
+In our system, this is provided using \textit{Key Lists} \ref{sec:transactions}.
+We provide two keys for each transaction; $KL_{AT}[n]$ is used to encrypt the \textit{transaction data} for $A$'s $nth$ transaction, and $KL_{AL}[n]$ is used to encrypt the \textit{backwards chronological link} between $A$'s $nth$ transaction and transaction $n-1$.
+
+To control his privacy, a user can choose only to reveal $KL_{AL}[n]$ for a specific transaction $n$.
+This may be useful if a user does not wish to reveal transaction data for transactions created within a certain distance of his house, for example.
+Hiding $KL_{AT}[n]$ while revealing $KL_{AL}[n]$ has the advantage of preserving the user's privacy while maintaining a clear backwards chronological link of transactions for the Verifier to follow, preserving both privacy and system consistency.
+
+\item[] \textbf{Selective in-sequence privacy}: This is the requirement that any proof chain must support \textit{sub-set verification}, allowing a user to provide only a sub-set of proofs from his current proof chain for verification.
+Our system satisfies this property by using \textit{Key Packets} (section \ref{sssec:key_packets}).
+
+In our system, a \textit{sub-set} of $A$'s proof chain can be defined as $KP_{An}$.
+The sub-set therefore begins with $ID_{An}$, and ends when there is no key $KL_{AL}[n-m]$ in $KP_{An}$ to decrypt the link to transaction $T_{An-m-1}$.
+
+\item[] \textbf{Privacy protected chronology}: This states that the proof system, which provides \textit{selective in-sequence privacy}, should also ensure that the user does not ``hide away'' important items within the subset.
+This is impossibnle in our system due to the use of backwards chronological linking between transactions, so our model satisfies this property.
+
+\item[] \textbf{Convenience and derivability}: This requirement states that the verification process should be convenient, and the user should not burden the Verifier node with a huge load of data.
+In our system, the data is stored in a central blockchain that the Verifier has access to, and the user provides the Verifier only with decryption keys and indexes into a sub-section of this data.
+Therefore the data sent to from the user to the Verifier, $KP_{An}$, is quite small in size.
+
+The Verifier has the freedom to decide how comprehensively to investigate the user's data; It can bound how deeply to investigate the graph of alibi's, if at all.
+We therefore satisfy this requirement by allowing the Verifier to choose how complex the verification process needs to be.
+\end{enumerate}
 
@@
 
+\bibitem{blueprint}
+  M. Swan,
+  ``Blockchain: Blueprint for a New Economy'',
+  Sebastopol, CA,
+  O’Reilly Media, 2015
+
+\bibitem{bitcoin}
+  S. Nakamoto,
+  ``Bitcoin: A Peer-to-Peer Electronic Cash System'',
+  2008
+
 \end{thebibliography}

### 2016-03-30 paper.tex
Adding overview diagrams and fixing errors

@@
 
-Hardware techniques \cite{brassil} operate by supplementing existing WiFi access points with \textit{femtocells} (small cellular antennae that connect to the mobile carrier via the Internet).
+Hardware techniques \cite{brassil} operate by supplementing existing Wi-Fi access points with \textit{femtocells} (small cellular antennae that connect to the mobile carrier via the Internet).
 Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data via Wi-Fi.
-This solution requires investment in additional hardware to supplement existing WiFi access points.
+This solution requires investment in additional hardware to supplement existing Wi-Fi access points.
 It also requires access to mobile providers user database to identify users locations.
@@
 Access points provide location proofs to nodes without ever learning the node's identity, thus protecting user's privacy.
-However, due to the system’s reliance on the group signature structure, access points become a target for attack.
+However, due to the systems reliance on the group signature structure, access points become a target for attack.
 Compromising an access point would allow an attacker to create false location proofs.
@@
 	\item \textbf{Malicious intruders.} A malicious intruder is not interested in obtaining location proofs for her own use but offers to help other users to get location proofs on their behalf in exchange for other benefits like money.
-	\item \textbf{Curious APs and applications.} A curious AP tries to learn a user’s identity while the user is acquiring a location proof from the AP.
+	\item \textbf{Curious APs and applications.} A curious AP tries to learn a users identity while the user is acquiring a location proof from the AP.
 Similarly, a curious application tries to learn more location information from a location proof than it really needs.
 	\item \textbf{Malicious applications.} A malicious application obtains location proofs from its users and then tries to take advantage of these proofs to get unauthorised access to other applications.
-	\item \textbf{Active and passive eavesdroppers.} An eavesdropper records and maybe modifies communication between users, proof- ssuers, or applications.
+	\item \textbf{Active and passive eavesdroppers.} An eavesdropper records and maybe modifies communication between users, proof- issuers, or applications.
 \end{itemize}
@@
 A central authority is used and acts as a certificate authority, issuing a unique ID to each person using the system.
-Unique identity is proved by users by providing SSN, driver’s licence, or passport documents.
+Unique identity is proved by users by providing SSN, drivers licence, or passport documents.
 This removes the threat of a Sybil attack \cite{sybil}, but makes the central authority a clear target for attack.
@@
 A user can launch a Sybil attack by generating multiple identities representing a user and a witness and provide false endorsements for location proofs.
-	\item \textbf{Denial of witness’s presence:} At the time of proof verification, the user can claim the absence of witnesses at the site or falsely claim an assertion to be counterfeit.
+	\item \textbf{Denial of witnesses presence:} At the time of proof verification, the user can claim the absence of witnesses at the site or falsely claim an assertion to be counterfeit.
 The user and the location authority may also collude and claim the non-availability of witnesses.
@@
 'OTIT' \cite{otit}, a model for designing secure location provenance, can be used to compare existing location proof systems.
-This model defines the following requirements necessary for designing any secure location provenance scheme: Chronological, Order Preserving, Vereifiable, Tamper Evident, Privacy Preserved, Selective In-Sequence Privacy, Privacy Protected Chronology, and Convenience \& Derivability.
+This model defines the following requirements necessary for designing any secure location provenance scheme: Chronological, Order Preserving, Verifiable, Tamper Evident, Privacy Preserved, Selective In-Sequence Privacy, Privacy Protected Chronology, and Convenience \& Derivability.
 
@@
 \section{Design}
-The location proof system we propose allows mobile nodes to create location proofs for each other after physically meeting.
-When two nodes are in close physical proximity, they initiate a transaction over a short range, ad-hoc network such as bluetooth.
+The location proof system we propose allows \textit{mobile nodes} to create location proofs for each other after physically meeting.
+When two mobile nodes are in close physical proximity, they initiate a transaction over a short range, ad-hoc network such as Bluetooth.
 
-To create a transaction, two nodes anonymously agree upon their location and current time over a short-range network.
-Once both nodes agree upon these parameters, they each create an encrypted, privacy-protecting transaction logging their location and the alibi used to create the transaction.
-This transaction is published onto a public, append-only bulletin board known as a \textit{blockchain}.
-Once given permission and decryption keys from a node, a \textit{verifier} can determine whether or not the node is present at its claimed location.
+To create a transaction, two mobile nodes anonymously share their GPS coordinates and current time over a short-range network.
+Both nodes then check that these parameters don't differ by more than some value $\epsilon$.
+Once satisfied, they each create an encrypted, privacy-protecting transaction logging their location and the identity of the other mobile node (the \textit{alibi}) used to create the transaction.
+This transaction is published onto a public, append-only bulletin board known as a \textit{blockchain} \cite{blueprint}.
 
-Any node acting as an alibi in a transaction will share details of its most recent transactions with the other node in the transaction.
-This allows the verifier to be given permission to check the authenticity of all recent alibi's, and each of the alibi's recent alibi's, etc.
-Only the owner of the transaction can give permission to a verifier to check its location history, by providing the verifier with the keys needed to decrypt the transactions.
+Once given permission from a mobile node (by transferring decryption keys), a \textit{Verifier node} can consult the data in blockchain and determine whether or not the mobile node is present at its claimed location.
+The blockchain is managed by a network of \textit{Miner nodes}, who collect transactions from mobile nodes, distribute them across the network, and try to create a new \textit{block} of transactions by attempting to solve a \textit{proof-of-work} puzzle.
+
+Any mobile node acting as an alibi in a transaction will share details of its most recent transactions with the other mobile node in the transaction.
+This means that when the mobile node seeks verification from a Verifier node, the Verifier can examine the mobile node's alibi's, and each of the alibi's recent alibi's, forming a large graph of connections which can be used to verify or reject the mobile nodes claimed location.
+Only the owner of the transaction can give permission to a Verifier to check its location history, by providing the Verifier with the keys needed to decrypt the transactions.
+
+Figure \ref{fig:overview} provides an overview of the operation of the proposed system.
+
+\begin{figure}[H]
+\begin{center}
+\resizebox {\columnwidth} {!} {\includegraphics{diagrams/overview.png}}
+\caption{Design and operation overview}
+\label{fig:overview}
+\end{center}
+\end{figure}
+
+\begin{enumerate}[label=\textbf{\arabic*}.]
+\item Two mobile nodes in close physical proximity create a transaction.
+\item The mobile nodes each publish their transaction to a Miner node.
+\item The Miner node distributes the transaction across the Miner network.
+\item One Miner node solves the proof-of-work for a block of transactions, and the new block of transactions is appended to the blockchain.
+\item A mobile node requests verification from a Verifier node (request structure is explained in section \ref{ssec:verification}).
+\item The Verifier node uses the public blockchain to examine the requesting node's transactions and determine their validity.
+\item The Verifier accepts or rejects the  mobile node's claimed location based on its transactions in the blockchain. 
+\end{enumerate}
 
@@
 In order to preserve user's privacy, a user will only ever use an identity for one transaction, before generating a new one.
-This prevents malicious users from watching the public blockchain for a known identity and tracking it.
-However, to prevent identity theft, it is important for the verifier to be able to prove that a node was the original creator of each identity.
-This is achieved using a public/private key pair for each node.
+This prevents curious users from watching the public blockchain for a known identity and tracking it.
+However, to prevent identity theft, it is important for the Verifier to be able to prove that a mobile node is the owner of each identity.
+This is achieved using a public/private key pair for each mobile node.
 
-% add nonces and PK verification to the verify_request diagram! and discuss them below!
+When a mobile node is created, it generates a public/private key pair.
+To maintain anonymity, the mobile node will use the public key to encrypt \textit{nonces} to create \textit{identities}, and use these to identify itself in a transaction.
+A different identity will be created for each transaction.
+During the verification stage, the node will provide the Verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions (see figure \ref{fig:verify_request}).
+This allows the Verifier to calculate all of the node's identities, and prove that they were all created by the same node, and can then retrieve the transactions associated with those identities from the blockchain.
+The Verifier will also ensure that the node owns the private key associated with the provided public key, to prevent identity theft.
 
-When a node is created, it generates a key pair.
-To maintain anonymoty, the node will use the public key to encrypt some nonces to create identities, and use these identify itself in a transaction.
-During the verification stage, the node will provide the verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions.
-The verifier calculates the node's identities using the public key and nonces, and retrieves the relevant transactions from the public blockchain.
-The verifier will also ensure that the node owns the private key associated with the provided public key, to prevent identity theft.
+\subsubsection{Nonce list} \label{sssec:nonce_list}
+A \textit{Nonce List} is simply a list of all of the nonces a mobile node has used so far to generate identities.
+When a mobile node generates a new identity, it must first generate a new nonce which is then encrypted to create the identity.
+The nonce is appended to the mobile node's nonce list, so it can be used later during verification (see section \ref{ssec:verification}).
 
+\subsubsection{Identity duplication}
+Since all identities are generated from random nonces, there is nothing to stop two nodes from generating the same identity and using it in different transactions.
+It is therefore possible that during verification, a Verifier node may find multiple transactions with the same ID in the blockchain.
+The Verifier will have a decryption key for the transaction it is searching for, which will only be able to decrypt one of the transactions with the duplicate ID.
+The Verifier will try to decrypt each one until it finds one that can be decrypted successfully.
+
+\newpage
 \subsection{Transactions} \label{sec:transactions}
 During a transaction between two nodes, a number of different items must be shared and calculated.
-Figure \ref{fig:transaction} describes an honest, successful transaction, assuming an ad-hoc bluetooth network has already been set up between nodes $A$ and $B$.
+Figure \ref{fig:transaction} describes an honest, successful transaction, assuming an ad-hoc Bluetooth network has already been set up between nodes $A$ and $B$.
 
-\begin{figure}[h]
+\begin{figure}[H]
 \resizebox {\columnwidth} {!} {\input{diagrams/transaction.tex}}
@@
 \begin{itemize}[noitemsep,topsep=0pt]
-	\item[] $\mathbf{NL_A[n]}$ is the $n$th nonce in $A$'s \textit{Nonce List}, which is used to generate $ID_{An}$.
+	\item[] $\mathbf{NL_A[n]}$ is the $n$th nonce in $A$'s \textit{Nonce List}, which is used to generate $ID_{An}$ (see section \ref{sssec:nonce_list}).
 \end{itemize}
@@
 
-After creating an ad-hoc bluetooth network between nodes $A$ and $B$, the first step in the transaction is for both nodes to share their IDs, and agree upon a GPS location and current time.
+After creating an ad-hoc Bluetooth network between nodes $A$ and $B$, the first step in the transaction is for both nodes to share their IDs, and agree upon a GPS location and current time.
 Nodes likely won't share the exact same GPS coordinates or time, but once the values don't differ by more than some small constant $\epsilon$, the nodes will continue with the transaction.
@@
 	\item[] $\mathbf{n}$ is node $A$'s current transaction number (i.e. $A$ has published $n-1$ transactions before now).
+	\item[] $\mathbf{KL_{AT}}$ is one of $A$'s \textit{Key Lists}, used to encrypt transactions.	
 	\item[] $\mathbf{ts}$ is the timestamp of the transaction, as recorded by node $A$.
 	\item[] $\mathbf{loc}$ is the GPS coordinates of the transaction, as recorded by node $A$.
-	\item[] $\mathbf{KL_{AT}}$ is one of $A$'s \textit{Key Lists}, used to encrypt transactions.
+	\item[] $\mathbf{ID_{An}}$ is $A$'s $nth$ identity, used for this transaction only.
 	\item[] $\mathbf{KP_{Bm}}$ is $B$'s \textit{Key Packet} at time $m$. Its exact contents are discussed in more detail in section \ref{sssec:key_packets}
@@
 \subsubsection{Publishing to the blockchain}
-After creating $T_{An}$, node $A$ needs to publish it to the public blockchain.
-The data published must be identifiablein order to provide a verifier with some way of identifying specific transactions.
-Nodes will use their current ID as the identifier for the transaction.
+After creating $T_{An}$, node $A$ must publish it to the public blockchain.
+The data published must be searchable in order to provide a Verifier with some way of identifying specific transactions.
+Nodes use their current ID as the identifier for the transaction.
 
-Backwards-chaining is an important part of verifiability.
-The verifier must be able to prove that the proof chain provided by the node has not had its order altered.
+\textit{Backwards-chaining} is an important part of verifiability.
+The Verifier must be able to prove that the proof chain provided by the mobile node has not been chronologically re-ordered.
 The transaction must therefore be accompanied by a link to the node's chronologically previous transaction.
-This link must be encrypted, otherwise a malicious user monitoring the public blockchain could monitor a user's transaction publishing activity.
+This link must be encrypted, along with the transaction timestamp, to prevent a curious user from monitoring the public blockchain to observe a user's transaction publishing activity.
 $A$'s copy of the transaction log $P_{An}$ will therefore be in the form:
@@
 \subsubsection{Key Packets} \label{sssec:key_packets}
-The key packet is more than simply a list of keys that $B$ has used to encrypt his transactions; in order to preserve the ``selective in-sequence privacy'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt.
+The key packet is more than simply a list of keys that a mobile node has used to encrypt its transactions; in order to preserve the ``selective in-sequence privacy'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt.
 However, in order to simultaneously preserve OTIT's ``privacy protected chronology'' property, the transaction backwards-chaining must not be broken.
-This is why two separate \textit{Key Lists} are maintained; $KL_{AL}$ is used to encrypt the backwards-chaining link, while $KL_{AT}$ encrypts the transaction data.
+This is why two separate \textit{Key Lists} are maintained; $KL_{AL}$ is used to encrypt the backwards-chaining link and transaction timestamp, while $KL_{AT}$ encrypts the transaction data.
 For example, if node $B$ doesn't want to reveal transaction $T_{Bm-1}$, he would reveal the following key packet:
@@
 In this case, $KL_{BT}[m-1]$ has not been included with $KL_{BL}[m-1]$, in order to protect the privacy of this transaction.
-This may be needed, for example, if node $B$ doesn't want to allow anyone to decrypt any transactions he has created withing 5Km of his home, in order to protect his privacy.
+This may be needed, for example, if node $B$ doesn't want to allow anyone to decrypt any transactions he has created withing 5km of his home, in order to protect his privacy.
 
@@
 In figure \ref{fig:aborted_transaction}, node $A$ encounters a malicious node $M$, who tries to spoof its identity with $A$.
-Node $A$ will abort the transaction once it notices that $|ts_A-ts_M| < \epsilon_{ts}$, or $|loc_A-loc_M| < \epsilon_{loc}$.
+Node $A$ will abort the transaction once it notices that $|ts_A-ts_M| \geq \epsilon_{ts}$, or $|loc_A-loc_M| \geq \epsilon_{loc}$.
 
@@
 This means that even if $M$ fabricates some data from $A$ and publishes a transaction onto the blockchain, the matching transaction from $A$ will not be present.
-Any transaction on the blockchain that does not reference the transaction of the alibi used to create it will be disregarded by any Verifiers.
+Any transaction on the blockchain that do not contain a reference to a valid  alibi transaction will be disregarded during verification.
 
@@
 
-\subsection{Verification}
+\subsection{Verification} \label{ssec:verification}
 \begin{minipage}{0.5\linewidth}
-In the verification stage, a node tries to prove its location to a Verifier 3rd party, e.g.
+In the verification stage, a mobile node tries to prove its location to a Verifier node, e.g.
 a bank.
-To do this, the node sends the Verifier a number of parameters, as shown in Figure \ref{fig:verify_request}:
+To do this, the mobile node sends the Verifier a number of parameters, as shown in Figure \ref{fig:verify_request}:
 \begin{itemize}[noitemsep,topsep=0pt]
 	\item[] $\mathbf{ID_{An-1}}$ is the ID of $A$'s most recently published transaction.
-	\item[] $\mathbf{KP_{An-1}}$ is $A$'s key packet from transaction $n-1$, and includes keys for as many transactions as $A$ feels is apropriate in order to receive verification.
-	\item[] $\mathbf{loc}$ is $A$'s current claimed location for which it is seeking verification.
-	\item[] $\mathbf{NP_{An-1}}$ is $A$'s \textit{Nonce Packet}, a list of the nonces used to generate $A$'s most recent IDs, from $n-1$.	
+	\item[] $\mathbf{KP_{An-1}}$ is $A$'s key packet up to transaction $n-1$, and includes keys for as many transactions as $A$ feels is appropriate in order to receive verification.
+	\item[] $\mathbf{loc}$ is $A$'s current claimed GPS coordinates for which it is seeking verification.
+	\item[] $\mathbf{NP_{An-1}}$ is $A$'s \textit{Nonce Packet}, a subset of its \textit{Nonce List} (section \ref{sssec:nonce_list}).
+A Nonce Packet is the list of the nonces used to generate $A$'s most recent IDs, up to $n-1$., that $A$ is willing to share with the Verifier.
 \end{itemize}
@@
 
-There are a huge number of possible factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain verifiers, and kept secret to improve reliability and avoid gaming.
+There are a huge number of possible factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain Verifiers, and kept secret to improve reliability and avoid gaming.
 Some simple example factors may include:
 \begin{itemize}
-	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, then the node is likely attempting a poorly-constructed Sybil attack, and the verifier will reject his verification request.
-	\item \textbf{Alibi reuse:} if the verifier can prove that alibi’s are being reused frequently, then it will reject the verification request.
+	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, then the node is likely attempting a poorly-constructed Sybil attack, and the Verifier will reject his verification request.
+	\item \textbf{Alibi reuse:} if the Verifier can prove that alibi’s are being reused frequently, then it will reject the verification request.
 	\begin{itemize}
-		\item Due to transaction anonymity, the verifier may not always be able to tell if two alibi's are the same person or not.
+		\item Due to transaction anonymity, the Verifier may not always be able to tell if two alibi's are the same person or not.
 e.g.
@@
 \end{itemize}
-
-\subsection{Sybil attack}
-This system is vulnerable to a Sybil attack, where a single physical node may create multiple \textit{pseudoidentities} \cite{sybil}.
-A suitably powerful node, or motivated attacker, could create enough pseudonyms to create a subnetwork of nodes, each creating malicious transactions with each other.
-This would allow an attacker to falsify a believable location proof.
-
-It has been proven that a central certificate authority is the only method of preventing a Sybil attack \cite{sybil}.
-Other measures, such as web of trust, increase the difficulty involved in performing an attack, but the system remains vulnerable to a motivated attacker.
 
@@
 \item[] \textbf{Privacy protected chronology}: This states that the proof system, which provides \textit{selective in-sequence privacy}, should also ensure that the user does not ``hide away'' important items within the subset.
-This is impossibnle in our system due to the use of backwards chronological linking between transactions, so our model satisfies this property.
+This is impossible in our system due to the use of backwards chronological linking between transactions, so our model satisfies this property.
 
@@
 \end{enumerate}
+
+\subsection{Attacks on the system}
+\subsubsection{Identity replication}
+By repeatedly publishing fake transactions with the same ID, a malicious user can impede the Verification of certain transactions.
+This is because a Verifier will have to attempt to decrypt all transactions with the same ID until it finds one that decrypts successfully.
+A malicious user can therefore slow down the verification stage of certain transactions by flooding the blockchain with transactions with the same ID.
+
+This is an abuse of the system than an attack.
+A malicious user will not be able to target specific users' transactions, because they are privacy protected.
+The malicious user can therefore gain no material advantage or compromise the security of the system by using an attack like this.
+
+To avoid this attack, Miner nodes may reject any transactions with duplicate transaction IDs.
+Assuming sufficiently large transaction IDs, a duplicate ID is unlikely to happen through honest operation.
+Miners can assume that any transactions with duplicate IDs are malicious, and reject them.
+
+\subsubsection{Sybil attack}
+This system is vulnerable to a Sybil attack, where a single physical node may create multiple \textit{pseudoidentities} \cite{sybil}.
+A suitably powerful node, or motivated attacker, could create enough pseudonyms to create a subnetwork of nodes, each creating malicious transactions with each other.
+This would allow an attacker to falsify a believable location proof.
+
+It has been proven that a central certificate authority is the only method of preventing a Sybil attack \cite{sybil}.
+Other measures, such as web of trust, increase the difficulty involved in performing an attack, but the system remains vulnerable to a motivated attacker.
 

### 2016-03-30 thesis/design.tex
updating thesis to match paper

--- 2016-03-30 paper.tex
@@
-\title{Decentralised location proof system}
-
-\documentclass[12pt]{article}
-
-\usepackage{tikz}
-\usetikzlibrary{calc,arrows}
-\usepackage{enumitem}
-\usepackage{float}
-\usepackage{enumitem}
-
-\setlist{parsep=0pt,listparindent=\parindent}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-\end{abstract}
-
-\section{Introduction}
-
-\section{Previous work}
-Location proof systems are expected to be accurate and tamper-proof. For this reason, existing solutions have chosen to use a central authority to issue proofs \cite{brassil, luo, khan}.
-
-Hardware techniques \cite{brassil} operate by supplementing existing Wi-Fi access points with \textit{femtocells} (small cellular antennae that connect to the mobile carrier via the Internet).
-Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data via Wi-Fi.
-This solution requires investment in additional hardware to supplement existing Wi-Fi access points.
-It also requires access to mobile providers user database to identify users locations.
-
-Other proof systems \cite{luo} deploy software on Wi-Fi access points.
-Access points taking part in the location proof network become part of a 'group' with a shared group signature.
-Mobile nodes can request a location proof from an access point, who signs it with the group signature.
-Access points provide location proofs to nodes without ever learning the node's identity, thus protecting user's privacy.
-However, due to the systems reliance on the group signature structure, access points become a target for attack.
-Compromising an access point would allow an attacker to create false location proofs.
-
-\cite{luo} considers a number of threats in their architecture:
-\begin{itemize}
-	\item \textbf{Dishonest users.} A dishonest user tries to obtain location proofs that certify her presence at some place at a particular time even if she was not there.
-Dishonest users may achieve this goal by colluding with malicious intruders.
-	\item \textbf{Malicious intruders.} A malicious intruder is not interested in obtaining location proofs for her own use but offers to help other users to get location proofs on their behalf in exchange for other benefits like money.
-	\item \textbf{Curious APs and applications.} A curious AP tries to learn a users identity while the user is acquiring a location proof from the AP.
-Similarly, a curious application tries to learn more location information from a location proof than it really needs.
-	\item \textbf{Malicious applications.} A malicious application obtains location proofs from its users and then tries to take advantage of these proofs to get unauthorised access to other applications.
-	\item \textbf{Active and passive eavesdroppers.} An eavesdropper records and maybe modifies communication between users, proof- issuers, or applications.
-\end{itemize}
-
-Distributed P2P location proof systems also exist \cite{khan}.
-A central authority is used and acts as a certificate authority, issuing a unique ID to each person using the system.
-Unique identity is proved by users by providing SSN, drivers licence, or passport documents.
-This removes the threat of a Sybil attack \cite{sybil}, but makes the central authority a clear target for attack.
-The system uses three parties to provide location proofs; a mobile user who requests a proof, a fixed location authority, and a mobile user who acts as a witness.
-The system becomes vulnerable in the case where all three users collude, but is otherwise quite an interesting approach.
-
-\cite{khan} also outlines a number of possible attacks on their system:
-\begin{itemize}
-	\item \textbf{False presence:} A malicious user can create a fake location proof on his own, without being physically present at the location.
-The fake proof is supposed to resemble an actual proof, which the user could have actually collected from a valid location authority.
-	\item \textbf{False timestamping (backdating, future dating):} In a backdating attack, the user and the location authority colludes to create a proof for a past time.
-Conversely, in future dating, the location authority and a user colludes to generate a proof with a future timestamp.
-	\item \textbf{Implication:} A location authority and/or a witnesses can falsely accuse a user of his presence at a certain location.
-In this case, the malicious location authority and witness colludes to generate a false proof of presence for the user.
-	\item \textbf{False assertion:} A user can collude with a witness, and generate a falsely asserted location proof.
-The truth value in such a fake proof is reinstated with the assertion received from the other user.
-	\item \textbf{Denial of presence:} A user can visit a location and at a later time, deny his presence at that location.
-In such a case, the user actually denies the validity of a certain location proof that has been been generated upon his presence at that particular location.
-	\item \textbf{Proof switching:} The user is expected to have full access to all storage facilities on his mobile device.
-Hence, the user utilizes the legitimate proof and manipulates the information to create a false proof for a different location.
-	\item \textbf{Relay attack:} A user can use a proxy to relay the requests and collect a location proof.
-Alternatively, a location authority can maliciously relay assertion requests with the witness not being present at the site.
-	\item \textbf{Sybil attack:} A Sybil attack occurs when a single user generates multiple presence and identities [29].
-A user can launch a Sybil attack by generating multiple identities representing a user and a witness and provide false endorsements for location proofs.
-	\item \textbf{Denial of witnesses presence:} At the time of proof verification, the user can claim the absence of witnesses at the site or falsely claim an assertion to be counterfeit.
-The user and the location authority may also collude and claim the non-availability of witnesses.
-	\item \textbf{Privacy violation:} An attacker may capture an asserted location proof generated for a user, and discover the identity of the user and/or the witness.
-\end{itemize}
-
-'OTIT' \cite{otit}, a model for designing secure location provenance, can be used to compare existing location proof systems.
-This model defines the following requirements necessary for designing any secure location provenance scheme: Chronological, Order Preserving, Verifiable, Tamper Evident, Privacy Preserved, Selective In-Sequence Privacy, Privacy Protected Chronology, and Convenience \& Derivability.
-
-\newpage
 \section{Design}
@@
 \end{itemize}
-
-\newpage
-\section{Evaluation}
-In this paper, we have presented a model for a location proof system which aims to preserve privacy and prevent false proofs from being created.
-
-\subsection{OTIT conformance}
-We can compare our model to OTIT \cite{otit}, a list of features and requirements necessary for designing any secure location proof scheme. OTIT presents 8 such requirements:
-\begin{enumerate}
-\item[] \textbf{Chronological}: The chronological property of OTIT ensures that transactions are published in the order they were created.
-In our system we do not enforce this property at the time of transaction publication.
-This is to avoid revealing any transaction information to the miner nodes, therefore preserving the privacy of the transaction owner.
-Instead, we enforce this property at the time of verification.
-The chronological link created by adding $KL_{AT}(ID_{A-1}|ts_A)$ to the transaction will allow Verifier nodes to prove that the transaction is chronologically ordered, preserving OTIT's ``Chronological'' property.
-
-\item[] \textbf{Order preserving}: This property states that the order of transactions cannot be modified after they are created.
-In our system, a blockchain is used to store transactions.
-In a blockchain, new blocks are added in a linear, chronological order, and cannot be modified so long as the majority of miners in the network are honest \cite{blueprint}.
-Therefore the transactions stored in these blocks satisfy the ``Order preserving'' property of OTIT.
-% in the dissertation i can discuss ordering within a block here (and go into detail about the merkle root etc)
-
-\item[] \textbf{Verifiable}: This states that the proof, and the order or proofs, should be verifiable by a trusted auditor.
-In our case, a Verifier node is an auditor trusted by the mobile node seeking verification.
-A Verifier node may be operated by a bank, government, or any entity wishing to make use of our location proof system.
-
-Our system inherently satisfies this property of OTIT, as Verifier nodes are required to verify or reject a mobile node's claimed location.
-This is done by examining the mobile node's chronological link of transactions, and recursing for each alibi used for each transaction along the chronological link until the Verifier can conclude if the transaction chain is valid or not.
-
-\item[] \textbf{Tamper evident}: Our system is tamper evident.
-If a malicious node creates a successful transaction with an honest node, but modifies the transaction data before publishing, a Verifier node will reject the malicious transaction.
-This rejection will be on the grounds that the matching transaction, published by the honest node, contains contradictory data.
-
-We assume the underlying security of the blockchain, so any malicious miner nodes will not be able to tamper with existing transaction data providing that the majority of CPU power in the mining system is owned by honest miners \cite{bitcoin}.
-Therefore the tamper evident property is satisfied.
-
-\item[] \textbf{Privacy preserved}: This states that the user should have control over his level of privacy exposure when using the system.
-In our system, this is provided using \textit{Key Lists} \ref{sec:transactions}.
-We provide two keys for each transaction; $KL_{AT}[n]$ is used to encrypt the \textit{transaction data} for $A$'s $nth$ transaction, and $KL_{AL}[n]$ is used to encrypt the \textit{backwards chronological link} between $A$'s $nth$ transaction and transaction $n-1$.
-
-To control his privacy, a user can choose only to reveal $KL_{AL}[n]$ for a specific transaction $n$.
-This may be useful if a user does not wish to reveal transaction data for transactions created within a certain distance of his house, for example.
-Hiding $KL_{AT}[n]$ while revealing $KL_{AL}[n]$ has the advantage of preserving the user's privacy while maintaining a clear backwards chronological link of transactions for the Verifier to follow, preserving both privacy and system consistency.
-
-\item[] \textbf{Selective in-sequence privacy}: This is the requirement that any proof chain must support \textit{sub-set verification}, allowing a user to provide only a sub-set of proofs from his current proof chain for verification.
-Our system satisfies this property by using \textit{Key Packets} (section \ref{sssec:key_packets}).
-
-In our system, a \textit{sub-set} of $A$'s proof chain can be defined as $KP_{An}$.
-The sub-set therefore begins with $ID_{An}$, and ends when there is no key $KL_{AL}[n-m]$ in $KP_{An}$ to decrypt the link to transaction $T_{An-m-1}$.
-
-\item[] \textbf{Privacy protected chronology}: This states that the proof system, which provides \textit{selective in-sequence privacy}, should also ensure that the user does not ``hide away'' important items within the subset.
-This is impossible in our system due to the use of backwards chronological linking between transactions, so our model satisfies this property.
-
-\item[] \textbf{Convenience and derivability}: This requirement states that the verification process should be convenient, and the user should not burden the Verifier node with a huge load of data.
-In our system, the data is stored in a central blockchain that the Verifier has access to, and the user provides the Verifier only with decryption keys and indexes into a sub-section of this data.
-Therefore the data sent to from the user to the Verifier, $KP_{An}$, is quite small in size.
-
-The Verifier has the freedom to decide how comprehensively to investigate the user's data; It can bound how deeply to investigate the graph of alibi's, if at all.
-We therefore satisfy this requirement by allowing the Verifier to choose how complex the verification process needs to be.
-\end{enumerate}
-
-\subsection{Attacks on the system}
-\subsubsection{Identity replication}
-By repeatedly publishing fake transactions with the same ID, a malicious user can impede the Verification of certain transactions.
-This is because a Verifier will have to attempt to decrypt all transactions with the same ID until it finds one that decrypts successfully.
-A malicious user can therefore slow down the verification stage of certain transactions by flooding the blockchain with transactions with the same ID.
-
-This is an abuse of the system than an attack.
-A malicious user will not be able to target specific users' transactions, because they are privacy protected.
-The malicious user can therefore gain no material advantage or compromise the security of the system by using an attack like this.
-
-To avoid this attack, Miner nodes may reject any transactions with duplicate transaction IDs.
-Assuming sufficiently large transaction IDs, a duplicate ID is unlikely to happen through honest operation.
-Miners can assume that any transactions with duplicate IDs are malicious, and reject them.
-
-\subsubsection{Sybil attack}
-This system is vulnerable to a Sybil attack, where a single physical node may create multiple \textit{pseudoidentities} \cite{sybil}.
-A suitably powerful node, or motivated attacker, could create enough pseudonyms to create a subnetwork of nodes, each creating malicious transactions with each other.
-This would allow an attacker to falsify a believable location proof.
-
-It has been proven that a central certificate authority is the only method of preventing a Sybil attack \cite{sybil}.
-Other measures, such as web of trust, increase the difficulty involved in performing an attack, but the system remains vulnerable to a motivated attacker.
-
-\section{Conclusions}
-
-\begin{thebibliography}{9}
-
-\bibitem{brassil}
-  J. Brassil, P.K. Manadhata,
-  ``Verifying the Location of a Mobile Device User'',
-  Proc. of MobiSec 2012,
-  June 2012.
-
-\bibitem{luo}
-  Luo, W., Hengartner, U.,
-  ``Proving your Location without giving up your Privacy'',
-  Proceedings of the Eleventh Workshop on Mobile Computing Systems \& Applications,
-  HotMobile 2010, Annapolis, Maryland, February 22 - 23, pp. 7–12. ACM,
-  New York (2010)
-
-\bibitem{khan}
-  R. Khan, S. Zawoad, M. M. Haque, and R. Hasan,
-  ```Who, When, and Where?' Location Proof Assertion for Mobile Devices'',
-  Proceedings of the 28th Annual IFIP WG 11.3 Working Conference on Data and Applications Security and Privacy, ser. DBSec. IFIP,
-  July 2014.
-
-\bibitem{otit}
-  Khan, R., Zawoad, S., Haque, M., Hasan, R.
-  ``OTIT: Towards secure provenance modeling for location proofs'',
-  Proc. of ASIACCS. ACM (2014)
-
-\bibitem{sybil}
-  Douceur, J.R.,
-  ``The sybil attack'',
-  Druschel, P., Kaashoek, M.F., Rowstron, A. (eds.) IPTPS 2002. LNCS, vol. 2429, pp. 251–260,
-  Springer, Heidelberg (2002)
-
-\bibitem{location-spoof}
-  N. O. Tippenhauer, K. B. Rasmussen, C. Popper, and S. Capkun,
-  ``iPhone and iPod location spoofing: Attacks on public WLAN-based positioning systems'',
-  SysSec Technical Report,
-  ETH Zurich, April, 2008
-
-\bibitem{blueprint}
-  M. Swan,
-  ``Blockchain: Blueprint for a New Economy'',
-  Sebastopol, CA,
-  O’Reilly Media, 2015
-
-\bibitem{bitcoin}
-  S. Nakamoto,
-  ``Bitcoin: A Peer-to-Peer Electronic Cash System'',
-  2008
-
-\end{thebibliography}
-
-\end{document}

### 2016-03-30 thesis/evaluation.tex
updating thesis to match paper

--- 2016-03-22 paper.tex
@@
-\title{Decentralised location proof system}
-
-\documentclass[12pt]{article}
-
-\usepackage{tikz}
-\usetikzlibrary{calc,arrows}
-\usepackage{enumitem}
-\usepackage{float}
-\usepackage{enumitem}
-
-\setlist{parsep=0pt,listparindent=\parindent}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-\end{abstract}
-
-\section{Introduction}
-
-\section{Previous work}
-Location proof systems are expected to be accurate and tamper-proof. For this reason, existing solutions have chosen to use a central authority to issue proofs \cite{brassil, luo, khan}.
-
-Hardware techniques \cite{brassil} operate by supplementing existing WiFi access points with \textit{femtocells} (small cellular antennae that connect to the mobile carrier via the Internet).
-Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data via Wi-Fi.
-This solution requires investment in additional hardware to supplement existing WiFi access points.
-It also requires access to mobile providers user database to identify users locations.
-
-Other proof systems \cite{luo} deploy software on Wi-Fi access points.
-Access points taking part in the location proof network become part of a 'group' with a shared group signature.
-Mobile nodes can request a location proof from an access point, who signs it with the group signature.
-Access points provide location proofs to nodes without ever learning the node's identity, thus protecting user's privacy.
-However, due to the system’s reliance on the group signature structure, access points become a target for attack.
-Compromising an access point would allow an attacker to create false location proofs.
-
-\cite{luo} considers a number of threats in their architecture:
-\begin{itemize}
-	\item \textbf{Dishonest users.} A dishonest user tries to obtain location proofs that certify her presence at some place at a particular time even if she was not there.
-Dishonest users may achieve this goal by colluding with malicious intruders.
-	\item \textbf{Malicious intruders.} A malicious intruder is not interested in obtaining location proofs for her own use but offers to help other users to get location proofs on their behalf in exchange for other benefits like money.
-	\item \textbf{Curious APs and applications.} A curious AP tries to learn a user’s identity while the user is acquiring a location proof from the AP.
-Similarly, a curious application tries to learn more location information from a location proof than it really needs.
-	\item \textbf{Malicious applications.} A malicious application obtains location proofs from its users and then tries to take advantage of these proofs to get unauthorised access to other applications.
-	\item \textbf{Active and passive eavesdroppers.} An eavesdropper records and maybe modifies communication between users, proof- ssuers, or applications.
-\end{itemize}
-
-Distributed P2P location proof systems also exist \cite{khan}.
-A central authority is used and acts as a certificate authority, issuing a unique ID to each person using the system.
-Unique identity is proved by users by providing SSN, driver’s licence, or passport documents.
-This removes the threat of a Sybil attack \cite{sybil}, but makes the central authority a clear target for attack.
-The system uses three parties to provide location proofs; a mobile user who requests a proof, a fixed location authority, and a mobile user who acts as a witness.
-The system becomes vulnerable in the case where all three users collude, but is otherwise quite an interesting approach.
-
-\cite{khan} also outlines a number of possible attacks on their system:
-\begin{itemize}
-	\item \textbf{False presence:} A malicious user can create a fake location proof on his own, without being physically present at the location.
-The fake proof is supposed to resemble an actual proof, which the user could have actually collected from a valid location authority.
-	\item \textbf{False timestamping (backdating, future dating):} In a backdating attack, the user and the location authority colludes to create a proof for a past time.
-Conversely, in future dating, the location authority and a user colludes to generate a proof with a future timestamp.
-	\item \textbf{Implication:} A location authority and/or a witnesses can falsely accuse a user of his presence at a certain location.
-In this case, the malicious location authority and witness colludes to generate a false proof of presence for the user.
-	\item \textbf{False assertion:} A user can collude with a witness, and generate a falsely asserted location proof.
-The truth value in such a fake proof is reinstated with the assertion received from the other user.
-	\item \textbf{Denial of presence:} A user can visit a location and at a later time, deny his presence at that location.
-In such a case, the user actually denies the validity of a certain location proof that has been been generated upon his presence at that particular location.
-	\item \textbf{Proof switching:} The user is expected to have full access to all storage facilities on his mobile device.
-Hence, the user utilizes the legitimate proof and manipulates the information to create a false proof for a different location.
-	\item \textbf{Relay attack:} A user can use a proxy to relay the requests and collect a location proof.
-Alternatively, a location authority can maliciously relay assertion requests with the witness not being present at the site.
-	\item \textbf{Sybil attack:} A Sybil attack occurs when a single user generates multiple presence and identities [29].
-A user can launch a Sybil attack by generating multiple identities representing a user and a witness and provide false endorsements for location proofs.
-	\item \textbf{Denial of witness’s presence:} At the time of proof verification, the user can claim the absence of witnesses at the site or falsely claim an assertion to be counterfeit.
-The user and the location authority may also collude and claim the non-availability of witnesses.
-	\item \textbf{Privacy violation:} An attacker may capture an asserted location proof generated for a user, and discover the identity of the user and/or the witness.
-\end{itemize}
-
-'OTIT' \cite{otit}, a model for designing secure location provenance, can be used to compare existing location proof systems.
-This model defines the following requirements necessary for designing any secure location provenance scheme: Chronological, Order Preserving, Vereifiable, Tamper Evident, Privacy Preserved, Selective In-Sequence Privacy, Privacy Protected Chronology, and Convenience \& Derivability.
-
-\newpage
-\section{Design}
-The location proof system we propose allows mobile nodes to create location proofs for each other after physically meeting.
-When two nodes are in close physical proximity, they initiate a transaction over a short range, ad-hoc network such as bluetooth.
-
-To create a transaction, two nodes anonymously agree upon their location and current time over a short-range network.
-Once both nodes agree upon these parameters, they each create an encrypted, privacy-protecting transaction logging their location and the alibi used to create the transaction.
-This transaction is published onto a public, append-only bulletin board known as a \textit{blockchain}.
-Once given permission and decryption keys from a node, a \textit{verifier} can determine whether or not the node is present at its claimed location.
-
-Any node acting as an alibi in a transaction will share details of its most recent transactions with the other node in the transaction.
-This allows the verifier to be given permission to check the authenticity of all recent alibi's, and each of the alibi's recent alibi's, etc.
-Only the owner of the transaction can give permission to a verifier to check its location history, by providing the verifier with the keys needed to decrypt the transactions.
-
-\subsection{Identities}
-In order to preserve user's privacy, a user will only ever use an identity for one transaction, before generating a new one.
-This prevents malicious users from watching the public blockchain for a known identity and tracking it.
-However, to prevent identity theft, it is important for the verifier to be able to prove that a node was the original creator of each identity.
-This is achieved using a public/private key pair for each node.
-
-% add nonces and PK verification to the verify_request diagram! and discuss them below!
-
-When a node is created, it generates a key pair.
-To maintain anonymoty, the node will use the public key to encrypt some nonces to create identities, and use these identify itself in a transaction.
-During the verification stage, the node will provide the verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions.
-The verifier calculates the node's identities using the public key and nonces, and retrieves the relevant transactions from the public blockchain.
-The verifier will also ensure that the node owns the private key associated with the provided public key, to prevent identity theft.
-
-\subsection{Transactions} \label{sec:transactions}
-During a transaction between two nodes, a number of different items must be shared and calculated.
-Figure \ref{fig:transaction} describes an honest, successful transaction, assuming an ad-hoc bluetooth network has already been set up between nodes $A$ and $B$.
-
-\begin{figure}[h]
-\resizebox {\columnwidth} {!} {\input{diagrams/transaction.tex}}
-\caption{Honest, successful transaction}
-\label{fig:transaction}
-\end{figure}
-
-Where:
-\begin{itemize}[noitemsep,topsep=0pt]
-	\item[] $\mathbf{NL_A[n]}$ is the $n$th nonce in $A$'s \textit{Nonce List}, which is used to generate $ID_{An}$.
-\end{itemize}
-
-\null
-When a node is initialised, it must begin to record two \textit{Key Lists} for itself.
-A \textit{Key List} is a list of encryption keys previously used for transactions.
-For example, $KL_{AT}[n]$ and $KL_{AL}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively.
-These \textit{Key Lists} and are assumed to have been initialised and populated before the transaction described in Figure \ref{fig:transaction} begins.
-
-After creating an ad-hoc bluetooth network between nodes $A$ and $B$, the first step in the transaction is for both nodes to share their IDs, and agree upon a GPS location and current time.
-Nodes likely won't share the exact same GPS coordinates or time, but once the values don't differ by more than some small constant $\epsilon$, the nodes will continue with the transaction.
-If node $A$ claims a GPS location or timestamp that differs from what node $B$ senses by more than $\epsilon$, node $B$ will abort the transaction.
-
-After nodes agree upon the parameters of the transaction, they exchange their previous ID, along with their \textit{Key Packets}.
-A \textit{Key Packet} is a list of keys used in a node's $n$ most recent transactions, along with the transaction ID's if necessary.
-This allows node $A$ to decrypt node $B$'s $m$ most recent transactions, therefore providing an alibi for node $A$.
-
-\subsubsection{Transaction creation}
-Once nodes have exchanged \textit{Key Packets}, their communication is finished and they can close their ad-hoc channel.
-Each node creates a new transaction object, $T$, to publish onto the public blockchain.
-The following transaction data will be calculated by node $A$, after communicating with node $B$:
-\\
-
-$T_{An} = KL_{AT}[n](ts|loc|ID_{An}|KP_{Bm})$
-\\
-
-Where:
-\begin{itemize}[noitemsep,topsep=0pt]
-	\item[] $\mathbf{n}$ is node $A$'s current transaction number (i.e. $A$ has published $n-1$ transactions before now).
-	\item[] $\mathbf{ts}$ is the timestamp of the transaction, as recorded by node $A$.
-	\item[] $\mathbf{loc}$ is the GPS coordinates of the transaction, as recorded by node $A$.
-	\item[] $\mathbf{KL_{AT}}$ is one of $A$'s \textit{Key Lists}, used to encrypt transactions.
-	\item[] $\mathbf{KP_{Bm}}$ is $B$'s \textit{Key Packet} at time $m$. Its exact contents are discussed in more detail in section \ref{sssec:key_packets}
-\end{itemize}
-
-\subsubsection{Publishing to the blockchain}
-After creating $T_{An}$, node $A$ needs to publish it to the public blockchain.
-The data published must be identifiablein order to provide a verifier with some way of identifying specific transactions.
-Nodes will use their current ID as the identifier for the transaction.
-
-Backwards-chaining is an important part of verifiability.
-The verifier must be able to prove that the proof chain provided by the node has not had its order altered.
-The transaction must therefore be accompanied by a link to the node's chronologically previous transaction.
-This link must be encrypted, otherwise a malicious user monitoring the public blockchain could monitor a user's transaction publishing activity.
-$A$'s copy of the transaction log $P_{An}$ will therefore be in the form:
-\\
-
-$P_{An} = ID_{An}|KL_{AL}[n](ID_{An-1}|ts_A)|T_{An}$
-
-\null
-To publish $P_{An}$, $A$ must send $P_{An}$ to a miner node, who will add it to its \textit{pending transaction} queue, and send it to other miners in the network to add it to their queues as well.
-The transaction will then be signed into the next block in the blockchain.
-
-\subsubsection{Key Packets} \label{sssec:key_packets}
-The key packet is more than simply a list of keys that $B$ has used to encrypt his transactions; in order to preserve the ``selective in-sequence privacy'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt.
-However, in order to simultaneously preserve OTIT's ``privacy protected chronology'' property, the transaction backwards-chaining must not be broken.
-This is why two separate \textit{Key Lists} are maintained; $KL_{AL}$ is used to encrypt the backwards-chaining link, while $KL_{AT}$ encrypts the transaction data.
-For example, if node $B$ doesn't want to reveal transaction $T_{Bm-1}$, he would reveal the following key packet:
-\\
-
-${KP_{Bm} = (\{KL_{BL}[m], KL_{BT}[m]\}, KL_{BL}[m-1], \{KL_{BL}[m-2], KL_{BT}[m-2]\})}$
-
-\null
-In this case, $KL_{BT}[m-1]$ has not been included with $KL_{BL}[m-1]$, in order to protect the privacy of this transaction.
-This may be needed, for example, if node $B$ doesn't want to allow anyone to decrypt any transactions he has created withing 5Km of his home, in order to protect his privacy.
-
-\subsubsection{Aborting transactions}
-A node may decide to abort a transaction if it thinks it is in contact with a malicious node.
-In figure \ref{fig:aborted_transaction}, node $A$ encounters a malicious node $M$, who tries to spoof its identity with $A$.
-Node $A$ will abort the transaction once it notices that $|ts_A-ts_M| < \epsilon_{ts}$, or $|loc_A-loc_M| < \epsilon_{loc}$.
-
-To abort the transaction, $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain.
-This means that even if $M$ fabricates some data from $A$ and publishes a transaction onto the blockchain, the matching transaction from $A$ will not be present.
-Any transaction on the blockchain that does not reference the transaction of the alibi used to create it will be disregarded by any Verifiers.
-
-\begin{figure}[h]
-\resizebox {\columnwidth} {!} {\input{diagrams/aborted_transaction.tex}}
-\caption{An aborted transaction due to malicious node $M$}
-\label{fig:aborted_transaction}
-\end{figure}
-
-\subsection{Verification}
-\begin{minipage}{0.5\linewidth}
-In the verification stage, a node tries to prove its location to a Verifier 3rd party, e.g.
-a bank.
-To do this, the node sends the Verifier a number of parameters, as shown in Figure \ref{fig:verify_request}:
-\begin{itemize}[noitemsep,topsep=0pt]
-	\item[] $\mathbf{ID_{An-1}}$ is the ID of $A$'s most recently published transaction.
-	\item[] $\mathbf{KP_{An-1}}$ is $A$'s key packet from transaction $n-1$, and includes keys for as many transactions as $A$ feels is apropriate in order to receive verification.
-	\item[] $\mathbf{loc}$ is $A$'s current claimed location for which it is seeking verification.
-	\item[] $\mathbf{NP_{An-1}}$ is $A$'s \textit{Nonce Packet}, a list of the nonces used to generate $A$'s most recent IDs, from $n-1$.	
-\end{itemize}
-\end{minipage}
-\hfill
-\begin{minipage}[c]{0.5\linewidth}
-\begin{figure}[H]
-\input{diagrams/verify_request.tex}
-\caption{Verification request}
-\label{fig:verify_request}
-\end{figure}
-\end{minipage}
-
-The goal of the verification stage is for the Verifier to either accept or reject the location that the user is claiming.
-Given $ID_{An-1}$ and $KP_{An-1}$, a Verifier is able to retrieve $A$'s previous transactions, and the transactions of all of its alibi's.
-
-The Verifier uses $NP_{An-1}$ and $K^{+}_A$ to prove that node $A$ was the author of all of the transactions he claims to be.
-This prevents a collusion attack whereby nodes could share common transactions between different proof chains.
-When walking chronologically backwards along $A$'s proof chain, the 3rd party will ensure that the ID used in transaction $m$ on the proof chain matches $K^{+}_A(NP_{An-1}[m])$.
-
-There are a huge number of possible factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain verifiers, and kept secret to improve reliability and avoid gaming.
-Some simple example factors may include:
-\begin{itemize}
-	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, then the node is likely attempting a poorly-constructed Sybil attack, and the verifier will reject his verification request.
-	\item \textbf{Alibi reuse:} if the verifier can prove that alibi’s are being reused frequently, then it will reject the verification request.
-	\begin{itemize}
-		\item Due to transaction anonymity, the verifier may not always be able to tell if two alibi's are the same person or not.
-e.g.
-node $A$ could use node $B$ as an alibi, then wait for $B$ to complete $n$ more transactions, then use node $B$ again.
-		\item This is not a viable attack on the verification system.
-Depending on the size of $n$, enough time may pass between both uses of node $B$ as an alibi that the transactions are no longer relevant.
-	\end{itemize}
-\end{itemize}
-
-\subsection{Sybil attack}
-This system is vulnerable to a Sybil attack, where a single physical node may create multiple \textit{pseudoidentities} \cite{sybil}.
-A suitably powerful node, or motivated attacker, could create enough pseudonyms to create a subnetwork of nodes, each creating malicious transactions with each other.
-This would allow an attacker to falsify a believable location proof.
-
-It has been proven that a central certificate authority is the only method of preventing a Sybil attack \cite{sybil}.
-Other measures, such as web of trust, increase the difficulty involved in performing an attack, but the system remains vulnerable to a motivated attacker.
-
-\newpage
 \section{Evaluation}
@@
 
-\section{Conclusions}
+\subsection{Attacks on the system}
+\subsubsection{Identity replication}
+By repeatedly publishing fake transactions with the same ID, a malicious user can impede the Verification of certain transactions.
+This is because a Verifier will have to attempt to decrypt all transactions with the same ID until it finds one that decrypts successfully.
+A malicious user can therefore slow down the verification stage of certain transactions by flooding the blockchain with transactions with the same ID.
 
-\begin{thebibliography}{9}
+This is an abuse of the system than an attack.
+A malicious user will not be able to target specific users' transactions, because they are privacy protected.
+The malicious user can therefore gain no material advantage or compromise the security of the system by using an attack like this.
 
-\bibitem{brassil}
-  J. Brassil, P.K. Manadhata,
-  ``Verifying the Location of a Mobile Device User'',
-  Proc. of MobiSec 2012,
-  June 2012.
+To avoid this attack, Miner nodes may reject any transactions with duplicate transaction IDs.
+Assuming sufficiently large transaction IDs, a duplicate ID is unlikely to happen through honest operation.
+Miners can assume that any transactions with duplicate IDs are malicious, and reject them.
 
-\bibitem{luo}
-  Luo, W., Hengartner, U.,
-  ``Proving your Location without giving up your Privacy'',
-  Proceedings of the Eleventh Workshop on Mobile Computing Systems \& Applications,
-  HotMobile 2010, Annapolis, Maryland, February 22 - 23, pp. 7–12. ACM,
-  New York (2010)
+\subsubsection{Sybil attack}
+This system is vulnerable to a Sybil attack, where a single physical node may create multiple \textit{pseudoidentities} \cite{sybil}.
+A suitably powerful node, or motivated attacker, could create enough pseudonyms to create a subnetwork of nodes, each creating malicious transactions with each other.
+This would allow an attacker to falsify a believable location proof.
 
-\bibitem{khan}
-  R. Khan, S. Zawoad, M. M. Haque, and R. Hasan,
-  ```Who, When, and Where?' Location Proof Assertion for Mobile Devices'',
-  Proceedings of the 28th Annual IFIP WG 11.3 Working Conference on Data and Applications Security and Privacy, ser. DBSec. IFIP,
-  July 2014.
-
-\bibitem{otit}
-  Khan, R., Zawoad, S., Haque, M., Hasan, R.
-  ``OTIT: Towards secure provenance modeling for location proofs'',
-  Proc. of ASIACCS. ACM (2014)
-
-\bibitem{sybil}
-  Douceur, J.R.,
-  ``The sybil attack'',
-  Druschel, P., Kaashoek, M.F., Rowstron, A. (eds.) IPTPS 2002. LNCS, vol. 2429, pp. 251–260,
-  Springer, Heidelberg (2002)
-
-\bibitem{location-spoof}
-  N. O. Tippenhauer, K. B. Rasmussen, C. Popper, and S. Capkun,
-  ``iPhone and iPod location spoofing: Attacks on public WLAN-based positioning systems'',
-  SysSec Technical Report,
-  ETH Zurich, April, 2008
-
-\bibitem{blueprint}
-  M. Swan,
-  ``Blockchain: Blueprint for a New Economy'',
-  Sebastopol, CA,
-  O’Reilly Media, 2015
-
-\bibitem{bitcoin}
-  S. Nakamoto,
-  ``Bitcoin: A Peer-to-Peer Electronic Cash System'',
-  2008
-
-\end{thebibliography}
-
-\end{document}
+It has been proven that a central certificate authority is the only method of preventing a Sybil attack \cite{sybil}.
+Other measures, such as web of trust, increase the difficulty involved in performing an attack, but the system remains vulnerable to a motivated attacker.

### 2016-03-31 presentation.tex
adding initial presentation files

\documentclass{beamer}

\beamertemplatenavigationsymbolsempty
\setbeamertemplate{footline}[frame number]

\usepackage{tikz}
\usetikzlibrary{matrix,positioning,arrows.meta,arrows,calc}

\title[Crisis]
{Decentralised location verification system}
\author{Conor Taylor}
\date{
	B.A.(Mod.) Computer Science\\
	Final Year Project, April 2016\\
	Supervisor: Stephen Barrett
}

\begin{document}

	\frame{\titlepage}

	\begin{frame}
    	\frametitle{Problem}
    	A system that allows participants to verify a users claimed location.
    	\\
    	\null
    	\visible<2->{
    		Goals:
   			\begin{itemize}
    			\item<3-> False location claims must be detectable.
    			\item<4-> Privacy protecting.
    			\item<5-> Cannot rely on any centralised resources.
    			\item<6-> Capable of running in the background on mobile devices.
    		\end{itemize}
    	}
	\end{frame}

	\begin{frame}
		\frametitle{Background}
		There are \textbf{no} known existing decentralised location proof systems.
		\\
		\null
		Existing centralised solutions: hardware and/or software
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		3 distinct entities:
		\begin{itemize}
			\item Mobile node $\vcenter{\hbox{\includegraphics[scale=0.2]{diagrams/overview-presentation/mobile-node.png}}}$
			\item Miner node $\vcenter{\hbox{\includegraphics[scale=0.2]{diagrams/overview-presentation/miner-node.png}}}$
			\item Verifier node $\vcenter{\hbox{\includegraphics[scale=0.2]{diagrams/overview-presentation/verifier-node.png}}}$
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Overview}
		\begin{figure}[H]
			\begin{center}
				\resizebox {\columnwidth} {!} {
					\includegraphics<1>{diagrams/overview-presentation/Overview-13.png}
					\includegraphics<2>{diagrams/overview-presentation/Overview-12.png}
					\includegraphics<3>{diagrams/overview-presentation/Overview-11.png}
					\includegraphics<4>{diagrams/overview-presentation/Overview-10.png}
					\includegraphics<5>{diagrams/overview-presentation/Overview-9.png}
					\includegraphics<6>{diagrams/overview-presentation/Overview-8.png}
					\includegraphics<7>{diagrams/overview-presentation/Overview-7.png}
					\includegraphics<8>{diagrams/overview-presentation/Overview-6.png}
					\includegraphics<9>{diagrams/overview-presentation/Overview-5.png}
					\includegraphics<10>{diagrams/overview-presentation/Overview-4.png}
					\includegraphics<11>{diagrams/overview-presentation/Overview-3.png}
					\includegraphics<12>{diagrams/overview-presentation/Overview-2.png}
					\includegraphics<13>{diagrams/overview-presentation/Overview-1.png}
					\includegraphics<14>{diagrams/overview-presentation/Overview-0.png}
			}
			\end{center}
		\end{figure}
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Identities}
		Used to anonymously identify a node in a transaction.
		\newline

		Balancing goals:
		\begin{itemize}
			\item False location claims must be detectable.
			\item Privacy protecting.
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Identities: Nonce Lists}
		\begin{figure}[H]
			\resizebox {\columnwidth} {!} {\input{diagrams/nonce_list_presentation.tex}}
		\end{figure}
	\end{frame}

	\begin{frame}
		\frametitle{Design}
		\framesubtitle{Identities: Duplication}
		Identity duplication is unavoidable in a decentralised system.
		\begin{table}[]
			\begin{tabular}{l|l}
				\textbf{ID} & \textbf{Contents}\\\hline
				\dots & \\\hline
				ffa0 & \\\hline
				ffa1 & \\\hline
				ffa2 & $T_{A4}$ \visible<2->{, \textcolor{red}{$T_{C102}$}}\\\hline
				ffa3 & \\\hline
				ffa4 & $T_{B87}$\\\hline
				\dots & \\
			\end{tabular}
		\end{table}
	\end{frame}
\end{document}

### 2016-03-31 diagrams/transaction_presentation.tex
updating presentation

\begin{tikzpicture}

\node[draw] (A) at (0,0) {\textbf{Node A}};
\only<2>{\node[above= 0mm of A] {\textcolor{red}{$n$}};}
\only<3->{\node[above= 0mm of A] {$n$};}

\only<3> {\node[below left= 0mm of A] (k_a) {\textcolor{red}{$K^+_A$, $K^-_A$}};}
\only<4-> {\node[below left= 0mm of A] (k_a) {$K^+_A$, $K^-_A$};}

\only<4> {\node[below= 0mm of k_a] (nl_a) {\textcolor{red}{$NL_A$}};}
\only<5-> {\node[below= 0mm of k_a] (nl_a) {$NL_A$};}

\only<5> {\node[below right=0mm and -1cm of nl_a] (id_a) {\textcolor{red}{$ID_{An} = K^+_A(NL_A[n])$}};}
\only<6-> {\node[below= 0mm of nl_a] (id_a) {$ID_{An}$};}

\only<6> {\node[below= 0mm of id_a] (ts_a) {\textcolor{red}{$ts_A$}};}
\only<7-> {\node[below= 0mm of id_a] (ts_a) {$ts_A$};}

\only<7> {\node[below= 0mm of ts_a] (loc_a) {\textcolor{red}{$loc_{A}$}};}
\only<8-> {\node[below= 0mm of ts_a] (loc_a) {$loc_{A}$};}

\only<15>{
\node[below= 0mm of loc_a] (id_b_a) {\textcolor{red}{$ID_{Bm}$}};
\node[below= 0mm of id_b_a] (ts_b_a) {\textcolor{red}{$ts_B$}};
\node[below= 0mm of ts_b_a] (loc_b_a) {\textcolor{red}{$loc_{B}$}};
}
\only<16->{
\node[below= 0mm of loc_a] (id_b_a) {$ID_{Bm}$};
\node[below= 0mm of id_b_a] (ts_b_a) {$ts_B$};
\node[below= 0mm of ts_b_a] (loc_b_a) {$loc_{B}$};
}

\node[draw] (B) at (5,0) {\textbf{Node B}};
\only<2>{\node[above= 0mm of B] {\textcolor{red}{$m$}};}
\only<3->{\node[above= 0mm of B] {$m$};}

\only<8->{
\node[below right= 0mm of B] (k_b) {$K^+_B$, $K^-_B$};
\node[below= 0mm of k_b] (nl_b) {$NL_B$};
\node[below= 0mm of nl_b] (id_b) {$ID_{Bm}$};
\node[below= 0mm of id_b] (ts_b) {$ts_B$};
\node[below= 0mm of ts_b] (loc_b) {$loc_{B}$};
}

\only<11>{
\node[below= 0mm of loc_b] (id_a_b) {\textcolor{red}{$ID_{An}$}};
\node[below= 0mm of id_a_b] (ts_a_b) {\textcolor{red}{$ts_A$}};
\node[below= 0mm of ts_a_b] (loc_a_b) {\textcolor{red}{$loc_{A}$}};
}
\only<12->{
\node[below= 0mm of loc_b] (id_a_b) {$ID_{An}$};
\node[below= 0mm of id_a_b] (ts_a_b) {$ts_A$};
\node[below= 0mm of ts_a_b] (loc_a_b) {$loc_{A}$};
}

\only<9>{
\draw[->] (A) -- (B) node[midway,below] (treq_label)
	{\textcolor{red}{$T_{req}$}};
}
\only<10>{
\draw[->] (A) -- (B) node[midway,below] (treq_label)
	{$T_{req}$};
}
\only<10>{
\node[below= 0mm of treq_label] {\textcolor{red}{$ID_{An} | ts_A | loc_A$}};
}

\only<12>{
\node[left= 5mm of loc_b] (v_b) {\small{\textit{\textcolor{red}{verify $|ts_A-ts_B| < \epsilon_{ts}$}}}};
\node[below= -2mm of v_b] {\small{\textit{\textcolor{red}{$\&\& |loc_A-loc_B| < \epsilon_{loc}$}}}};
}

\only<13>{
\draw[->] (B) -- (A) node[midway,below] (tres_label)
	{\textcolor{red}{$T_{res}$}};
}
\only<14>{
\draw[->] (B) -- (A) node[midway,below] (tres_label)
	{$T_{res}$};
}
\only<14>{
\node[below= 0mm of tres_label] {\textcolor{red}{$ID_{Bm} | ts_B | loc_B$}};
}

\only<16>{
\node[right= 5mm of loc_a] (v_a) {\small{\textit{\textcolor{red}{verify $|ts_A-ts_B| < \epsilon_{ts}$}}}};
\node[below= -2mm of v_a] {\small{\textit{\textcolor{red}{$\&\& |loc_A-loc_B| < \epsilon_{loc}$}}}};
}

\end{tikzpicture}

### 2016-03-31 network_diagram.tex
updating presentation

\documentclass[a4paper,11pt]{article}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{matrix,shapes,arrows,positioning,chains, calc}
\begin{document}

\begin{tikzpicture}
\matrix (m)[matrix of nodes, column  sep=2cm,row  sep=8mm, nodes={draw=none, anchor=center,text depth=0pt} ]{
Prover & & Verifier\\[-4mm]
Choose a random number & & \\[-7mm]
$r \in \{0,1\}^{*}.$ & & \\
 & Send $r$ & \\
& & Choose a random number  \\[-7mm]
& &$s \in \{0,1\}^{*}.$\\
 & Send $s$ & \\
};

\draw[shorten <=-1.5cm,shorten >=-1.5cm] (m-1-1.south east)--(m-1-1.south west);
\draw[shorten <=-1.5cm,shorten >=-1.5cm] (m-1-3.south east)--(m-1-3.south west);
\draw[shorten <=-1cm,shorten >=-1cm,-latex] (m-4-2.south west)--(m-4-2.south east);
\draw[shorten <=-1cm,shorten >=-1cm,-latex] (m-7-2.south east)--(m-7-2.south west);
\end{tikzpicture}
\end{document}

### 2016-03-31 presentation.tex
updating presentation

@@
 		Identity duplication is unavoidable in a decentralised system.
+		\visible<2->{
 		\begin{table}[]
@@
 				ffa1 & \\\hline
-				ffa2 & $T_{A4}$ \visible<2->{, \textcolor{red}{$T_{C102}$}}\\\hline
+				ffa2 & $T_{A4}$ \visible<3->{, \textcolor{red}{$T_{C102}$}}\\\hline
 				ffa3 & \\\hline
@@
 		\end{table}
+		}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Design}
+		\framesubtitle{Transactions}
+		Transactions are created when two mobile nodes physically meet.
+		\begin{itemize}
+			\item Ad-hoc bluetooth connection between the nodes.
+		\end{itemize}
+
+		\begin{center}
+			\resizebox {0.35\columnwidth} {!} {\includegraphics{diagrams/overview-presentation/mobile-node-meet.png}}
+		\end{center}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Design}
+		\framesubtitle{Transactions II}
+		\begin{figure}[t]
+			\resizebox {\columnwidth} {!} {\input{diagrams/transaction_presentation.tex}}
+		\end{figure}
 	\end{frame}

### 2016-04-01 presentation.tex
finishing presentation design section

@@
 		\framesubtitle{Transactions II}
-		\begin{figure}[t]
-			\resizebox {\columnwidth} {!} {\input{diagrams/transaction_presentation.tex}}
+		Node $A$ will create the following transaction after meeting node $B$:
+		\newline
+
+		\begin{center}
+		\only<1>{$T_{An} = K_A(ts_A|loc_A|ID_{An}|KP_{Bm})$}
+		\only<2->{$T_{An} = K_A(ts_A|loc_A|ID_{An}|\textcolor{red}{KP_{Bm}})$}
+		\end{center}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Design}
+		\framesubtitle{Transactions: Key Packets}
+		Key Packets provide a Verifier with a means of examining a mobile node's transactions.
+		\newline
+
+		\only<2->{
+		Two main properties:
+		\begin{itemize}
+			\only<2>{
+			\item Allow a Verifier to build a tree of a mobile node's activity.
+			}
+			\only<3>{
+			\item \textcolor{red}{Allow a Verifier to build a graph of a mobile node's activity.}
+			}
+			\item Allow a mobile node to preserve control its own privacy.
+		\end{itemize}
+		}
+	\end{frame}
+
+	\begin{frame}[b]
+		\frametitle{Design}
+		\framesubtitle{Transactions: Key Packets - Verification}
+		\vspace{-0.5cm}
+		\begin{figure}
+			\resizebox {\columnwidth} {!} {\input{diagrams/tree.tex}}
 		\end{figure}
 	\end{frame}
+
+	\begin{frame}
+		\frametitle{Design}
+		\framesubtitle{Transactions: Key Packets}
+		Key Packets provide a Verifier with a means of examining a mobile node's transactions.
+		\newline
+
+		Two main properties:
+		\begin{itemize}
+			\item Allow a Verifier to build a graph of a mobile node's activity.
+			\item \textcolor{red}{Allow a mobile node to preserve control its own privacy.}
+		\end{itemize}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Design}
+		\framesubtitle{Transactions: Key Packets - Privacy}
+		Published transactions split into two parts: Link and Transaction
+		\newline
+
+		\begin{figure}
+			\resizebox {\columnwidth} {!} {\input{diagrams/link.tex}}
+		\end{figure}
+		\only<4->{
+			\begin{center}
+				Two \textit{Key Lists}: $KL_{AT}$ and $KL_{AL}$.
+			\end{center}
+		}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Design}
+		\framesubtitle{Transactions III}
+		Node $A$ will create the following transaction after meeting node $B$:
+
+		\begin{center}
+		\only<1>{$T_{An} = \textcolor{red}{K_A}(ts_A|loc_A|ID_{An}|KP_{Bm})$}
+		\only<2>{$T_{An} = \textcolor{red}{KL_{AT}[n]}(ts_A|loc_A|ID_{An}|KP_{Bm})$}
+		\only<3->{$T_{An} = KL_{AT}[n](ts_A|loc_A|ID_{An}|KP_{Bm})$}
+		\end{center}
+		\vspace{0.5cm}
+
+		\only<3->{
+		Node $A$ will then publish the following to the blockchain:
+
+		\begin{center}
+		$P_{An} = ID_{An}|\textcolor{red}{KL_{AL}[n]}(ID_{An-1}|ts_A)|T_{An}$
+		\end{center}
+		} 
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Design}
+		\framesubtitle{Verification}
+		Mobile node needs to provide Verifier node with:
+		\begin{itemize}
+			\item ID of most recent transaction.
+			\item Key Packet for $n$ most recent transactions.
+			\item Nonce list for $n$ most recent IDs.
+			\item Public key.
+		\end{itemize}
+	\end{frame}
+
 \end{document}

### 2016-04-04 presentation.tex
Adding finished (hopefully) presentation, with speaker notes

@@
 \usetikzlibrary{matrix,positioning,arrows.meta,arrows,calc}
+
+\usepackage{soul}
 
@@
     	\frametitle{Problem}
-    	A system that allows participants to verify a users claimed location.
-    	\\
+    	Design and evaluate a decentralised system that allows participants to prove their location.
+    	\begin{itemize}
+    		\item<2-> Is is possible?
+    		\item<3-> Is it resilient to attack?
+    		\item<4-> Does it satisfy my goals?
+    	\end{itemize}
     	\null
-    	\visible<2->{
+    	\visible<5->{
     		Goals:
    			\begin{itemize}
-    			\item<3-> False location claims must be detectable.
-    			\item<4-> Privacy protecting.
-    			\item<5-> Cannot rely on any centralised resources.
-    			\item<6-> Capable of running in the background on mobile devices.
+   				\item<5-> Privacy protecting.
+    			\item<6-> False location claims must be detectable.
+    			\item<7-> Cannot rely on any centralised resources.
+    			\item<8-> Capable of running on mobile devices.
     		\end{itemize}
@@
 		\frametitle{Background}
-		There are \textbf{no} known existing decentralised location proof systems.
-		\\
+		There are no known existing decentralised location proof systems.
+		\newline
+
+		\visible<2->{There are existing \textit{distributed} location proof systems, with different interesting approaches.}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Background}
+		\framesubtitle{HP Laboratories}
+		\begin{center}
+			HP Laboratories.
+		\end{center}
+	\end{frame}
+
+	\begin{frame}[noframenumbering]
+		\frametitle{Background}
+		\framesubtitle{HP Laboratories}
+		\begin{figure}[H]
+			\begin{center}
+				\resizebox {0.5\columnwidth} {!} {
+					\includegraphics<1>{diagrams/femto_diag_5.png}
+					\includegraphics<2>{diagrams/femto_diag_4.png}
+					\includegraphics<3>{diagrams/femto_diag_3.png}
+					\includegraphics<4>{diagrams/femto_diag_2.png}
+					\includegraphics<5>{diagrams/femto_diag_1.png}
+					\includegraphics<6>{diagrams/femto_diag_0.png}
+				}
+			\end{center}
+		\end{figure}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Background}
+		\framesubtitle{University of Waterloo}
+		\begin{center}
+			University of Waterloo.
+		\end{center}
+	\end{frame}
+
+	\begin{frame}[noframenumbering]
+		\frametitle{Background}
+		\framesubtitle{University of Waterloo}
+		\begin{figure}[H]
+			\begin{center}
+				\resizebox {0.8\columnwidth} {!} {
+					\includegraphics<1>{diagrams/AP_paper_2.png}
+					\includegraphics<2>{diagrams/AP_paper_1.png}
+					\includegraphics<3>{diagrams/AP_paper_3.png}
+				}
+			\end{center}
+		\end{figure}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Background}
+		\framesubtitle{Who, When. and Where?}
+		\begin{center}
+			Who, When, and Where?\\
+			University of Alabama.
+		\end{center}
+	\end{frame}
+
+	\begin{frame}[noframenumbering]
+		\frametitle{Background}
+		\framesubtitle{Who, When. and Where?}
+		\begin{figure}[H]
+			\begin{center}
+				\resizebox {0.4\columnwidth} {!} {
+					\includegraphics<1>{diagrams/witness_paper_3.png}
+					\includegraphics<2>{diagrams/witness_paper_2.png}
+					\includegraphics<3>{diagrams/witness_paper_1.png}
+					\includegraphics<4>{diagrams/witness_paper_0.png}
+					\includegraphics<5>{diagrams/witness_paper_5.png}
+					\includegraphics<6>{diagrams/witness_paper_4.png}
+				}
+			\end{center}
+		\end{figure}
+	\end{frame}
+
+	\begin{frame}
+    	\frametitle{Problem}
+    	\framesubtitle{Issues}
+    	A decentralised location proof system needs a way of:
+   		\begin{itemize}
+    		\item Creating, storing, and providing access to location proofs.
+    		\item Detecting fake location proofs.
+    		\item Allowing users full control over their own privacy.
+    	\end{itemize}
+		\visible<2>{
 		\null
-		Existing centralised solutions: hardware and/or software
+		Without any central resource to store data or manage the system.}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Background}
+		\framesubtitle{Blockchain}
+		A blockchain is a decentralised, tamper-proof, append-only ledger.
+		\newline
+
+		\visible<2->{Allows transaction records to be stored publicly and permenantly, without use of a central authority.}
+	\end{frame}
+
+	\begin{frame}[noframenumbering]
+		\frametitle{Background}
+		\framesubtitle{Blockchain}
+		\begin{figure}[H]
+			\resizebox {0.8\columnwidth} {!} {\input{diagrams/blockchain.tex}}
+		\end{figure}
+	\end{frame}
+
+	\begin{frame}[noframenumbering]
+		\frametitle{Background}
+		\framesubtitle{Blockchain}
+		Decentralised, tamper-proof method of storing location proofs.
 	\end{frame}
@@
 
+	\begin{frame}[noframenumbering]
+    	\frametitle{Problem}
+    	A system that allows participants to verify a users claimed location.
+    	\\
+    	\null
+    	Goals:
+   		\begin{itemize}
+    		\item Privacy protecting.
+    		\item False location claims must be detectable.
+    		\item \textcolor{red}{Cannot rely on any centralised resources.}
+    		\item \textcolor{red}{Capable of running on mobile devices.}
+    	\end{itemize}
+	\end{frame}
+
 	\begin{frame}
@@
 		\framesubtitle{Identities}
-		Used to anonymously identify a node in a transaction.
+		Used to \textbf{anonymously} identify a node in a transaction.
+		\newline
+
+		Every node generates a new identity for each transaction, making it untrackable.
 		\newline
@@
 		\framesubtitle{Identities: Duplication}
-		Identity duplication is unavoidable in a decentralised system.
+		Identity duplication unavoidable in a scalable decentralised system.
 		\visible<2->{
@@
 
-	\begin{frame}
+	\begin{frame}[noframenumbering]
 		\frametitle{Design}
-		\framesubtitle{Transactions II}
+		\framesubtitle{Transactions}
 		Node $A$ will create the following transaction after meeting node $B$:
@@
 
-		\only<2->{
+		\visible<2->{
 		Two main properties:
@@
 			}
-			\only<3>{
-			\item \textcolor{red}{Allow a Verifier to build a graph of a mobile node's activity.}
+			\only<3->{
+			\item \textcolor{red}{Allow a Verifier to build a tree of a mobile node's activity.}
 			}
@@
 		\end{figure}
+	\end{frame}
+
+	\begin{frame}[noframenumbering]
+    	\frametitle{Problem}
+    	A system that allows participants to verify a users claimed location.
+    	\\
+    	\null
+    	Goals:
+   		\begin{itemize}
+    		\item Privacy protecting.
+    		\item \textcolor{red}{False location claims must be detectable.}
+    		\item Cannot rely on any centralised resources.
+    		\item Capable of running on mobile devices.
+    	\end{itemize}
 	\end{frame}
@@
 		\end{figure}
-		\only<4->{
+		\visible<4->{
 			\begin{center}
@@
 		\frametitle{Design}
-		\framesubtitle{Transactions III}
+		\framesubtitle{Transactions}
 		Node $A$ will create the following transaction after meeting node $B$:
@@
 
-		\only<3->{
+		\visible<3->{
 		Node $A$ will then publish the following to the blockchain:
@@
 
+	\begin{frame}[noframenumbering]
+    	\frametitle{Problem}
+    	A system that allows participants to verify a users claimed location.
+    	\\
+    	\null
+    	Goals:
+   		\begin{itemize}
+    		\item \textcolor{red}{Privacy protecting.}
+    		\item False location claims must be detectable.
+    		\item Cannot rely on any centralised resources.
+    		\item Capable of running on mobile devices.
+    	\end{itemize}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Evaluation}
+		Case-based evaluation.
+		\newline
+
+		\visible<2->{
+		Two kinds of case-based evaluation:
+		\begin{itemize}
+			\item Desirable properties.
+			\item Threats.
+		\end{itemize}}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Evaluation}
+		\framesubtitle{Desirable properties}
+		OTIT defines 8 desirable properties of a location proof system:
+		\begin{columns}
+			\begin{column}{0.5\textwidth}
+				\begin{itemize}
+					\item Chronological.
+					\item Order-preserving.\newline
+					\item Verifiable.\newline
+					\item Tamper evident.
+				\end{itemize}
+			\end{column}
+			\begin{column}{0.5\textwidth}
+				\begin{itemize}
+					\item Privacy preserved.
+					\item Selective in-sequence privacy.
+					\item Privacy protected chronology.
+					\item Convenience and derivablilty.
+				\end{itemize}
+			\end{column}
+		\end{columns}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Evaluation}
+		\framesubtitle{Threats}
+		A number of papers have gathered threats to evaluate their models against:
+		\begin{columns}
+			\begin{column}{0.5\textwidth}
+				\begin{itemize}
+					\item Dishonest users.
+					\item Malicious intruders.
+					\item Curious users.
+					\item Malicious applications.
+					\item False timestamping.
+					\item Implication.
+					\item Proof switching.
+					\item Relay attack.\newline
+				\end{itemize}
+			\end{column}
+			\begin{column}{0.5\textwidth}
+				\begin{itemize}
+					\item Eavesdroppers.
+					\item Wormhole attacks.
+					\item False presence.
+					\item False assertion.
+					\item Denial of presence.
+					\item Denial of witness's presence.
+					\item Privacy violation.
+					\item \st{Weak identities.}
+					\item \st{Sybil attack.}
+				\end{itemize}
+			\end{column}
+		\end{columns}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Evaluation}
+		\framesubtitle{Threats - Weak identities}
+		I assume that private keys and nonce lists are never shared.
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Evaluation}
+		\framesubtitle{Threats - Sybil attack}
+		No way of determining if two distinct location proof chains were created by two distinct mobile nodes.
+		\newline
+
+		\visible<2->{
+		No provable decentralised solution to the Sybil attack (yet).}
+		\newline
+
+		\visible<3->{
+		Mitigations:
+		\begin{itemize}
+			\item Introduce identity creation penalty.
+			\item Web of trust.
+			\item Secret verification techniques.
+		\end{itemize}}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Conclusion}
+		Developed a privacy-protecting, decentralised location proof system.
+		\newline
+
+		\visible<2->{
+		Completed a case-based evaluation.}
+		\newline
+
+		\visible<3->{
+		Currently vulnerable to extremely targeted Sybil attacks.}
+		\newline
+
+		\visible<4->{
+		Resilient against every other known attack.
+		\begin{itemize}
+			\item<5-> Sybil attack can be heavily mitigated against.
+			\item<6-> Decentralised solution to Sybil attack may be found in future.
+		\end{itemize}}
+	\end{frame}
+
+	\begin{frame}
+		\frametitle{Future work}
+		Further study into advanced Verification techniques.
+		\newline
+
+		\visible<2->{
+		Investigate the impact that witholding certain private transactions has on verifiability.}
+		\newline
+
+		\visible<3->{
+		Build it!}
+	\end{frame}
+
 \end{document}

### 2016-04-07 thesis/background.tex
Adding 3 example papers to background

@@
 \subsection{Proving your location}
-As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, the security that existed by requiring physical interaction between humans to transfer sensitive data is lost.
+As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, the security that previously existed by requiring physical interaction between humans to transfer sensitive data is lost.
+
+Location proving is a large part of that security.
+There is currently no ubiquitous method of \textit{proving} your location digitally.
+Many companies, such as Netflix, use GeoIP databases such as MaxMind \cite{maxmind} to determine a users location based on his IP address.
+This technique is inaccurate and easily bypassable using proxy servers or VPNs.
+
+One newer, more advanced tecnique of GeoIP location verification is Constraint-Based Geolocation \cite{constraint-based}.
+This is an active geolocation technique, compared with GeoIP verification which is static.
+It operates by estimating the location of the users IP address by calculating the latencies between the user's machine and multiple surrounding machines with fixed, known locations.
+However, even advanced systems like these can easily be bypassed, using IP spoofing techniques, proxy servers, VPNs, or by using anonymising networks such as TOR \cite{tor}.
+
+Better solutions to this problem exist.
+\textit{Location proof systems} are systems which allow users of the system to \textit{prove} their location to another user.
+Examples of these are discussed in detail in section \ref{ssec:proof_systems}.
+
+\subsection{Distributed and decentralised systems}
+A distributed system is a system which distributes the computation of a task across multiple computers (nodes) connected over a network.
+These nodes then communicate to complete the task by passing messages over the network \cite{distributed}.
+
+For example, Google search indexes are not computed on just one node, rather on a network of nodes that communicate by sending messages to each other.
+Google therefore \textit{distributes} the task of calculating search indexes across multiple nodes.
+This two main advantages; It's far more efficient, because different index calculations can be computed on different nodes at the same time, and it's very scalable, because nodes can be added or removed from the network dynamically, to react to demand.
+
+A decentralised system is similar to a distributed system, except no node is in charge.
+Nodes in a decentralised network still communicate by passing messages to each other over the network, but unlike a distributed system, they don't act as slaves to a master.
+Bitcoin \cite{bitcoin} is a good example of a large-scale decentralised system.
+Two nodes in the Bitcoin network can choose to create a transaction by sending money between themselves, and they make the details of that transaction public.
+The two nodes created and published the transaction independently of all other nodes on the network.
+
+In the context of a location proof system, I consider a distributed system to be one where the task of facilitating user proof request and creation is distributed across multiple \textit{worker nodes}, which are controlled and coordinated by a central node.
+This allows a higher volume of proofs to be created concurrently, while maintaining centralised control over the system.
+This is shown in figure \ref{fig:distributed_location}.
+
+\begin{figure}[H]
+\begin{center}
+\resizebox {0.6\columnwidth} {!} {\input{diagrams/distributed_location.tex}}
+\end{center}
+\caption{Distributed location proof system}
+\label{fig:distributed_location}
+\end{figure}
+
+I consider a decentralised location proof system to be one where no node is in charge of controlling or coordinating the system.
+Nodes can create and publish location proofs between themselves, without the need for a central third party to coordinate the interaction (figure \ref{fig:decentralised_location}).
+
+\begin{figure}[H]
+\begin{center}
+\resizebox {0.6\columnwidth} {!} {\input{diagrams/decentralised_location.tex}}
+\end{center}
+\caption{Decentralised location proof system}
+\label{fig:decentralised_location}
+\end{figure}
+
+\subsection{Existing location proof systems} \label{ssec:proof_systems}
+Location proof systems are expected to be accurate and tamper-proof.
+For this reason, existing solutions have chosen to use a central authority to issue proofs, or to regulate proof issuance \cite{brassil, luo, khan}.
+
+A hardware technique \cite{brassil}, developed by Brassil et al.
+of HP Laboratories, operates by supplementing existing WiFi access points (\textit{AP's}) with \textit{femtocells}.
+A femtocell is a small cellular antenna that connects to a mobile carrier via the Internet.
+Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data via Wi-Fi.
+This is possible because the central server in the location verification system has access to the mobile operator's user data.
+This solution requires investment in additional hardware to supplement existing WiFi access points, and requires access to mobile providers' user database to identify users locations (see figure \ref{fig:hp_labs}).
+
+\begin{figure}[H]
+\begin{center}
+\resizebox {0.5\columnwidth} {!} {\includegraphics{diagrams/hp_paper.png}}
+\caption{Hardware-based proof system (Adapted from Brassil et al. \cite{brassil})}
+\label{fig:hp_labs}
+\end{center}
+\end{figure}
+
+The use of a centralised system, as described above, creates security, privacy and vulnerability issues.
+An attacker who succeeds in compromising the security of the central server can violate the privacy of the users of the system, and potentially track their location.
+This is because in this system, location proofs reside with the central server, so the user has no control over their security.
+The central system architecture is also vulnerable, in the sense that a resource availability attack such as a DDoS attack could render the central architecture unavailable, making location verification unavailable.
+
+Luo et al.
+propose a system that uses software installed on Wi-Fi access points to allow users to create location proofs \cite{luo}.
+In their system, each access point is given a \textit{group signature} by a central server, and can sign location proofs for users (figure \ref{fig:luo_diagram}).
+
+\begin{figure}[H]
+\begin{center}
+\resizebox {0.5\columnwidth} {!} {\includegraphics{diagrams/ap_paper.png}}
+\caption{Access point proof system (Adapted from Luo et al. \cite{luo})}
+\label{fig:luo_diagram}
+\end{center}
+\end{figure}
+
+Users can request a location proof from any access point, and receive a proof encrypted by the AP with the group signature, as shown in figure \ref{fig:luo_transaction}.
+This can then be submitted to a Verifier.
+
+This system creates \textit{proactive} location proofs.
+A proactive location proof is one which is created before it is needed.
+The user creates application-independent location proofs, and can use them at a later time with any application(s) he chooses.
+
+A system proposed by Khan et al.
+takes a different approach, by using other users as witnesses to a location claim \cite{khan}.
+In this system, a \textit{witness} physically located near the user is used by the central server to verify the user's location claim (figure \ref{fig:witness_paper}).
+Like the model proposed by Luo et al., this system allows the user to have control over their own privacy, as the user owns the location proof.
+
+\begin{figure}[H]
+\begin{center}
+\resizebox {0.4\columnwidth} {!} {\includegraphics{diagrams/witness_paper.png}}
+\caption{Proof system using witnesses (Adapted from Khan et al. \cite{khan})}
+\label{fig:witness_paper}
+\end{center}
+\end{figure}
 
@@
 
-\subsection{Centralised location proof systems}
-Location proof systems are expected to be accurate and tamper-proof.
-For this reason, existing solutions have chosen to use a central authority to issue proofs, or to regulate proof issuance \cite{brassil, luo, khan}.
-
-A hardware technique \cite{brassil} operates by supplementing existing WiFi access points with \textit{femtocells}.
-A femtocell is a small cellular antenna that connects to a mobile carrier via the Internet.
-Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data via Wi-Fi.
-This solution requires investment in additional hardware to supplement existing WiFi access points, and requires access to mobile providers' user database to identify users locations.
-
-The use of a centralised system, like that described by Brassil et al.
-\cite{brassil}, creates security, privacy and vulnerability issues.
-An attacker who succeeds in compromising the security of the central server can violate the privacy of the users of the system, and potentially track their location.
-The central system architecture is also vulnerable, in the sense that a resource availability attack such as a DDoS attack could render the central architecture unavailable, making location verification unavailable.
-
-Luo et al.
-propose a system that uses Wi-Fi access points (\textit{AP's}) to allow users to create location proofs \cite{luo}.
-In their system, each access point has a \textit{group signature} and can sign location proofs for requesting users.
-Users can request a location proof from any access point, and receive a proof encrypted by the AP with the group signature, as shown in figure \ref{fig:luo_transaction}.
-This can then be submitted to a Verifier.
-
-\begin{figure}[H]
-\begin{center}
-\resizebox {0.6\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
-\end{center}
-\caption{Adopted from Luo et al. \cite{luo}}
-\label{fig:luo_transaction}
-\end{figure}
-
-This kind of system creates \textit{proactive} location proofs.
-A proactive location proof is one which is created before it is needed.
-The user creates application-independent location proofs, and can use them at a later time with any application(s) he chooses.
+\subsection{Goals of a decentralised proof system}

### 2016-04-07 thesis/diagrams/distributed_location.tex
Adding 3 example papers to background

\begin{tikzpicture}

\node[draw] (C) at (0,0) {Central node};

\node[draw,style=circle,fill=black] (D1) at (-2,-1) {};
\node[draw,style=circle,fill=black] (D2) at (0,-1) {};
\node[draw,style=circle,fill=black] (D3) at (2,-1) {};

\draw[-] (C) -- (D1) (C) -- (D2) (C) -- (D3);

\node[draw,style=circle] (N1) at (-2.5,-2) {};\node[draw,style=circle] (N2) at (-1.5,-2) {};
\node[draw,style=circle] (N3) at (1.5,-2) {};

\draw[-] (N1) -- (D1) (N2) -- (D1) (N3) -- (D3);

\node[draw,style=circle,fill=black,label=right:Worker node] (L1) at (-1.5,-3) {};
\node[draw,style=circle,label=right:User node] (L2) at (-1.5,-3.5) {};

\end{tikzpicture}

### 2016-04-07 thesis/introduction.tex
Adding 3 example papers to background

@@
 \subsection{Project and Motivation}
-Location verification is the process of verifying whether or not a mobile node (computer) is physically present at the location it claims to be.
-Existing location verification systems attept to provide this service using centralised, trusted ``authoritive'' nodes to provide proof of a mobile node's location.
-These approaches require investment in infrastructure, and are subject to data breaches and denial of service attacks.
-This project aims to present a \textit{decentralised} solution to this problem, in which there is no ``authoritive source'' trusted and relied upon to provide and store location information.
+Location verification is the process of verifying whether or not a  node (computer) is physically present at the location it claims to be.
+Existing location verification systems attept to provide this service using centralised, trusted ``authoritive'' nodes to provide proof of another node's location.
+These approaches require investment in infrastructure, and are subject to attacks on privacy and denial of service attacks.
+This project aims to present a \textit{decentralised} solution to this problem, in which there is no ``authoritive source'' trusted and relied upon to provide and store sensitive location information.
 
-This project will focus on obtaining location proofs by using other untrusted mobile nodes as \textit{alibi's}.
-Proofs will be created over an ad-hoc peer-to-peer network, encrypted, and published on a public append-only bulletin board, known as a \textit{blockchain}.
-The decentralised nature of the system means that there is no single point of failure, and no one entity controlling the security of every node's location proofs.
+This project describes a decentralised location proof system that operates on mobile devices (mobile nodes).
+I propose a design in which location proofs are obtained by using other untrusted mobile nodes as \textit{alibi's}.
+Proofs will be created by communicating over an ad-hoc bluetooth network, encrypted, and published on a public append-only bulletin board, known as a \textit{blockchain}.
+The decentralised nature of the system means that there is no single point of failure, no entity controlling the security of every node's location proofs, and no entity capable of violating another node's privacy.

### 2016-04-07 thesis/thesis.tex
updating thesis to match paper
Adding 3 example papers to background

@@
 \usepackage{float}
+
+\usepackage{chngcntr}
+\counterwithin{figure}{section}
+
+\renewcommand{\thefigure}{\thesection.\arabic{figure}}
 
@@
 \end{abstract}
+\newpage
+
+\tableofcontents
+\newpage
+
+\listoffigures
+\newpage
 
@@
 \input{background.tex}
+\newpage
+\input{design.tex}
+\newpage
+\input{evaluation.tex}
 
@@
   HotMobile 2010, Annapolis, Maryland, February 22 - 23, pp. 7–12. ACM,
-  New York (2010)
+  New York (2010).
 
@@
   ``OTIT: Towards secure provenance modeling for location proofs'',
-  Proc. of ASIACCS. ACM (2014)
+  Proc. of ASIACCS. ACM (2014).
 
@@
   Druschel, P., Kaashoek, M.F., Rowstron, A. (eds.) IPTPS 2002. LNCS, vol. 2429, pp. 251–260,
-  Springer, Heidelberg (2002)
+  Springer, Heidelberg (2002).
+
+\bibitem{maxmind}
+  MaxMind LLC. GeoIP. http://www.maxmind.com,
+  2010.
+
+\bibitem{constraint-based}
+  B. Gueye, A. Ziviani, M. Crovella, and S. Fdida,
+  ``Constraint-based geolocation of Internet hosts'',
+  IEEE/ACM Transactions on Networking,
+  14(6):1219–1232, 2006.
 
@@
   SysSec Technical Report,
-  ETH Zurich, April, 2008
+  ETH Zurich, April, 2008.
+
+\bibitem{tor}
+  R. Dingledine, N. Mathewson, and P. Syverson,
+  ``TOR: The second generation onion router'',
+  Proceedings of the Usenix Security Symposium,
+  2004.
+
+\bibitem{distributed}
+  Coulouris, George; Jean Dollimore; Tim Kindberg; Gordon Blair,
+  ``Distributed Systems: Concepts and Design (5th Edition)'',
+  Boston: Addison-Wesley,
+  2011.
+
+\bibitem{blueprint}
+  M. Swan,
+  ``Blockchain: Blueprint for a New Economy'',
+  Sebastopol, CA,
+  O’Reilly Media, 2015
+
+\bibitem{bitcoin}
+  S. Nakamoto,
+  ``Bitcoin: A Peer-to-Peer Electronic Cash System'',
+  2008
 

### 2016-04-07 thesis/background.tex
converting thesis to Report format

@@
-\section{Background}
-\subsection{Proving your location}
+\section{Proving your location}
 As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, the security that previously existed by requiring physical interaction between humans to transfer sensitive data is lost.
@@
 
-\subsection{Distributed and decentralised systems}
+\section{Distributed and decentralised systems}
 A distributed system is a system which distributes the computation of a task across multiple computers (nodes) connected over a network.
@@
 
-\subsection{Existing location proof systems} \label{ssec:proof_systems}
+\section{Existing location proof systems} \label{ssec:proof_systems}
 Location proof systems are expected to be accurate and tamper-proof.
@@
 
-\subsection{Ad-hoc networks}
+\section{Ad-hoc networks}
 
-\subsection{Blockchain}
+\section{Blockchain}
 
-\subsection{Goals of a decentralised proof system}
+\section{Goals of a decentralised proof system}

### 2016-04-07 thesis/design.tex
Adding 3 example papers to background
converting thesis to Report format

@@
-\section{Design}
 The location proof system we propose allows \textit{mobile nodes} to create location proofs for each other after physically meeting.
@@
 
-\subsection{Identities}
+\section{Identities}
 In order to preserve user's privacy, a user will only ever use an identity for one transaction, before generating a new one.
@@
 
-\subsubsection{Nonce list} \label{sssec:nonce_list}
+\subsection{Nonce list} \label{sssec:nonce_list}
 A \textit{Nonce List} is simply a list of all of the nonces a mobile node has used so far to generate identities.
@@
 
-\subsubsection{Identity duplication}
+\subsection{Identity duplication}
 Since all identities are generated from random nonces, there is nothing to stop two nodes from generating the same identity and using it in different transactions.
@@
 \newpage
-\subsection{Transactions} \label{sec:transactions}
+\section{Transactions} \label{sec:transactions}
 During a transaction between two nodes, a number of different items must be shared and calculated.
@@
 
-\subsubsection{Transaction creation}
+\subsection{Transaction creation}
 Once nodes have exchanged \textit{Key Packets}, their communication is finished and they can close their ad-hoc channel.
@@
 
-$T_{An} = KL_{AT}[n](ts|loc|ID_{An}|KP_{Bm})$
+$T_{An} = KL_{AT}[n](ts|loc|ID_{An}|ID_{Bm}|KP_{Bm})$
 \\
@@
 	\item[] $\mathbf{ID_{An}}$ is $A$'s $nth$ identity, used for this transaction only.
+	\item[] $\mathbf{ID_{Bm}}$ is $B$'s $mth$ identity.
 	\item[] $\mathbf{KP_{Bm}}$ is $B$'s \textit{Key Packet} at time $m$. Its exact contents are discussed in more detail in section \ref{sssec:key_packets}
@@
 
-\subsubsection{Publishing to the blockchain}
+\subsection{Publishing to the blockchain}
 After creating $T_{An}$, node $A$ must publish it to the public blockchain.
@@
 
-\subsubsection{Key Packets} \label{sssec:key_packets}
+\subsection{Key Packets} \label{sssec:key_packets}
 The key packet is more than simply a list of keys that a mobile node has used to encrypt its transactions; in order to preserve the ``selective in-sequence privacy'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt.
@@
 
-\subsubsection{Aborting transactions}
+\subsection{Aborting transactions}
 A node may decide to abort a transaction if it thinks it is in contact with a malicious node.
@@
 
-\subsection{Verification} \label{ssec:verification}
+\section{Verification} \label{ssec:verification}
 \begin{minipage}{0.5\linewidth}

### 2016-04-07 thesis/evaluation.tex
converting thesis to Report format

@@
-\section{Evaluation}
 In this paper, we have presented a model for a location proof system which aims to preserve privacy and prevent false proofs from being created.
 
-\subsection{OTIT conformance}
+\section{OTIT conformance}
 We can compare our model to OTIT \cite{otit}, a list of features and requirements necessary for designing any secure location proof scheme. OTIT presents 8 such requirements:
@@
 
-\subsection{Attacks on the system}
-\subsubsection{Identity replication}
+\section{Attacks on the system}
+\subsection{Identity replication}
 By repeatedly publishing fake transactions with the same ID, a malicious user can impede the Verification of certain transactions.
@@
 
-\subsubsection{Sybil attack}
+\subsection{Sybil attack}
 This system is vulnerable to a Sybil attack, where a single physical node may create multiple \textit{pseudoidentities} \cite{sybil}.

### 2016-04-07 thesis/introduction.tex
converting thesis to Report format

@@
-\section{Introduction}
-\subsection{Project and Motivation}
+\section{Project and Motivation}
 Location verification is the process of verifying whether or not a  node (computer) is physically present at the location it claims to be.

### 2016-04-12 thesis/background.tex
Updates after proofreading Background chapter

@@
 \section{Proving your location}
-As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, the security that previously existed by requiring physical interaction between humans to transfer sensitive data is lost.
+As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, we are losing the security that previously existed by requiring physical interaction between humans to transfer sensitive data
 
-Location proving is a large part of that security.
-There is currently no ubiquitous method of \textit{proving} your location digitally.
-Many companies, such as Netflix, use GeoIP databases such as MaxMind \cite{maxmind} to determine a users location based on his IP address.
+Location proof is a large part of that security.
+There is currently no ubiquitous method of \textit{proving} your location at a given time digitally.
+Many companies, such as Netflix, use GeoIP databases such as MaxMind \cite{maxmind} to estimate a users location based on his IP address.
 This technique is inaccurate and easily bypassable using proxy servers or VPNs.
 
-One newer, more advanced tecnique of GeoIP location verification is Constraint-Based Geolocation \cite{constraint-based}.
+One newer, more advanced tecnique of location observation is Constraint-Based Geolocation \cite{constraint-based}.
 This is an active geolocation technique, compared with GeoIP verification which is static.
-It operates by estimating the location of the users IP address by calculating the latencies between the user's machine and multiple surrounding machines with fixed, known locations.
+It estimates the location of a users IP address by calculating the latencies between the user's machine and multiple surrounding machines with fixed, known locations.
 However, even advanced systems like these can easily be bypassed, using IP spoofing techniques, proxy servers, VPNs, or by using anonymising networks such as TOR \cite{tor}.
@@
 Better solutions to this problem exist.
-\textit{Location proof systems} are systems which allow users of the system to \textit{prove} their location to another user.
-Examples of these are discussed in detail in section \ref{ssec:proof_systems}.
+\textit{Location proof systems} allow users of the system to \textit{prove} their location to another user, by creating \textit{location proofs}.
+Location proofs vary from system to system.
+In essence, a location proof is a piece of data, potentially signed or encrypted by another party, which attests the location of a user at a specific time.
+Examples of location proof systems are discussed in detail in section \ref{ssec:proof_systems}.
 
 \section{Distributed and decentralised systems}
-A distributed system is a system which distributes the computation of a task across multiple computers (nodes) connected over a network.
-These nodes then communicate to complete the task by passing messages over the network \cite{distributed}.
+A \textit{distributed} system is a system which distributes the computation of a task across multiple nodes (computers) connected over a network.
+These nodes then work together and communicate to complete the task by passing messages over the network \cite{distributed}.
 
@@
 Google therefore \textit{distributes} the task of calculating search indexes across multiple nodes.
-This two main advantages; It's far more efficient, because different index calculations can be computed on different nodes at the same time, and it's very scalable, because nodes can be added or removed from the network dynamically, to react to demand.
+This two main advantages; It is less time consuming, because different index calculations can be computed on different nodes at the same time, and it's scalable, because nodes can be added or removed from the network dynamically, to meet demand.
 
-A decentralised system is similar to a distributed system, except no node is in charge.
-Nodes in a decentralised network still communicate by passing messages to each other over the network, but unlike a distributed system, they don't act as slaves to a master.
+A \textit{decentralised} system is similar to a distributed system, except no node is in charge.
+Nodes in a decentralised network still communicate by passing messages to each other over the network, but unlike a distributed system, they arent assigned tasks by a central or master node.
 Bitcoin \cite{bitcoin} is a good example of a large-scale decentralised system.
-Two nodes in the Bitcoin network can choose to create a transaction by sending money between themselves, and they make the details of that transaction public.
-The two nodes created and published the transaction independently of all other nodes on the network.
+Two nodes in the Bitcoin network can choose to send money between themselves, creating a transaction.
+They make the details of that transaction public.
+The two nodes therefore create and publish the transaction iwithout coordination from a central node.
 
-In the context of a location proof system, I consider a distributed system to be one where the task of facilitating user proof request and creation is distributed across multiple \textit{worker nodes}, which are controlled and coordinated by a central node.
-This allows a higher volume of proofs to be created concurrently, while maintaining centralised control over the system.
+In the context of a location proof system, I consider a distributed location proof system to be one where the task of facilitating user proof request and creation is distributed across multiple \textit{worker nodes}, which are controlled and coordinated by a central node.
+This allows a higher volume of proofs to be created concurrently compared with using a single node, while maintaining centralised and simple control over the system.
 This is shown in figure \ref{fig:distributed_location}.
@@
 Nodes can create and publish location proofs between themselves, without the need for a central third party to coordinate the interaction (figure \ref{fig:decentralised_location}).
+This makes coordination more complex, but means that no node is considered to be ``in charge'' of the system.
 
@@
 Location proof systems are expected to be accurate and tamper-proof.
-For this reason, existing solutions have chosen to use a central authority to issue proofs, or to regulate proof issuance \cite{brassil, luo, khan}.
+For this reason, existing solutions \cite{brassil, luo, khan} have chosen to use a central authority to issue proofs, or to regulate proof issuance.
 
@@
 of HP Laboratories, operates by supplementing existing WiFi access points (\textit{AP's}) with \textit{femtocells}.
-A femtocell is a small cellular antenna that connects to a mobile carrier via the Internet.
+A femtocell \cite{femtocell} is a small cellular antenna that connects to a mobile carrier via the Internet, which allows mobile networks (e.g.
+networks used for calls and texts) to be extended on demand.
 Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data via Wi-Fi.
 This is possible because the central server in the location verification system has access to the mobile operator's user data.
+
 This solution requires investment in additional hardware to supplement existing WiFi access points, and requires access to mobile providers' user database to identify users locations (see figure \ref{fig:hp_labs}).
@@
 An attacker who succeeds in compromising the security of the central server can violate the privacy of the users of the system, and potentially track their location.
-This is because in this system, location proofs reside with the central server, so the user has no control over their security.
-The central system architecture is also vulnerable, in the sense that a resource availability attack such as a DDoS attack could render the central architecture unavailable, making location verification unavailable.
+This is because in this system, location proof data resides with the central server.
+This means that the user has no control over the security of their proofs, and an attacker could sieze them.
+The central system architecture is also vulnerable, in the sense that a resource availability attack such as a DDoS attack \cite{ddos} could render the central architecture unavailable, making location verification unavailable.
+\\
 
@@
 
+\begin{figure}[H]
+\resizebox {\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
+\caption{Proof encrypted with group signature (Adapted from Luo et al. \cite{luo})}
+\label{fig:luo_transaction}
+\end{figure}
+
 This system creates \textit{proactive} location proofs.
@@
 The user creates application-independent location proofs, and can use them at a later time with any application(s) he chooses.
+\\
 
@@
 
-\section{Ad-hoc networks}
+\section{Blockchain}
+In Bitcoin \cite{bitcoin}, the entire transaction history is stored in the \textit{blockchain}.
+This is a decentralised, append-only ledger (database) \cite{blueprint}.
+The blockchain is maintained by a network of \textit{miner} nodes competing to collect transactions into a new block, sign that block by solving a difficult puzzle known as a \textit{proof-of-work}, and append it to the ledger.
+It is used in Bitcoin to enforce consensus; every miner in the network agrees that all blocks in the blockchain are valid, due to the presence of their associated proof-of-work.
 
-\section{Blockchain}
+A proof-of-work is a solution (a numerical value) to a problem which is computationally expensive to solve, but computationally cheap to verify that the solution is correct.
+As blocks are added to the blockchain, the amount of work required to generate the proofs-of-work for the entire chain increases.
+Because proof-of-work solutions also incorporate some information about the previous block in the chain, changing data inside a block in the blockchain would not just require regeneration of the proof-of-work for that block, but for all successive blocks as well.
+Therefore the blockchain is tamper-proof, assuming that the majority of the CPU power in the miner network is controlled by  honest nodes \cite{bitcoin}.
 
-\section{Goals of a decentralised proof system}
+To add a transaction to the blockchain, a user will send the transaction to a miner node.
+That miner node propagates the transaction to other miner nodes in the network, and they each try to include it in the next block by solving the proof-of-work.
+A simple overview of the system is shown in figure \ref{fig:blockchain}.
+
+Once a proof-of-work has been solved, the solution is distributed to all other miners in the network to prove that the solver expended significant computational effort to solve it.
+This is a proof of resource ownership, meaning that by solving the proof-of-work, the miner has shown that it has significant computational resources and is therefore considered a valid miner.
+Once other miners in the network verify that the proof-of-work is correct, the block (and therefore all transactions contained in it) is considered the newest block in the tamper-proof chain, and miners begin working on the next block.
+
+\begin{figure}[H]
+\begin{center}
+\input{diagrams/blockchain.tex}
+\end{center}
+\caption{Blockchain overview}
+\label{fig:blockchain}
+\end{figure}
+
+\section{Design goals}
+Before designing the system, a number of goals must be defined and an attempt made to satisfy them in the design. My design goals are listed below.
+
+\begin{itemize}
+	\item The system must be \textit{privacy preserving}.
+It must not be possible for a malicious user to obtain any additional information from an honest user than the information the honest user intended to release.
+	\item False location proofs must be detectable. It must be possible to detect any location proofs attempting to prove false information.
+	\item The system must be decentralised, and cannot rely on any central nodes. This is discussed in section \ref{ssec:centralised}.
+	\item The design must conform to the desirable properties defined in OTIT (discussed in section \ref{ssec:otit}).
+	\item The system must not be vulnerable to any known threats (section \ref{ssec:threats}).
+\end{itemize}
+
+\subsection{Central services} \label{ssec:centralised}
+Location proof systems which rely on central noes, such as those discussed in section \ref{ssec:proof_systems}, have a fundamental weakness.
+These systems assume that the central node is honest, always available, and cannot be compromised by an attacker.
+Since the central node is in charge of coordinating the system, compromising it allows an attacker potentially unlimited control over the system.
+This completely violates a users privacy in a location verification system, as the central node may contain sensitive information about users and their location, or a means of retrieving sensitive information, such as decryption keys.
+Users of the system also have to assume that the central node is available at all times, otherwise the system is considered unavailable, or ``down''.
+
+These problems do not occur in a decentralised location proof system, because no node is considered to be ``in charge''.
+This lack of authority prevents privacy breaches, but presents other issues.
+System coordination, which is easily maintained by the central node in a centralised system, is now maintained by each participant in the decentralised system.
+
+\subsection{OTIT} \label{ssec:otit}
+Khan et al. present the \textit{OTIT} model, a ``model for designing secure location provenance'' \cite{otit}. It defines the following 8 desirable properties of a location proof system:
+\begin{itemize}
+	\item[] \textbf{Chronological}: Location proofs should be ordered according to the sequence of their creation.
+	\item[] \textbf{Order preserving}: The order in which the proofs were entered into the proof chain should always be maintained.
+	\item[] \textbf{Verifiable}: A Verifier should be able to verify or reject the claim by the user that he has visited the given location(s).
+	\item[] \textbf{Tamper evident}: A Verifier should be able to detect if the proof chain has been tampered with or modified by an unauthorised party.
+	\item[] \textbf{Privacy preserved}: When the proof chain is verified for specific location proofs, privacy is preserved for the other location proofs within the chain.
+	\item[] \textbf{Selective In-sequence privacy}: The user should be able to choose not to reveal some location proofs within the proof chain when seeking verification.
+	\item[] \textbf{Privacy protected chronology}: The system should ensure that the user does not hide important information from the items within the subset of the proof chain.
+	\item[] \textbf{Convenience and derivability}: The system shold ensure that the user does not burden the Verifier with a large amount of data to analyse in order to verify his location.
+\end{itemize}
+
+\subsection{Threats} \label{ssec:threats}
+A number of related publications \cite{luo,khan} have identified various potential threats (or attacks) on location verification systems. These are outlined below.
+
+\begin{itemize}
+	\item[] \textbf{False presence}: A dishonest user tries to obtain a location proof for a false location.
+	\item[] \textbf{Malicious intruders}: A malicious intruder offers to help another user prove a false location, but doesn't prove a false location for himself.
+	\item[] \textbf{Curious users}: A curious user learns another user's identity while the user is acquiring the location proof.
+	\item[] \textbf{Malicious applications}: The application that the user is proving his location to takes advantage of the user's information.
+	\item[] \textbf{Eavesdroppers}: An eavesdropper intercepts or modifies communication between two honest users.
+	\item[] \textbf{Wormhole attacks}: An attacker records network traffic in one location and replays it in another location (at another time).
+	\item[] \textbf{Weak identities}: A user gives his public key or identity to another colluding user in order to create a location proof.
+	\item[] \textbf{False timestamping (backdating, future dating)}: In a backdating attack, the attacker creates a location proof with a past timestamp.
+In future dating, the attacker creates a location proof with a future timestamp
+	\item[] \textbf{Implication}: A malicious user, or group of colluding malicious users, create a false location proof for an honest user.
+	\item[] \textbf{False assertion}: Two malicious users collude to create a false location proof for themselves.
+	\item[] \textbf{Proof switching}: A malicious user modifies one of its existing honest proofs to spoof a false location.
+	\item[] \textbf{Relay attack}: A malicious user creates a location proof with an honest user by relaying his requests through a colluding \textit{proxy user}, who is physically present at a location that the malicious user wishes to create false proofs at.
+	\item[] \textbf{Sybil attack}: A Sybil attack occurs when a single malicious user of the system generates multiple \textit{pseudoidentities} and masquerades as multiple users \cite{sybil}.
+\end{itemize}

### 2016-04-12 thesis/design.tex
Updates after proofreading Background chapter

@@
-The location proof system we propose allows \textit{mobile nodes} to create location proofs for each other after physically meeting.
+The location proof system I propose allows \textit{mobile nodes} to create location proofs for each other after physically meeting.
 When two mobile nodes are in close physical proximity, they initiate a transaction over a short range, ad-hoc network such as Bluetooth.
@@
 \end{figure}
+
+\begin{itemize}
+	\item[] \textbf{(1)} Before the transaction begins, both nodes generate a new entry in their nonce list, and generate a new identity from that nonce.
+	\item[] \textbf{(2)} Node A sends its identity to Node B, along with its observed current timestamp $ts_A$ and current GPS location $loc_A$.
+	\item[] \textbf{(3)} Node B verifies that the observed timestamp and GPS location received from Node A are within an acceptable difference from its own observations.
+This difference is defined by some system constant $\epsilon$.
+	\item[] \textbf{(4)} If Node B verifies the parameters received from Node A, it will respond with its own identity and observations for A to verify.
+	\item[] \textbf{(5)} Node A verifies that the parameters received from B differ by no more than $\epsilon$ from its own observed parameters.
+	\item[] \textbf{(6)} Node A sends $KP_{An}$, its $nth$ \textit{Key Packet}. Key Packets are used to provide alibi credibility, and are discussed in section \ref{sssec:key_packets}.
+	\item[] \textbf{(7)} B responds with its own Key Packet.
+	\item[] \textbf{(8)} Both nodes generate their own transaction $T$, using their alibi's Key Packets. These are then published onto the public blockchain.
+\end{itemize}
 

### 2016-04-12 thesis/introduction.tex
Updates after proofreading Background chapter

@@
 \section{Project and Motivation}
-Location verification is the process of verifying whether or not a  node (computer) is physically present at the location it claims to be.
-Existing location verification systems attept to provide this service using centralised, trusted ``authoritive'' nodes to provide proof of another node's location.
-These approaches require investment in infrastructure, and are subject to attacks on privacy and denial of service attacks.
-This project aims to present a \textit{decentralised} solution to this problem, in which there is no ``authoritive source'' trusted and relied upon to provide and store sensitive location information.
+Location verification is the process of verifying whether a \textit{node} (computer) is physically present at a location it claims to be.
+Existing location proof systems attept to use centralised, trusted ``authoritive'' nodes to provide proof of another node's location.
+These approaches require investment in infrastructure, and are subject to privacy violation and denial of service attacks.
+This project aims to present a \textit{decentralised} solution to this problem.
+A decentralised location proof system is a system in which there is no ``authoritive source'' trusted and relied upon to provide and store sensitive location information.
 
-This project describes a decentralised location proof system that operates on mobile devices (mobile nodes).
-I propose a design in which location proofs are obtained by using other untrusted mobile nodes as \textit{alibi's}.
-Proofs will be created by communicating over an ad-hoc bluetooth network, encrypted, and published on a public append-only bulletin board, known as a \textit{blockchain}.
+This project describes a decentralised location proof system that is capable of operating on \textit{mobile nodes} (mobile devices).
+I propose a design in which location proofs are obtained using other untrusted mobile nodes as \textit{alibi's}.
+Proofs will be created as two mobile nodes communicate over an ad-hoc bluetooth network, transfer encrypted location information, and publish it on a public append-only bulletin board, known as a \textit{blockchain}.
 The decentralised nature of the system means that there is no single point of failure, no entity controlling the security of every node's location proofs, and no entity capable of violating another node's privacy.
+This is because in a decentralised system, no node is ``in charge'', and no node has more authority in the system than any other node.

### 2016-04-12 thesis/thesis.tex
converting thesis to Report format
Updates after proofreading Background chapter

@@
+\documentclass[12pt]{report}
+
 \title{Decentralised location proof system}
 
-\documentclass[12pt,titlepage]{article}
+\usepackage[utf8]{inputenc}
+\usepackage{graphicx}
+\usepackage{subcaption}
 
@@
 \usepackage{float}
-
-\usepackage{chngcntr}
-\counterwithin{figure}{section}
-
-\renewcommand{\thefigure}{\thesection.\arabic{figure}}
+\usepackage{subfig}
 
@@
 
-\begin{abstract}
-\end{abstract}
-\newpage
-
 \tableofcontents
@@
 
+\chapter{Introduction}
 \input{introduction.tex}
-\newpage
+
+\chapter{Background}
 \input{background.tex}
-\newpage
+
+\chapter{Design}
 \input{design.tex}
-\newpage
+
+\chapter{Evaluation}
 \input{evaluation.tex}
+
+\chapter{Future work}
 
@@
 \bibitem{luo}
-  Luo, W., Hengartner, U.,
+  W. Luo, U. Hengartner,
   ``Proving your Location without giving up your Privacy'',
@@
 \bibitem{khan}
-  R. Khan, S. Zawoad, M. M. Haque, and R. Hasan,
+  R. Khan, S. Zawoad, M. Haque, and R. Hasan,
   ```Who, When, and Where?' Location Proof Assertion for Mobile Devices'',
@@
 \bibitem{otit}
-  Khan, R., Zawoad, S., Haque, M., Hasan, R.
+  R. Khan, S. Zawoad, M. Haque, and R, Hasan.
   ``OTIT: Towards secure provenance modeling for location proofs'',
@@
 \bibitem{sybil}
-  Douceur, J.R.,
+  J.R. Douceur,
   ``The sybil attack'',
@@
 \bibitem{distributed}
-  Coulouris, George; Jean Dollimore; Tim Kindberg; Gordon Blair,
+  G. Coulouris, J. Dollimore, T. Kindberg, and G. Blair,
   ``Distributed Systems: Concepts and Design (5th Edition)'',
@@
 
+\bibitem{femtocell}
+  V. Chandrasekhar, J. Andrews, and A. Gatherer,
+  ``Femtocell Networks: A Survey'',
+  IEEE Communications Magazine, Vol. 46, No. 9, pps. 59-67,
+  September 2008
+
+\bibitem{ddos}
+  J. Mirkovic, P. Reiher,
+  ``A taxonomy of DDoS attack and DDoS defense mechanisms'',
+  ACM SIGCOMM Comput. Commun. Rev. 34, 2, 39–53,
+  2004
+
 \end{thebibliography}

### 2016-04-12 thesis/background.tex
Updates after proofreading Introduction and Design chapters

@@
 \section{Proving your location}
-As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, we are losing the security that previously existed by requiring physical interaction between humans to transfer sensitive data
+As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, we are losing the security that previously existed by requiring physical interaction between humans to transfer sensitive data.
 
@@
 \begin{figure}[H]
-\resizebox {\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
-\caption{Proof encrypted with group signature (Adapted from Luo et al. \cite{luo})}
+\begin{center}
+\resizebox {0.7\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
+\caption{Proof request with group signature (Adapted from Luo et al. \cite{luo})}
 \label{fig:luo_transaction}
+\end{center}
 \end{figure}
@@
 	\item[] \textbf{Malicious intruders}: A malicious intruder offers to help another user prove a false location, but doesn't prove a false location for himself.
-	\item[] \textbf{Curious users}: A curious user learns another user's identity while the user is acquiring the location proof.
+	\item[] \textbf{Curious users}: A curious user learns another user's identity by monitoring its location proofs.
 	\item[] \textbf{Malicious applications}: The application that the user is proving his location to takes advantage of the user's information.

### 2016-04-12 thesis/design.tex
Updates after proofreading Introduction and Design chapters

@@
-The location proof system I propose allows \textit{mobile nodes} to create location proofs for each other after physically meeting.
-When two mobile nodes are in close physical proximity, they initiate a transaction over a short range, ad-hoc network such as Bluetooth.
+The location proof system I propose allows \textit{mobile nodes} to create location proofs by initiating an \textit{exchange} with another anonymous mobile node.
+When two mobile nodes are in close physical proximity, they initiate an exchange in the background over a short range, ad-hoc network such as Bluetooth.
+On completion of the exchange, both nodes can generate their own \textit{transaction}, a cryptographically secure proof of location, attested by the other mobile node.
 
-To create a transaction, two mobile nodes anonymously share their GPS coordinates and current time over a short-range network.
-Both nodes then check that these parameters don't differ by more than some value $\epsilon$.
+To create a transaction, two mobile nodes anonymously exchange their GPS coordinates and current time over the ad-hoc network.
+Both nodes then check that these parameters don't differ from their own observed parameters by more than some value $\epsilon$.
 Once satisfied, they each create an encrypted, privacy-protecting transaction logging their location and the identity of the other mobile node (the \textit{alibi}) used to create the transaction.
 This transaction is published onto a public, append-only bulletin board known as a \textit{blockchain} \cite{blueprint}.
+Once given permission from a mobile node, a \textit{Verifier node} can consult the data in blockchain and determine whether or not the mobile node is present at its claimed location.
 
-Once given permission from a mobile node (by transferring decryption keys), a \textit{Verifier node} can consult the data in blockchain and determine whether or not the mobile node is present at its claimed location.
-The blockchain is managed by a network of \textit{Miner nodes}, who collect transactions from mobile nodes, distribute them across the network, and try to create a new \textit{block} of transactions by attempting to solve a \textit{proof-of-work} puzzle.
-
-Any mobile node acting as an alibi in a transaction will share details of its most recent transactions with the other mobile node in the transaction.
-This means that when the mobile node seeks verification from a Verifier node, the Verifier can examine the mobile node's alibi's, and each of the alibi's recent alibi's, forming a large graph of connections which can be used to verify or reject the mobile nodes claimed location.
+Any mobile node acting as an alibi in a transaction will share details of its most recent transactions with the other mobile node in the exchange.
+This means that when the mobile node seeks verification from a Verifier node, the Verifier can examine the mobile node's alibi's, and each of the alibi's recent alibi's, forming a large tree of connections which can be used to verify or reject the mobile nodes claimed location.
 Only the owner of the transaction can give permission to a Verifier to check its location history, by providing the Verifier with the keys needed to decrypt the transactions.
@@
 \begin{enumerate}[label=\textbf{\arabic*}.]
-\item Two mobile nodes in close physical proximity create a transaction.
-\item The mobile nodes each publish their transaction to a Miner node.
-\item The Miner node distributes the transaction across the Miner network.
-\item One Miner node solves the proof-of-work for a block of transactions, and the new block of transactions is appended to the blockchain.
+\item Two mobile nodes come in close physical proximity and create an ad-hoc network, over which they initiate an exchange and each create a transaction.
+\item Both mobile nodes publish their own transaction to a Miner node.
+\item The Miner node who received the transaction distributes it across the Miner network.
+\item One Miner node solves the proof-of-work for a block of transactions, and the new block is appended to the blockchain.
 \item A mobile node requests verification from a Verifier node (request structure is explained in section \ref{ssec:verification}).
 \item The Verifier node uses the public blockchain to examine the requesting node's transactions and determine their validity.
-\item The Verifier accepts or rejects the  mobile node's claimed location based on its transactions in the blockchain. 
+\item The Verifier accepts or rejects the  mobile node's claimed location based on its analysis of the transactions in the blockchain. 
 \end{enumerate}
@@
 
-When a mobile node is created, it generates a public/private key pair.
+When a mobile node is first joins the network, it generates a public/private key pair.
 To maintain anonymity, the mobile node will use the public key to encrypt \textit{nonces} to create \textit{identities}, and use these to identify itself in a transaction.
@@
 During the verification stage, the node will provide the Verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions (see figure \ref{fig:verify_request}).
-This allows the Verifier to calculate all of the node's identities, and prove that they were all created by the same node, and can then retrieve the transactions associated with those identities from the blockchain.
-The Verifier will also ensure that the node owns the private key associated with the provided public key, to prevent identity theft.
+This allows the Verifier to calculate all of the node's identities, and prove that they were all created by the same node.
+The Verifier can then retrieve the transactions associated with those identities from the blockchain.
+The Verifier will also ensure that the node owns the private key associated with the provided public key, to prevent a weak identity attack.
 
@@
 A \textit{Nonce List} is simply a list of all of the nonces a mobile node has used so far to generate identities.
-When a mobile node generates a new identity, it must first generate a new nonce which is then encrypted to create the identity.
+When a mobile node wishes to generate a new identity, it must first generate a new nonce which is then encrypted to create the identity.
 The nonce is appended to the mobile node's nonce list, so it can be used later during verification (see section \ref{ssec:verification}).
 
+\begin{figure}[H]
+\resizebox {\columnwidth} {!} {\input{diagrams/nonce_list.tex}}
+\caption{Identity generation from Nonce List}
+\label{fig:nonce_list}
+\end{figure}
+
+In figure \ref{fig:nonce_list} above, nonce $0047$ is encrypted with $K^+$ to create identity $ee3bc14$.
+By providing the nonce list and $K^+$, a node can prove that it created all of the identities in the identities list.
+It must also verify that it owns $K^-$, its private key.
+
 \subsection{Identity duplication}
-Since all identities are generated from random nonces, there is nothing to stop two nodes from generating the same identity and using it in different transactions.
-It is therefore possible that during verification, a Verifier node may find multiple transactions with the same ID in the blockchain.
-The Verifier will have a decryption key for the transaction it is searching for, which will only be able to decrypt one of the transactions with the duplicate ID.
-The Verifier will try to decrypt each one until it finds one that can be decrypted successfully.
+Since all identities are generated from random nonces, there is nothing to prevent two nodes from generating the same identity and using it in different transactions.
+It is therefore possible that during verification, a Verifier node may find multiple transactions with the same ID while searching the blockchain.
+The Verifier will have a decryption key for the transaction it is searching for, which will only successfully decrypt one of the transactions with the duplicate ID.
+The Verifier will try to decrypt each one until it finds the one that can be decrypted successfully.
 
@@
 \section{Transactions} \label{sec:transactions}
-During a transaction between two nodes, a number of different items must be shared and calculated.
-Figure \ref{fig:transaction} describes an honest, successful transaction, assuming an ad-hoc Bluetooth network has already been set up between nodes $A$ and $B$.
+During an exchange between two nodes, a number of different items must be shared and calculated.
+Figure \ref{fig:transaction} describes and explains an honest, successful exchange, assuming an ad-hoc Bluetooth network has already been set up between nodes $A$ and $B$.
 
 \begin{figure}[H]
-\resizebox {\columnwidth} {!} {\input{diagrams/transaction.tex}}
-\caption{Honest, successful transaction}
+\begin{center}
+\resizebox {1.1\columnwidth} {!} {\input{diagrams/transaction.tex}}
+\caption{Honest, successful exchange}
 \label{fig:transaction}
+\end{center}
 \end{figure}
@@
 \begin{itemize}
-	\item[] \textbf{(1)} Before the transaction begins, both nodes generate a new entry in their nonce list, and generate a new identity from that nonce.
+	\item[] \textbf{(1)} Before the exchange begins, both nodes generate a new entry in their nonce list (e.g. $NL_A[n]$), and generate a new identity from that nonce (e.g. $ID_A[n]$).
 	\item[] \textbf{(2)} Node A sends its identity to Node B, along with its observed current timestamp $ts_A$ and current GPS location $loc_A$.
@@
 	\item[] \textbf{(7)} B responds with its own Key Packet.
-	\item[] \textbf{(8)} Both nodes generate their own transaction $T$, using their alibi's Key Packets. These are then published onto the public blockchain.
+	\item[] \textbf{(8)} Both nodes generate their own transaction $T$, using their alibi's Key Packets. These are then used to generate $P$, the data published onto the public blockchain.
 \end{itemize}
 
-Where:
-\begin{itemize}[noitemsep,topsep=0pt]
-	\item[] $\mathbf{NL_A[n]}$ is the $n$th nonce in $A$'s \textit{Nonce List}, which is used to generate $ID_{An}$ (see section \ref{sssec:nonce_list}).
-\end{itemize}
-
-\null
+\subsection{Key Lists}
 When a node is initialised, it must begin to record two \textit{Key Lists} for itself.
@@
 
-After creating an ad-hoc Bluetooth network between nodes $A$ and $B$, the first step in the transaction is for both nodes to share their IDs, and agree upon a GPS location and current time.
-Nodes likely won't share the exact same GPS coordinates or time, but once the values don't differ by more than some small constant $\epsilon$, the nodes will continue with the transaction.
-If node $A$ claims a GPS location or timestamp that differs from what node $B$ senses by more than $\epsilon$, node $B$ will abort the transaction.
-
-After nodes agree upon the parameters of the transaction, they exchange their previous ID, along with their \textit{Key Packets}.
-A \textit{Key Packet} is a list of keys used in a node's $n$ most recent transactions, along with the transaction ID's if necessary.
-This allows node $A$ to decrypt node $B$'s $m$ most recent transactions, therefore providing an alibi for node $A$.
-
 \subsection{Transaction creation}
 Once nodes have exchanged \textit{Key Packets}, their communication is finished and they can close their ad-hoc channel.
-Each node creates a new transaction object, $T$, to publish onto the public blockchain.
-The following transaction data will be calculated by node $A$, after communicating with node $B$:
+Each node creates a new transaction, $T$, and generates data $P$ to publish onto the public blockchain.
+The following transaction will be created by node $A$, after communicating with node $B$:
 \\
 
-$T_{An} = KL_{AT}[n](ts|loc|ID_{An}|ID_{Bm}|KP_{Bm})$
+$T_{An} = KL_{AT}[n](ts|loc|ID_{A}[n]|ID_{B}[m]|KP_{Bm})$
 \\
@@
 	\item[] $\mathbf{n}$ is node $A$'s current transaction number (i.e. $A$ has published $n-1$ transactions before now).
-	\item[] $\mathbf{KL_{AT}}$ is one of $A$'s \textit{Key Lists}, used to encrypt transactions.	
+	\item[] $\mathbf{KL_{AT}}$ is $A$'s transaction \textit{Key Lists}, used to encrypt transactions.	
 	\item[] $\mathbf{ts}$ is the timestamp of the transaction, as recorded by node $A$.
 	\item[] $\mathbf{loc}$ is the GPS coordinates of the transaction, as recorded by node $A$.
-	\item[] $\mathbf{ID_{An}}$ is $A$'s $nth$ identity, used for this transaction only.
-	\item[] $\mathbf{ID_{Bm}}$ is $B$'s $mth$ identity.
+	\item[] $\mathbf{ID_{A}[n]}$ is $A$'s $nth$ identity, used for this transaction only.
+	\item[] $\mathbf{ID_{B}[m]}$ is $B$'s $mth$ identity.
 	\item[] $\mathbf{KP_{Bm}}$ is $B$'s \textit{Key Packet} at time $m$. Its exact contents are discussed in more detail in section \ref{sssec:key_packets}
@@
 The Verifier must be able to prove that the proof chain provided by the mobile node has not been chronologically re-ordered.
+This is the ``order preserving'' property of OTIT \cite{otit}.
 The transaction must therefore be accompanied by a link to the node's chronologically previous transaction.
-This link must be encrypted, along with the transaction timestamp, to prevent a curious user from monitoring the public blockchain to observe a user's transaction publishing activity.
-$A$'s copy of the transaction log $P_{An}$ will therefore be in the form:
+This link is encrypted with $KL_{AL}[n]$, $A$'s $nth$ \textit{link} key list, to prevent a curious user from monitoring the public blockchain to observe a user's transaction publishing activity.
+The timestamp $ts_A$ is also included in the backwards-chaining data, to verify the ``order preserving'' property.
+$A$'s transaction data $P_{An}$ will therefore be in the form:
 \\
 
-$P_{An} = ID_{An}|KL_{AL}[n](ID_{An-1}|ts_A)|T_{An}$
+$P_{An} = ID_{An}|KL_{AL}[n](ID_{A}[n-1]|ts_A)|T_{An}$
 
@@
 To publish $P_{An}$, $A$ must send $P_{An}$ to a miner node, who will add it to its \textit{pending transaction} queue, and send it to other miners in the network to add it to their queues as well.
-The transaction will then be signed into the next block in the blockchain.
+The transaction will signed into the next block in the blockchain, once the next proof-of-work is solved.
+
+Node $B$, $A$'s alibi for the above transaction example, will publish $P_{Bm}$ after the exchange.
+If $B$'s transaction is not available on the blockchain, $A$'s transaction will be considered invalid and disregarded during verification.
+A transaction $T_A$ in the blockchain must be accompanied by a reference to some valid alibi transaction $T_B$, and $T_B$ must reference $T_A$, otherwise the proof is not considered credible by a verifier.
 
@@
 In this case, $KL_{BT}[m-1]$ has not been included with $KL_{BL}[m-1]$, in order to protect the privacy of this transaction.
-This may be needed, for example, if node $B$ doesn't want to allow anyone to decrypt any transactions he has created withing 5km of his home, in order to protect his privacy.
+This means that a node who received this key packet will not be able to decrypt $B$'s transaction $T_{Bm-1}$, but can still prove that a transaction exists at that time and in the correct sequence, as $B$ will still provide $KL_{BL}[m-1]$.
+This may be needed, for example, if node $B$ doesn't want to allow anyone to decrypt any transactions he has created within 5km of his home, in order to protect his privacy.
 
@@
 To abort the transaction, $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain.
-This means that even if $M$ fabricates some data from $A$ and publishes a transaction onto the blockchain, the matching transaction from $A$ will not be present.
-Any transaction on the blockchain that do not contain a reference to a valid  alibi transaction will be disregarded during verification.
+This means that even if $M$ fabricates some data from $A$ and publishes a transaction onto the blockchain, the matching transaction from $A$ will not be present, so the transaction will be disregarded by any verifiers.
 
-\begin{figure}[h]
+\begin{figure}
 \resizebox {\columnwidth} {!} {\input{diagrams/aborted_transaction.tex}}
@@
 
+\clearpage
 \section{Verification} \label{ssec:verification}
-\begin{minipage}{0.5\linewidth}
 In the verification stage, a mobile node tries to prove its location to a Verifier node, e.g.
 a bank.
-To do this, the mobile node sends the Verifier a number of parameters, as shown in Figure \ref{fig:verify_request}:
+To do this, the mobile node sends the Verifier a number of parameters, as shown in Figure \ref{fig:verify_request}.
+
+\begin{figure}[H]
+\begin{center}
+\resizebox {0.8\columnwidth} {!} {\input{diagrams/verify_request.tex}}
+\caption{Verification request}
+\label{fig:verify_request}
+\end{center}
+\end{figure}
+
 \begin{itemize}[noitemsep,topsep=0pt]
-	\item[] $\mathbf{ID_{An-1}}$ is the ID of $A$'s most recently published transaction.
+	\item[] $\mathbf{ID_{A}[n-1]}$ is the ID of $A$'s most recently published transaction.
 	\item[] $\mathbf{KP_{An-1}}$ is $A$'s key packet up to transaction $n-1$, and includes keys for as many transactions as $A$ feels is appropriate in order to receive verification.
@@
 	\item[] $\mathbf{NP_{An-1}}$ is $A$'s \textit{Nonce Packet}, a subset of its \textit{Nonce List} (section \ref{sssec:nonce_list}).
-A Nonce Packet is the list of the nonces used to generate $A$'s most recent IDs, up to $n-1$., that $A$ is willing to share with the Verifier.
+A Nonce Packet is the list of the nonces used to generate $A$'s most recent IDs, up to $n-1$, that $A$ is willing to share with the Verifier.
 \end{itemize}
-\end{minipage}
-\hfill
-\begin{minipage}[c]{0.5\linewidth}
+
+\null
+The goal of the verification stage is for the Verifier to either accept or reject the location that the user is claiming.
+Given $ID_{A}[n-1]$ and $KP_{An-1}$, a Verifier is able to retrieve $A$'s previous transactions, and the transactions of all of its alibi's.
+This will allow the Verifier to recursively inspect the transactions of all alibi's used in a nodes transactions, until it is satisfied that the location can be verified or rejected.
+This recursive inspection can be visualised as a tree, as shown in figure \ref{fig:tree}.
+
 \begin{figure}[H]
-\input{diagrams/verify_request.tex}
-\caption{Verification request}
-\label{fig:verify_request}
+\begin{center}
+\resizebox {0.7\columnwidth} {!} {\input{diagrams/tree.tex}}
+\caption{Alibi chain relationship tree}
+\label{fig:tree}
+\end{center}
 \end{figure}
-\end{minipage}
 
-The goal of the verification stage is for the Verifier to either accept or reject the location that the user is claiming.
-Given $ID_{An-1}$ and $KP_{An-1}$, a Verifier is able to retrieve $A$'s previous transactions, and the transactions of all of its alibi's.
+In this figure, the red chain is the requesting node's transaction chain.
+The blue chains are the red node's alibis' transaction chains, and the black chains are the blue node's alibis' transaction chains.
+If the verifier wishes to recurse more, it could inspect the black node's alibis' transaction chains.
+Note that this is a simple example, and $n = 3$, the length of the transaction chain subset provided for verification.
+In reality $n$ should be much larger.
 
@@
 \begin{itemize}
-	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, then the node is likely attempting a poorly-constructed Sybil attack, and the Verifier will reject his verification request.
+	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, they won't be considered credible alibis, and the Verifier will reject his verification request.
+	\item \textbf{Transaction relevance:} if the Verifier considers the transactions it receives to be out of date, they will be rejected on the grounds that they are no longer relevant.
 	\item \textbf{Alibi reuse:} if the Verifier can prove that alibi’s are being reused frequently, then it will reject the verification request.

### 2016-04-12 thesis/introduction.tex
Updates after proofreading Introduction and Design chapters

@@
 This is because in a decentralised system, no node is ``in charge'', and no node has more authority in the system than any other node.
+
+\section{Report outline}
+This report consists of four additional chapters, listed biefly below.
+
+\subsection{Background}
+Chapter 2 begins with a brief introduction to the problem space.
+A brief explanation of decentralised and distributed networks, as well as the blockchain is then presented, in the context of location proof systems.
+The chapter closes with an explanation of the design goals defined for this project.
+
+\subsection{Design}
+Chapter 3 explains the design of the decentralised location proof system in detail. It begins with an overview of the entire system, and then details the design of each specific part.
+
+\subsection{Evaluation}
+Chapter 4 presents an evaluation of the system described in the design, with respect to the goals laid out in Chapter 3.
+
+\subsection{Future work}
+Chapter 5 presents the conclusions of the project, and details interesting areas for possible future work relating to the project.

### 2016-04-15 thesis/background.tex
Adding evaluation chapter

@@
 
-\section{Design goals}
+\section{Design goals} \label{sec:design_goals}
 Before designing the system, a number of goals must be defined and an attempt made to satisfy them in the design. My design goals are listed below.
@@
 \begin{itemize}
-	\item[] \textbf{False presence}: A dishonest user tries to obtain a location proof for a false location.
+	\item[] \textbf{False presence}: A dishonest user attempts to obtain a location proof for a false location.
 	\item[] \textbf{Malicious intruders}: A malicious intruder offers to help another user prove a false location, but doesn't prove a false location for himself.

### 2016-04-15 thesis/design.tex
Adding evaluation chapter

@@
 
-\subsection{Key Lists}
+\subsection{Key Lists} \label{ssec:key_lists}
 When a node is initialised, it must begin to record two \textit{Key Lists} for itself.
@@
 
-\subsection{Aborting transactions}
-A node may decide to abort a transaction if it thinks it is in contact with a malicious node.
+\subsection{Aborting exchanges} \label{ssec:aborting_exchanges}
+A node may decide to abort an exchange if it thinks it is in contact with a malicious node.
 In figure \ref{fig:aborted_transaction}, node $A$ encounters a malicious node $M$, who tries to spoof its identity with $A$.
-Node $A$ will abort the transaction once it notices that $|ts_A-ts_M| \geq \epsilon_{ts}$, or $|loc_A-loc_M| \geq \epsilon_{loc}$.
+Node $A$ will abort the exchange once it notices that $|ts_A-ts_M| \geq \epsilon_{ts}$, or $|loc_A-loc_M| \geq \epsilon_{loc}$.
 
-To abort the transaction, $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain.
-This means that even if $M$ fabricates some data from $A$ and publishes a transaction onto the blockchain, the matching transaction from $A$ will not be present, so the transaction will be disregarded by any verifiers.
+To abort the exchange, $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain.
+This means that even if $M$ fabricates some data from $A$ and publishes a transaction onto the blockchain, the matching transaction from $A$ will not be present, so $M$'s transaction will be disregarded by any verifiers.
 
@@
 \resizebox {0.7\columnwidth} {!} {\input{diagrams/tree.tex}}
+\vspace{-3cm}
 \caption{Alibi chain relationship tree}
@@
 
-In this figure, the red chain is the requesting node's transaction chain.
-The blue chains are the red node's alibis' transaction chains, and the black chains are the blue node's alibis' transaction chains.
 If the verifier wishes to recurse more, it could inspect the black node's alibis' transaction chains.

### 2016-04-15 thesis/diagrams/uncredible_tree.tex
Adding evaluation chapter

\begin{tikzpicture}[every node/.style={draw,shape=circle,fill=black}]

\node[fill=white] (A) at (0,0) {};
\node[fill=white] (B) at (0,1) {};
\node[fill=white] (C) at (0,2) {};
\node[fill=white] (D) at (0,3) {};
\node[fill=white] (E) at (0,4) {};

\node[fill=white,label=right:Requesting node's transactions] (L1) at (-3,-1) {};
\node[fill=gray,label=right:Requesting node's alibis transactions] (L2) at (-3,-1.5) {};

\draw (A) -- (B) (B) -- (C) (C) -- (D) (D) -- (E);

\node[fill=gray] (F) at (1,1) {};
\draw (A) -- (F);

\node[fill=gray] (G) at (-1,2) {};
\draw (B) -- (G);

\node[fill=gray] (H) at (1,3) {};
\draw (C) -- (H);

\node[fill=gray] (I) at (-1,4) {};
\draw (D) -- (I);

\node[fill=gray] (J) at (1,5) {};
\draw (E) -- (J);

\end{tikzpicture}

### 2016-04-15 thesis/evaluation.tex
Adding evaluation chapter

@@
-In this paper, we have presented a model for a location proof system which aims to preserve privacy and prevent false proofs from being created.
+The previous chapter introduced a model for a decentralised location proof system.
+This chapter will present an evaluation of the model with respect to the design goals defined in section \ref{sec:design_goals}.
 
 \section{OTIT conformance}
-We can compare our model to OTIT \cite{otit}, a list of features and requirements necessary for designing any secure location proof scheme. OTIT presents 8 such requirements:
-\begin{enumerate}
-\item[] \textbf{Chronological}: The chronological property of OTIT ensures that transactions are published in the order they were created.
-In our system we do not enforce this property at the time of transaction publication.
+As explained in section \ref{ssec:otit}, the OTIT model \cite{otit} defines 8 desirable properties of a lcoation proof system.
+The model introduced in chapter \ref{ch:design} is evaluated with respect to OTIT below.
+
+\subsection{Chronological}
+The chronological property of OTIT states that location proofs should be ordered according to the sequence of their creation.
+
+This property is not enforced at the time of transaction publication in this system.
 This is to avoid revealing any transaction information to the miner nodes, therefore preserving the privacy of the transaction owner.
-Instead, we enforce this property at the time of verification.
-The chronological link created by adding $KL_{AT}(ID_{A-1}|ts_A)$ to the transaction will allow Verifier nodes to prove that the transaction is chronologically ordered, preserving OTIT's ``Chronological'' property.
+Instead, the Chronological property is enforced at the time of verification.
+The chronological link created by adding $KL_{AT}(ID_{A}[n-1]|ts_A)$ to the published transaction will allow Verifier nodes to prove that the transaction is chronologically ordered.
+Therefore the system preserves OTIT's ``Chronological'' property.
 
-\item[] \textbf{Order preserving}: This property states that the order of transactions cannot be modified after they are created.
-In our system, a blockchain is used to store transactions.
+\subsection{Order preserving}
+This property states that the order in which location proofs were entered into the proof chain should be maintained.
+
+In this system, a blockchain is used to store location proof transactions.
 In a blockchain, new blocks are added in a linear, chronological order, and cannot be modified so long as the majority of miners in the network are honest \cite{blueprint}.
+
+A block consists of a number of transactions.
+These transactions are included in the block in the order they were received by the miner who solved the proof-of-work for that block.
+Once the block has been signed into the blockchain, it is impossible for the transactions inside the block to be reordered, assuming the miner network is controlled by a majority of honest nodes.
+
+As a further method of preserving order, each node includes its observed timestamp in its encrypted transaction and link data.
+This prevents a group of malicious miner nodes from altering the order and timestamp of the transaction before signing it into the blockchain.
 Therefore the transactions stored in these blocks satisfy the ``Order preserving'' property of OTIT.
-% in the dissertation i can discuss ordering within a block here (and go into detail about the merkle root etc)
 
-\item[] \textbf{Verifiable}: This states that the proof, and the order or proofs, should be verifiable by a trusted auditor.
-In our case, a Verifier node is an auditor trusted by the mobile node seeking verification.
-A Verifier node may be operated by a bank, government, or any entity wishing to make use of our location proof system.
+\subsection{Verifiable}
+This states that a Verifier should be able to verify or reject the claim by the user that he has visited the given location(s).
 
-Our system inherently satisfies this property of OTIT, as Verifier nodes are required to verify or reject a mobile node's claimed location.
-This is done by examining the mobile node's chronological link of transactions, and recursing for each alibi used for each transaction along the chronological link until the Verifier can conclude if the transaction chain is valid or not.
+The sytem described in chapter \ref{ch:design} inherently satisfies this property of OTIT.
+Verifier nodes may be operated by banks, employers, or other parties who have a vested interest in allowing their customers or employees to be able to prove their location.
+These Verifiers can verify or reject a mobile nodes claimed location by examining the nodes chronological link of transactions (as shown in figure \ref{fig:tree}).
+The Verifier will revursively generate and examine this tree until it can conclude whether the transaction chain is valid or not.
 
-\item[] \textbf{Tamper evident}: Our system is tamper evident.
+\subsection{Tamper evident}
+The system is tamper evident, meaning the Verifier is able to detect if the proof chain has been tampered with or modified.
 If a malicious node creates a successful transaction with an honest node, but modifies the transaction data before publishing, a Verifier node will reject the malicious transaction.
@@
 
-We assume the underlying security of the blockchain, so any malicious miner nodes will not be able to tamper with existing transaction data providing that the majority of CPU power in the mining system is owned by honest miners \cite{bitcoin}.
+The design assumes the underlying security of the blockchain, so any malicious miner nodes will not be able to tamper with existing transaction data providing that the majority of CPU power in the mining system is owned by honest miners \cite{bitcoin}.
 Therefore the tamper evident property is satisfied.
 
-\item[] \textbf{Privacy preserved}: This states that the user should have control over his level of privacy exposure when using the system.
-In our system, this is provided using \textit{Key Lists} \ref{sec:transactions}.
-We provide two keys for each transaction; $KL_{AT}[n]$ is used to encrypt the \textit{transaction data} for $A$'s $nth$ transaction, and $KL_{AL}[n]$ is used to encrypt the \textit{backwards chronological link} between $A$'s $nth$ transaction and transaction $n-1$.
+\subsection{Privacy preserved}
+This property states that when the proof chain is verified for specific location proofs, privacy must be preserved for the other location proofs within the chain.
+
+In the system, privacy is preserved using \textit{Key Lists} \ref{ssec:key_lists}.
+Two keys are used for each transaction; $KL_{AT}[n]$ is used to encrypt the \textit{transaction data} for $A$'s $nth$ transaction, and $KL_{AL}[n]$ is used to encrypt the \textit{backwards chronological link} between $A$'s $nth$ transaction and transaction $n-1$.
 
@@
 This may be useful if a user does not wish to reveal transaction data for transactions created within a certain distance of his house, for example.
-Hiding $KL_{AT}[n]$ while revealing $KL_{AL}[n]$ has the advantage of preserving the user's privacy while maintaining a clear backwards chronological link of transactions for the Verifier to follow, preserving both privacy and system consistency.
+Hiding $KL_{AT}[n]$ while revealing $KL_{AL}[n]$ has the advantage of preserving the user's privacy while maintaining a clear backwards chronological link of transactions for the Verifier to follow.
+This simulatneously preserves both privacy and chronological integrity.
 
-\item[] \textbf{Selective in-sequence privacy}: This is the requirement that any proof chain must support \textit{sub-set verification}, allowing a user to provide only a sub-set of proofs from his current proof chain for verification.
-Our system satisfies this property by using \textit{Key Packets} (section \ref{sssec:key_packets}).
+\subsection{Selective in-sequence privacy}
+This is the requirement that the user must be able to choose not to reveal certain location proofs within the proof chain when seeking verification.
+The system satisfies this property by using \textit{Key Packets} (section \ref{sssec:key_packets}).
 
-In our system, a \textit{sub-set} of $A$'s proof chain can be defined as $KP_{An}$.
-The sub-set therefore begins with $ID_{An}$, and ends when there is no key $KL_{AL}[n-m]$ in $KP_{An}$ to decrypt the link to transaction $T_{An-m-1}$.
+A \textit{sub-set} of size $m$ of a node $A$'s proof chain, beginning at proof $n$, contains all proofs in the sequence $ID_{A}[n-m] - ID_{A}[n]$.
+Every transaction in this chain is split into two parts (a transaction data and link data part), and separately encrypted.
+If a node reveals keys for a verifier decrypt all transactions in the sequence $ID_{A}[n-m] - ID_{A}[n]$, it will not be possible for the verifier to discover transaction $ID_{A}[n-m-1]$, or any transaction outside the sequence $ID_{A}[n-m] - ID_{A}[n]$.
 
-\item[] \textbf{Privacy protected chronology}: This states that the proof system, which provides \textit{selective in-sequence privacy}, should also ensure that the user does not ``hide away'' important items within the subset.
-This is impossible in our system due to the use of backwards chronological linking between transactions, so our model satisfies this property.
+By encrypting each transaction with a different pair of keys, this system satisfies OTIT's ``selective in-sequence privacy'' property.
 
-\item[] \textbf{Convenience and derivability}: This requirement states that the verification process should be convenient, and the user should not burden the Verifier node with a huge load of data.
-In our system, the data is stored in a central blockchain that the Verifier has access to, and the user provides the Verifier only with decryption keys and indexes into a sub-section of this data.
+\subsection{Privacy protected chronology}
+This property of OTIT states that the location proof system should ensure that the user does not hide important information from the items within the subset of the proof chain.
+In this system, it is impossible by design to hide important information, due to the use of backwards chronological linking between transactions.
+
+\subsection{Convenience and derivability}
+This requirement states that the system must ensure that the user does not burden the Verifier with a large amount of data to analyse in order to verify the user's location.
+
+In this system, the data is stored in a central blockchain that the Verifier has access to, and the user provides the Verifier  with decryption keys and indexes into just a sub-section of this data.
 Therefore the data sent to from the user to the Verifier, $KP_{An}$, is quite small in size.
 
-The Verifier has the freedom to decide how comprehensively to investigate the user's data; It can bound how deeply to investigate the graph of alibi's, if at all.
-We therefore satisfy this requirement by allowing the Verifier to choose how complex the verification process needs to be.
-\end{enumerate}
+The Verifier has the freedom to decide how comprehensively to investigate the users data; It can decide how far to recurse while investigating the tree of alibi relationships.
+This property of OTIT is therefore satisfied by allowing the Verifier to decide how complex the verification process needs to be.
 
-\section{Attacks on the system}
-\subsection{Identity replication}
-By repeatedly publishing fake transactions with the same ID, a malicious user can impede the Verification of certain transactions.
-This is because a Verifier will have to attempt to decrypt all transactions with the same ID until it finds one that decrypts successfully.
-A malicious user can therefore slow down the verification stage of certain transactions by flooding the blockchain with transactions with the same ID.
+\section{Threat analysis}
+\subsection{False presence}
+In a false presence attack, a dishonest user attempts to obtain a location proof for a false location.
 
-This is an abuse of the system than an attack.
-A malicious user will not be able to target specific users' transactions, because they are privacy protected.
-The malicious user can therefore gain no material advantage or compromise the security of the system by using an attack like this.
+In this system, any dishonest user attempting to obtain a location proof with an honest alibi will not succeed, as the honest alibi will abort the exchange (see section \ref{ssec:aborting_exchanges}).
+A dishonest user who publishes a transaction onto the blockchain with a fabricated alibi will also not succeed, as the transaction will be rejected during verification if a Verifier can't find the matching alibi transaction.
+The system is therefore not vulnerable to a false presence attack.
 
-To avoid this attack, Miner nodes may reject any transactions with duplicate transaction IDs.
-Assuming sufficiently large transaction IDs, a duplicate ID is unlikely to happen through honest operation.
-Miners can assume that any transactions with duplicate IDs are malicious, and reject them.
+\subsection{Malicious intruders}
+A malicious intruder offers to help another user to prove a false location, but doesn't prove a false location for himself.
+
+In the context of this system, a malicious intruder may collude with another user to prove a false location, by acting as an alibi.
+These transactions will be successfully published onto the blockchain.
+However, if this user attempts to have his transaction chain verified, a Verifier will quickly notice the lack of credible alibis in the proof chain, indicating malicious activity, and reject the proof request.
+A sample tree of a node with uncredible alibis is shown in figure \ref{fig:uncredible_tree}.
+This avoids a malicious intruder vulnerability.
+
+\begin{figure}[H]
+\begin{center}
+\resizebox {0.5\columnwidth} {!} {\input{diagrams/uncredible_tree.tex}}
+\vspace{-3cm}
+\caption{A proof chain with uncredible alibis}
+\label{fig:uncredible_tree}
+\end{center}
+\end{figure}
+
+\subsection{Curious users}
+A curious user is one who learns another users identity by monitoring its location proofs.
+
+Identity discovery is impossible by design in this sytem.
+By using a different, seemingly random identity for each transaction, it is impossible for a curious user to determine if two transactions belong to the same user or not.
+It is therefore impossible for a curious user to learn another users identity by monitoring location proofs.
+
+\subsection{Malicious applications}
+A malicious application is one that tries to take advantage of a users information as the user seeks verification.
+
+This attack does not affect this system, as a user will only seek verification from applications (verifiers) it deems trustworthy.
+Verifiers, such as banks or employers, will be known to the user, and therefore trusted.
+The user also has complete control over which verifiers it chooses to seek verification from, it is not obliged to send verification requests to any verifier.
+
+\subsection{Eavesdroppers}
+An eavesdropper intercepts or modifies communication between two honest users.
+This threat does not affect this system, as ad-hoc bluetooth networks are set up between two mobile nodes advertising their current transaction ID, e.g.
+$ID_A[n]$.
+An eavesdropper will not be a member of this ad-hoc network, and therefore cannot modify any communication in the network.
+
+\subsection{Wormhole attacks}
+In a wormhole attack, an attacker records network traffic in one location and replays it in another location, at another time.
+
+This attack is not relevant to the system presented in chapter \ref{ch:design}, as this system is decentralised. Any wormhole attack transmissions will simply be ignored by the intended victim.
+
+\subsection{Weak identities}.
+In a weak identity attack, a user gives his public key or identity to another colluding user in order to create a location proof.
+
+A weak identity attack will not affect this system.
+Exchanging public keys or identities between colluding users offers no advantage.
+This is because the Verifier will ensure that any users requesting verification own the private key corresponding to the public key transferred during the verification request (see section \ref{ssec:verification}).
+
+\subsection{False timestamping}
+False timestamping includes backdating and future dating attacks.
+In a backdating attack, the attacker creates a location proof with a past timestamp.
+In future dating, the attacker creates a location proof with a future timestamp.
+
+This system is resilient against a false timestamping attack by design.
+Every transaction is created with a reference to an alibi transaction.
+If an attacker creates a transaction with a past or future timestamp, the corresponding alibi transaction will contain contradictory information, and a Verifier will disregard it.
+
+\subsection{Implication}
+An implication attack occurs when a malicious user, or group of colluding malicious users, create a false location proof for an honest user.
+
+This system is resilient to an implication attack.
+Location proofs are stored in a public blockchain, but the decryption keys, nonce and public key used to create the transaction all reside with the user who created it.
+A user cannot be implicated in a location proof without creating the identity used in the proof, and encrypting the transaction data.
+
+It is therefore impossible to implicate an honest user in a location proof, without finding vulnerabilities outside the location proof system (for example by compromising their device).
+
+\subsection{False assertion}
+In a false assertion attack, two malicious users collude to create false location proofs for themselves.
+
+It is possible in this system for two malicious users to collude as alibis and publish their transactions on the blockchain.
+This is allowed because the miner nodes do not know the contents of the data they are signing into the blockchain, as it is encrypted.
+
+Providing that the system is comprised of a majority of honest nodes, this attack will not succeed.
+It will be obvious to a Verifier after construcing a graph of the nodes alibi transaction (as shown in section \ref{ssec:verification}) that the graph lacks alibi credibility, and therefore two malicious users are likely colluding to create location proofs for themselves.
+Therefore the system is not vulnerable to this attack.
+
+\subsection{Proof switching}
+In a proof switching attack, a malicious user modifies one of its existing honest proofs to spoof a false location.
+
+This is not possible in this system, as the blockchain is used as a tamper-proof method of storing location proofs. Once the proof is included in the blockchain, it cannot be modified.
+
+If the proof has not been added to the blockchain yet, then it is possible for the malicous user to modify it to attempt to spoof a false location.
+However this attack will not work on this system.
+Any Verifier will reject the transaction on the grounds that it contains contradictory information to the alibis transaction, which has not been modified.
+
+\subsection{Relay attack}
+In a relay attack, a malicious user uses a colluding \textit{proxy user} physically present at the location that the malicious user wishes to create a false proof, to create a location proof with an honest user.
+
+This system is resilient against a most relay attacks.
+This is because proofs created using a proxy user will be inconsistent with the other proofs in a users proof chain.
+For example, a user living in New York uses a proxy user to create a proof with a user in London.
+A Verifier will reject the users claim that it is in London, because of the lack of alibi credibility.
+
+One vulnerability of the system can be called a \textit{complete} relay attack.
+In a \textit{complete} relay attack, two malicious nodes exist purely for the purpose of proxying location proof.
+One node, the proxy, will \textit{never} request location proofs for itself.
+Its only purpose is to proxy exchange data between honest nodes and the other malicious node, the \textit{attacker}.
+
+Resilience against a complete relay attack scenario must be taken out of the scope of this system.
 
 \subsection{Sybil attack}
-This system is vulnerable to a Sybil attack, where a single physical node may create multiple \textit{pseudoidentities} \cite{sybil}.
-A suitably powerful node, or motivated attacker, could create enough pseudonyms to create a subnetwork of nodes, each creating malicious transactions with each other.
-This would allow an attacker to falsify a believable location proof.
+A Sybil attack occurs when a single malicious user generates multiple \textit{pseudoidentities}, and begins masquerading as multiple users.
 
-It has been proven that a central certificate authority is the only method of preventing a Sybil attack \cite{sybil}.
-Other measures, such as web of trust, increase the difficulty involved in performing an attack, but the system remains vulnerable to a motivated attacker.
+While some studies have been done on Sybil attacks in decentralised systems \cite{sybil}.
+There are various methods of mitigating against a subil attack, however a solution for the Sybil attack in a decentralised system is considered an open problem.
+This system is therefore vulnerable to a highly targeted Sybil attack.

### 2016-04-18 thesis/background.tex
updating after (another) proofread

@@
-\section{Proving your location}
-As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, we are losing the security that previously existed by requiring physical interaction between humans to transfer sensitive data.
+\section{Proving location}
+As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, the security that previously existed by requiring physical interaction between humans to transfer sensitive data is lost.
 
 Location proof is a large part of that security.
-There is currently no ubiquitous method of \textit{proving} your location at a given time digitally.
-Many companies, such as Netflix, use GeoIP databases such as MaxMind \cite{maxmind} to estimate a users location based on his IP address.
-This technique is inaccurate and easily bypassable using proxy servers or VPNs.
+There is currently no ubiquitous method of \textit{proving} a mobile user's location at a given time over the internet.
+Many companies, such as Netflix, use GeoIP databases such as MaxMind \cite{maxmind} to estimate a user's location based on its IP address.
+This is a location observation technique rather than a proof.
+It is therefore inaccurate and easily bypassable using proxy servers or VPNs.
 
-One newer, more advanced tecnique of location observation is Constraint-Based Geolocation \cite{constraint-based}.
+One newer, more advanced technique of location observation is Constraint-Based Geolocation \cite{constraint-based}.
 This is an active geolocation technique, compared with GeoIP verification which is static.
@@
 \textit{Location proof systems} allow users of the system to \textit{prove} their location to another user, by creating \textit{location proofs}.
-Location proofs vary from system to system.
+The structure of a location proof varies from system to system.
 In essence, a location proof is a piece of data, potentially signed or encrypted by another party, which attests the location of a user at a specific time.
@@
 A \textit{distributed} system is a system which distributes the computation of a task across multiple nodes (computers) connected over a network.
-These nodes then work together and communicate to complete the task by passing messages over the network \cite{distributed}.
+These nodes are assigned a task from a central node, and then work together and communicate to complete the task by passing messages to each other over the network \cite{distributed}.
 
@@
 Google therefore \textit{distributes} the task of calculating search indexes across multiple nodes.
-This two main advantages; It is less time consuming, because different index calculations can be computed on different nodes at the same time, and it's scalable, because nodes can be added or removed from the network dynamically, to meet demand.
+This has two main advantages; It is less time consuming, because different index calculations can be computed on different nodes at the same time, and it is scalable, because nodes can be added or removed from the network dynamically, to meet demand.
 
 A \textit{decentralised} system is similar to a distributed system, except no node is in charge.
-Nodes in a decentralised network still communicate by passing messages to each other over the network, but unlike a distributed system, they arent assigned tasks by a central or master node.
+Nodes in a decentralised network still communicate by passing messages to each other over the network, but unlike a distributed system, they are not assigned tasks by a central or master node.
 Bitcoin \cite{bitcoin} is a good example of a large-scale decentralised system.
@@
 They make the details of that transaction public.
-The two nodes therefore create and publish the transaction iwithout coordination from a central node.
+The two nodes therefore create and publish the transaction without coordination from a central node.
 
-In the context of a location proof system, I consider a distributed location proof system to be one where the task of facilitating user proof request and creation is distributed across multiple \textit{worker nodes}, which are controlled and coordinated by a central node.
+In the context of this project, a distributed location proof system is considered to be a proof system where the task of facilitating user proof request and creation is distributed across multiple \textit{worker nodes}, which are controlled and coordinated by a central node.
 This allows a higher volume of proofs to be created concurrently compared with using a single node, while maintaining centralised and simple control over the system.
@@
 
-I consider a decentralised location proof system to be one where no node is in charge of controlling or coordinating the system.
-Nodes can create and publish location proofs between themselves, without the need for a central third party to coordinate the interaction (figure \ref{fig:decentralised_location}).
+A decentralised location proof system is considered to be one where no node is in charge of controlling or coordinating the system.
+Nodes can create and publish location proofs between themselves, without the need for a central third party to coordinate their interaction (figure \ref{fig:decentralised_location}).
 This makes coordination more complex, but means that no node is considered to be ``in charge'' of the system.
@@
 A hardware technique \cite{brassil}, developed by Brassil et al.
-of HP Laboratories, operates by supplementing existing WiFi access points (\textit{AP's}) with \textit{femtocells}.
-A femtocell \cite{femtocell} is a small cellular antenna that connects to a mobile carrier via the Internet, which allows mobile networks (e.g.
+of HP Laboratories, operates by supplementing existing Wi-Fi access points (\textit{AP's}) with \textit{femtocells}.
+A femtocell \cite{femtocell} is a small cellular antenna that connects to a mobile network operator (such as Vodafone) via the Internet, which allows mobile networks (e.g.
 networks used for calls and texts) to be extended on demand.
-Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data via Wi-Fi.
+Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data over Wi-Fi.
 This is possible because the central server in the location verification system has access to the mobile operator's user data.
 
-This solution requires investment in additional hardware to supplement existing WiFi access points, and requires access to mobile providers' user database to identify users locations (see figure \ref{fig:hp_labs}).
+This solution requires investment in additional hardware to supplement existing Wi-Fi access points, and requires access to mobile providers' user databases to identify users' locations (see figure \ref{fig:hp_labs}).
+Note that the two lines between the user and the AP in figure \ref{fig:hp_labs} indicates that the user is connected to the AP \textit{and} its attached femtocell.
 
@@
 \begin{center}
-\resizebox {0.5\columnwidth} {!} {\includegraphics{diagrams/hp_paper.png}}
+\resizebox {0.45\columnwidth} {!} {\includegraphics{diagrams/hp_paper.png}}
 \caption{Hardware-based proof system (Adapted from Brassil et al. \cite{brassil})}
@@
 
-The use of a centralised system, as described above, creates security, privacy and vulnerability issues.
-An attacker who succeeds in compromising the security of the central server can violate the privacy of the users of the system, and potentially track their location.
+The use of a centralised system, as described in figure \ref{fig:hp_labs}, creates security, privacy and vulnerability issues.
+An attacker who succeeds in compromising the security of the central server can create unlimited false location proofs for itself, or violate the privacy of the users of the system, and potentially track their location.
 This is because in this system, location proof data resides with the central server.
-This means that the user has no control over the security of their proofs, and an attacker could sieze them.
+This means that the user has no control over the security of their proofs, and an attacker could seize them.
 The central system architecture is also vulnerable, in the sense that a resource availability attack such as a DDoS attack \cite{ddos} could render the central architecture unavailable, making location verification unavailable.
@@
 \resizebox {0.5\columnwidth} {!} {\includegraphics{diagrams/ap_paper.png}}
-\caption{Access point proof system (Adapted from Luo et al. \cite{luo})}
+\caption{Distributed proof system on access points (Adapted from Luo et al. \cite{luo})}
 \label{fig:luo_diagram}
@@
 \begin{center}
-\resizebox {0.7\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
+\resizebox {0.65\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
 \caption{Proof request with group signature (Adapted from Luo et al. \cite{luo})}
@@
 
+The operation of the system shown in figure \ref{fig:luo_transaction} is described below.
+\begin{enumerate}
+\item[] \textbf{(1)} The access point generates a nonce $n_{AP}$ and sends it to the user.
+\item[] \textbf{(2)} The user generates its own nonce $n_{user}$, and responds with a one-way hash of its nonce and the AP's nonce, encrypted with its own secret key.
+\item[] \textbf{(3)} The AP generates a location proof, encrypted with $S_{group}$, the system group signature. This proof now resides with the user, and can be used to prove its location.
+\end{enumerate}
+
 This system creates \textit{proactive} location proofs.
 A proactive location proof is one which is created before it is needed.
-The user creates application-independent location proofs, and can use them at a later time with any application(s) he chooses.
+The user creates application-independent location proofs, and can use them at a later time with any application(s) it chooses.
 \\
@@
 \begin{center}
-\resizebox {0.4\columnwidth} {!} {\includegraphics{diagrams/witness_paper.png}}
+\resizebox {0.275\columnwidth} {!} {\includegraphics{diagrams/witness_paper.png}}
 \caption{Proof system using witnesses (Adapted from Khan et al. \cite{khan})}
@@
 Because proof-of-work solutions also incorporate some information about the previous block in the chain, changing data inside a block in the blockchain would not just require regeneration of the proof-of-work for that block, but for all successive blocks as well.
-Therefore the blockchain is tamper-proof, assuming that the majority of the CPU power in the miner network is controlled by  honest nodes \cite{bitcoin}.
+A malicious node attempting to change the transaction history would have to solve proofs-of-work at a greater rate than the rest of the network combined in order to succeed.
+Therefore the blockchain is tamper-proof, assuming that the majority of the CPU power in the miner network is controlled by  honest miner nodes \cite{bitcoin}.
 
@@
 That miner node propagates the transaction to other miner nodes in the network, and they each try to include it in the next block by solving the proof-of-work.
-A simple overview of the system is shown in figure \ref{fig:blockchain}.
+A simple overview of the components in the system is shown in figure \ref{fig:blockchain}.
 
-Once a proof-of-work has been solved, the solution is distributed to all other miners in the network to prove that the solver expended significant computational effort to solve it.
-This is a proof of resource ownership, meaning that by solving the proof-of-work, the miner has shown that it has significant computational resources and is therefore considered a valid miner.
-Once other miners in the network verify that the proof-of-work is correct, the block (and therefore all transactions contained in it) is considered the newest block in the tamper-proof chain, and miners begin working on the next block.
+Once a proof-of-work has been solved, the solution is distributed to all other miner nodes in the network to prove that the solver expended significant computational effort to solve it.
+This is a proof of resource ownership, meaning that by solving the proof-of-work, the miner node has shown that it has significant computational resources and is therefore considered a valid miner node.
+Once other miner nodes in the network verify that the proof-of-work is correct, the block (and therefore all transactions contained in it) is considered the newest block in the tamper-proof chain, and miner nodes begin working on the next block.
 
@@
 \section{Design goals} \label{sec:design_goals}
-Before designing the system, a number of goals must be defined and an attempt made to satisfy them in the design. My design goals are listed below.
+Before designing the system, a number of goals must be defined and an attempt made to satisfy them in the design. The design goals of this project are listed below.
 
-\begin{itemize}
+\begin{enumerate}
 	\item The system must be \textit{privacy preserving}.
-It must not be possible for a malicious user to obtain any additional information from an honest user than the information the honest user intended to release.
+It must not be possible for a malicious user to obtain any additional information from an honest user other than the information the honest user intended to release.
 	\item False location proofs must be detectable. It must be possible to detect any location proofs attempting to prove false information.
@@
 	\item The system must not be vulnerable to any known threats (section \ref{ssec:threats}).
-\end{itemize}
+\end{enumerate}
 
 \subsection{Central services} \label{ssec:centralised}
-Location proof systems which rely on central noes, such as those discussed in section \ref{ssec:proof_systems}, have a fundamental weakness.
+Location proof systems which rely on central nodes, such as those discussed in section \ref{ssec:proof_systems}, have a fundamental weakness.
 These systems assume that the central node is honest, always available, and cannot be compromised by an attacker.
 Since the central node is in charge of coordinating the system, compromising it allows an attacker potentially unlimited control over the system.
-This completely violates a users privacy in a location verification system, as the central node may contain sensitive information about users and their location, or a means of retrieving sensitive information, such as decryption keys.
+This completely violates a user's privacy, as the central node may contain sensitive information about users and their location, or a means of retrieving sensitive information, such as decryption keys.
 Users of the system also have to assume that the central node is available at all times, otherwise the system is considered unavailable, or ``down''.
@@
 These problems do not occur in a decentralised location proof system, because no node is considered to be ``in charge''.
+If no node is in charge, any node(s) can join or leave the network without altering the state of the network, or making any services unavailable.
 This lack of authority prevents privacy breaches, but presents other issues.
-System coordination, which is easily maintained by the central node in a centralised system, is now maintained by each participant in the decentralised system.
+System coordination, which is easily maintained by the central node in a centralised system, is now maintained by each participant in the decentralised system, who may or may not all be honest.
 
@@
 	\item[] \textbf{Chronological}: Location proofs should be ordered according to the sequence of their creation.
-	\item[] \textbf{Order preserving}: The order in which the proofs were entered into the proof chain should always be maintained.
-	\item[] \textbf{Verifiable}: A Verifier should be able to verify or reject the claim by the user that he has visited the given location(s).
+	\item[] \textbf{Order preserving}: The order in which the proofs are entered into the proof chain should always be maintained.
+	\item[] \textbf{Verifiable}: A Verifier should be able to verify or reject the claim by the user that it has visited the given location(s).
 	\item[] \textbf{Tamper evident}: A Verifier should be able to detect if the proof chain has been tampered with or modified by an unauthorised party.
@@
 	\item[] \textbf{Privacy protected chronology}: The system should ensure that the user does not hide important information from the items within the subset of the proof chain.
-	\item[] \textbf{Convenience and derivability}: The system shold ensure that the user does not burden the Verifier with a large amount of data to analyse in order to verify his location.
+	\item[] \textbf{Convenience and derivability}: The system should ensure that the user does not burden the Verifier with a large amount of data to analyse in order to verify its location.
 \end{itemize}
@@
 	\item[] \textbf{False presence}: A dishonest user attempts to obtain a location proof for a false location.
-	\item[] \textbf{Malicious intruders}: A malicious intruder offers to help another user prove a false location, but doesn't prove a false location for himself.
+	\item[] \textbf{Malicious intruders}: A malicious intruder offers to help another user prove a false location, but does not prove a false location for itself.
 	\item[] \textbf{Curious users}: A curious user learns another user's identity by monitoring its location proofs.
-	\item[] \textbf{Malicious applications}: The application that the user is proving his location to takes advantage of the user's information.
+	\item[] \textbf{Malicious applications}: The application that the user is proving its location to takes advantage of the user's information.
 	\item[] \textbf{Eavesdroppers}: An eavesdropper intercepts or modifies communication between two honest users.
 	\item[] \textbf{Wormhole attacks}: An attacker records network traffic in one location and replays it in another location (at another time).
-	\item[] \textbf{Weak identities}: A user gives his public key or identity to another colluding user in order to create a location proof.
+	\item[] \textbf{Weak identities}: A user gives its public key or identity to another colluding user in order to create a location proof.
 	\item[] \textbf{False timestamping (backdating, future dating)}: In a backdating attack, the attacker creates a location proof with a past timestamp.
-In future dating, the attacker creates a location proof with a future timestamp
-	\item[] \textbf{Implication}: A malicious user, or group of colluding malicious users, create a false location proof for an honest user.
+In future dating, the attacker creates a location proof with a future timestamp.
+	\item[] \textbf{Implication}: A malicious user, or group of colluding malicious users, creates a false location proof for an honest user.
 	\item[] \textbf{False assertion}: Two malicious users collude to create a false location proof for themselves.
 	\item[] \textbf{Proof switching}: A malicious user modifies one of its existing honest proofs to spoof a false location.
-	\item[] \textbf{Relay attack}: A malicious user creates a location proof with an honest user by relaying his requests through a colluding \textit{proxy user}, who is physically present at a location that the malicious user wishes to create false proofs at.
+	\item[] \textbf{Relay attack}: A malicious user creates a location proof with an honest user by relaying its requests through a colluding \textit{proxy user}, who is physically present at a location that the malicious user wishes to create false proofs at.
 	\item[] \textbf{Sybil attack}: A Sybil attack occurs when a single malicious user of the system generates multiple \textit{pseudoidentities} and masquerades as multiple users \cite{sybil}.

### 2016-04-18 thesis/conclusion.tex
updating after (another) proofread

\section{Future work}
There are many worthwhile areas for future work, because to the best of the author's knowledge, this is the first attempted design of a fully decentralised location proof system.

\subsection{Verification techniques}
Section \ref{ssec:verification} outlined a number of simple verification techniques that a Verifier node could use to analyse the a proof chain. There is potential for further research on advanced techniques of analysing proof chain trees to determine the validity of a user's proof request.

\subsection{Privacy and verifiability}
As explained in section \ref{sssec:key_packets}, certain transactions can be hidden from a proof chain in order to protect a user's privacy, but maintain chronological integrity. There is an interesting area of further work in studying the effect that hiding certain proofs has on that user's verifiability.

\subsection{Sybil attack}
Previous work has indicated that there is no provably correct way of preventing a Sybil attack in a decentralised system \cite{sybil}. However, further work studying strong mitigations against a Sybil attack, or even preventing a Sybil attack entirely, would greatly improve the appeal of a decentralised location proof system, and potentially lead to its ubiquitous use.

\section{Conclusion}
This project presented the design of a decentralised location proof system. The aim of the project was to design a system that satisfied the design goals, as defined in section \ref{sec:design_goals}. This system satisfies all of the requirements of OTIT \cite{otit}, and all but one of the threats defined in section \ref{ssec:threats}. However, chapter \ref{ch:evaluation} concluded that this Sybil attack threat must be highly targeted to be effective.

In conclusion, the model presented in this project is a viable design of a decentralised location proof system, providing that the Sybil attack vulnerability can be heavily mitigated against or prevented outright.

### 2016-04-18 thesis/design.tex
updating after (another) proofread

@@
-The location proof system I propose allows \textit{mobile nodes} to create location proofs by initiating an \textit{exchange} with another anonymous mobile node.
-When two mobile nodes are in close physical proximity, they initiate an exchange in the background over a short range, ad-hoc network such as Bluetooth.
-On completion of the exchange, both nodes can generate their own \textit{transaction}, a cryptographically secure proof of location, attested by the other mobile node.
+The location proof system proposed in this project allows \textit{mobile nodes} to create location proofs by initiating an \textit{exchange} with another anonymous mobile node.
+Mobile nodes, physically moving around, advertise their identity over a short range, ad-hoc network such as bluetooth.
+When two mobile nodes are in close physical proximity, they initiate an exchange in the background over the ad-hoc network.
+On completion of the exchange, both nodes can generate their own \textit{transaction}, a cryptographically secure proof of location, attested by the other mobile node (the \textit{alibi}), and make it public.
 
-To create a transaction, two mobile nodes anonymously exchange their GPS coordinates and current time over the ad-hoc network.
-Both nodes then check that these parameters don't differ from their own observed parameters by more than some value $\epsilon$.
-Once satisfied, they each create an encrypted, privacy-protecting transaction logging their location and the identity of the other mobile node (the \textit{alibi}) used to create the transaction.
+To create a transaction, two mobile nodes anonymously exchange their GPS coordinates and current timestamp over the ad-hoc network.
+Both nodes then check that these parameters do not differ from their own observed parameters by more than some value $\epsilon$.
+Once satisfied, they each create an encrypted, privacy-protecting transaction logging their location and the identity of the the alibi used to create the transaction.
 This transaction is published onto a public, append-only bulletin board known as a \textit{blockchain} \cite{blueprint}.
@@
 Any mobile node acting as an alibi in a transaction will share details of its most recent transactions with the other mobile node in the exchange.
-This means that when the mobile node seeks verification from a Verifier node, the Verifier can examine the mobile node's alibi's, and each of the alibi's recent alibi's, forming a large tree of connections which can be used to verify or reject the mobile nodes claimed location.
+This means that when a mobile node seeks verification from a Verifier node, the Verifier can examine the mobile node's alibis, and each of the alibis' recent alibis, forming a large tree of connections which can be used to verify or reject the mobile nodes claimed location (see figure \ref{fig:tree}).
 Only the owner of the transaction can give permission to a Verifier to check its location history, by providing the Verifier with the keys needed to decrypt the transactions.
@@
 
+\vspace{-1cm}
 \begin{enumerate}[label=\textbf{\arabic*}.]
@@
 \item Both mobile nodes publish their own transaction to a Miner node.
-\item The Miner node who received the transaction distributes it across the Miner network.
+\item The Miner node who received the transaction distributes it to the other miner nodes in the network.
 \item One Miner node solves the proof-of-work for a block of transactions, and the new block is appended to the blockchain.
 \item A mobile node requests verification from a Verifier node (request structure is explained in section \ref{ssec:verification}).
-\item The Verifier node uses the public blockchain to examine the requesting node's transactions and determine their validity.
+\item The Verifier node refers to the public blockchain to examine the requesting node's transactions and determine their validity.
 \item The Verifier accepts or rejects the  mobile node's claimed location based on its analysis of the transactions in the blockchain. 
@@
 \section{Identities}
-In order to preserve user's privacy, a user will only ever use an identity for one transaction, before generating a new one.
+In order to preserve users' privacy, a user will only ever use an identity for one transaction, before generating a new one.
 This prevents curious users from watching the public blockchain for a known identity and tracking it.
-However, to prevent identity theft, it is important for the Verifier to be able to prove that a mobile node is the owner of each identity.
+However, to prevent identity theft, it is important for a Verifier to be able to prove that a mobile node is the owner of each identity.
 This is achieved using a public/private key pair for each mobile node.
 
-When a mobile node is first joins the network, it generates a public/private key pair.
+When a mobile node first joins the network, it generates a public/private key pair.
 To maintain anonymity, the mobile node will use the public key to encrypt \textit{nonces} to create \textit{identities}, and use these to identify itself in a transaction.
 A different identity will be created for each transaction.
-During the verification stage, the node will provide the Verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions (see figure \ref{fig:verify_request}).
-This allows the Verifier to calculate all of the node's identities, and prove that they were all created by the same node.
-The Verifier can then retrieve the transactions associated with those identities from the blockchain.
-The Verifier will also ensure that the node owns the private key associated with the provided public key, to prevent a weak identity attack.
+During the verification stage, a node will provide a Verifier with its public key, along with the list of the nonces used to generate its $n$ most recent transactions (see figure \ref{fig:verify_request}).
+This allows a Verifier to calculate all of the node's identities, and prove that they were all created by the same node.
+A Verifier can then retrieve the transactions associated with those identities from the blockchain.
+Verifiers will also ensure that a node owns the private key associated with its provided public key, to prevent a weak identity attack.
 
@@
 A \textit{Nonce List} is simply a list of all of the nonces a mobile node has used so far to generate identities.
-When a mobile node wishes to generate a new identity, it must first generate a new nonce which is then encrypted to create the identity.
+When a mobile node wishes to generate a new identity, it must first generate a new random nonce which is then encrypted to create the identity.
 The nonce is appended to the mobile node's nonce list, so it can be used later during verification (see section \ref{ssec:verification}).
@@
 
-In figure \ref{fig:nonce_list} above, nonce $0047$ is encrypted with $K^+$ to create identity $ee3bc14$.
+In figure \ref{fig:nonce_list} above, nonce $0047$ is encrypted with $K^+$, a node's public key, to create identity $ee3bc14$.
 By providing the nonce list and $K^+$, a node can prove that it created all of the identities in the identities list.
@@
 It is therefore possible that during verification, a Verifier node may find multiple transactions with the same ID while searching the blockchain.
-The Verifier will have a decryption key for the transaction it is searching for, which will only successfully decrypt one of the transactions with the duplicate ID.
-The Verifier will try to decrypt each one until it finds the one that can be decrypted successfully.
+Verifiers are provided with decryption key from the requesting node for the transactions they are searching for, which will only successfully decrypt one of the transactions with the duplicate ID.
+A Verifier will try to decrypt each one until it finds the one that can be decrypted successfully.
 
@@
 During an exchange between two nodes, a number of different items must be shared and calculated.
-Figure \ref{fig:transaction} describes and explains an honest, successful exchange, assuming an ad-hoc Bluetooth network has already been set up between nodes $A$ and $B$.
+Figure \ref{fig:transaction} describes and explains an honest, successful exchange, assuming an ad-hoc network has already been set up between nodes $A$ and $B$.
 
@@
 	\item[] \textbf{(1)} Before the exchange begins, both nodes generate a new entry in their nonce list (e.g. $NL_A[n]$), and generate a new identity from that nonce (e.g. $ID_A[n]$).
-	\item[] \textbf{(2)} Node A sends its identity to Node B, along with its observed current timestamp $ts_A$ and current GPS location $loc_A$.
-	\item[] \textbf{(3)} Node B verifies that the observed timestamp and GPS location received from Node A are within an acceptable difference from its own observations.
+	\item[] \textbf{(2)} Node $A$ sends its identity to node $B$, along with its observed current timestamp $ts_A$ and current GPS location $loc_A$.
+	\item[] \textbf{(3)} Node $B$ verifies that the observed timestamp and GPS location received from node $A$ are within an acceptable difference from its own observations.
 This difference is defined by some system constant $\epsilon$.
-	\item[] \textbf{(4)} If Node B verifies the parameters received from Node A, it will respond with its own identity and observations for A to verify.
-	\item[] \textbf{(5)} Node A verifies that the parameters received from B differ by no more than $\epsilon$ from its own observed parameters.
-	\item[] \textbf{(6)} Node A sends $KP_{An}$, its $nth$ \textit{Key Packet}. Key Packets are used to provide alibi credibility, and are discussed in section \ref{sssec:key_packets}.
-	\item[] \textbf{(7)} B responds with its own Key Packet.
+	\item[] \textbf{(4)} If node $B$ verifies the parameters received from node $A$, it will respond with its own identity and observations for node $A$ to verify.
+	\item[] \textbf{(5)} Node $A$ verifies that the parameters received from node $B$ differ by no more than $\epsilon$ from its own observed parameters.
+	\item[] \textbf{(6)} Node $A$ sends $KP_{An}$, its $nth$ \textit{Key Packet}. Key Packets are used to provide alibi credibility, and are discussed in section \ref{sssec:key_packets}.
+	\item[] \textbf{(7)} Node $B$ responds with its own Key Packet.
 	\item[] \textbf{(8)} Both nodes generate their own transaction $T$, using their alibi's Key Packets. These are then used to generate $P$, the data published onto the public blockchain.
@@
 For example, $KL_{AT}[n]$ and $KL_{AL}[n]$ are the two keys used to encrypt node $A$'s $n$th transaction and matching chronological link, respectively.
-These \textit{Key Lists} and are assumed to have been initialised and populated before the transaction described in Figure \ref{fig:transaction} begins.
+These \textit{Key Lists} are assumed to have been initialised and populated before the transaction described in Figure \ref{fig:transaction} begins.
 
@@
 \begin{itemize}[noitemsep,topsep=0pt]
-	\item[] $\mathbf{n}$ is node $A$'s current transaction number (i.e. $A$ has published $n-1$ transactions before now).
-	\item[] $\mathbf{KL_{AT}}$ is $A$'s transaction \textit{Key Lists}, used to encrypt transactions.	
+	\item[] $\mathbf{n}$ is node $A$'s current transaction number (i.e. node $A$ has published $n-1$ transactions before now).
+	\item[] $\mathbf{KL_{AT}}$ is node $A$'s transaction \textit{Key List}, used to encrypt transactions. $KL_{AT}[n]$ is the $nth$ entry in the Key List.
 	\item[] $\mathbf{ts}$ is the timestamp of the transaction, as recorded by node $A$.
@@
 The data published must be searchable in order to provide a Verifier with some way of identifying specific transactions.
-Nodes use their current ID as the identifier for the transaction.
+Nodes use their current ID as the identifier for a transaction.
 
 \textit{Backwards-chaining} is an important part of verifiability.
-The Verifier must be able to prove that the proof chain provided by the mobile node has not been chronologically re-ordered.
-This is the ``order preserving'' property of OTIT \cite{otit}.
-The transaction must therefore be accompanied by a link to the node's chronologically previous transaction.
-This link is encrypted with $KL_{AL}[n]$, $A$'s $nth$ \textit{link} key list, to prevent a curious user from monitoring the public blockchain to observe a user's transaction publishing activity.
-The timestamp $ts_A$ is also included in the backwards-chaining data, to verify the ``order preserving'' property.
-$A$'s transaction data $P_{An}$ will therefore be in the form:
+A Verifier must be able to prove that the proof chain provided by a mobile node has not been chronologically re-ordered.
+This was designed to satisfy the ``order preserving'' property of OTIT \cite{otit}.
+Each transaction must therefore be accompanied by a link to the node's chronologically previous transaction.
+This link is encrypted with $KL_{AL}[n]$, node $A$'s $nth$ \textit{link} key list, to prevent a curious user from monitoring the public blockchain to observe a user's transaction publishing activity.
+The timestamp $ts_A$ is also included in the backwards-chaining data, required to verify the ``order preserving'' property of OTIT.
+Node $A$'s transaction data $P_{An}$ will therefore be in the form:
 \\
@@
 \null
-To publish $P_{An}$, $A$ must send $P_{An}$ to a miner node, who will add it to its \textit{pending transaction} queue, and send it to other miners in the network to add it to their queues as well.
-The transaction will signed into the next block in the blockchain, once the next proof-of-work is solved.
+To publish $P_{An}$, node $A$ must send $P_{An}$ to a miner node, who will add it to its \textit{pending transaction} queue, then send it to other miners in the network to add it to their queues.
+The transaction will be signed into the next block in the blockchain, once the next proof-of-work is solved.
 
 Node $B$, $A$'s alibi for the above transaction example, will publish $P_{Bm}$ after the exchange.
-If $B$'s transaction is not available on the blockchain, $A$'s transaction will be considered invalid and disregarded during verification.
-A transaction $T_A$ in the blockchain must be accompanied by a reference to some valid alibi transaction $T_B$, and $T_B$ must reference $T_A$, otherwise the proof is not considered credible by a verifier.
+If node $B$'s transaction is not available on the blockchain, node $A$'s transaction will be considered invalid and disregarded during verification.
+A transaction $T_A$ in the blockchain must be accompanied by a reference to some valid alibi transaction $T_B$, and $T_B$ must reference $T_A$, otherwise the proof is not considered credible by a Verifier.
 
 \subsection{Key Packets} \label{sssec:key_packets}
-The key packet is more than simply a list of keys that a mobile node has used to encrypt its transactions; in order to preserve the ``selective in-sequence privacy'' property of OTIT \cite{otit}, a user must be able to choose transactions that he doesn't want others to be able to decrypt.
+A key packet is more than simply a list of keys that a mobile node has used to encrypt its transactions; in order to preserve the ``selective in-sequence privacy'' property of OTIT \cite{otit}, a user must be able to choose transactions that it does not want others to be able to decrypt.
 However, in order to simultaneously preserve OTIT's ``privacy protected chronology'' property, the transaction backwards-chaining must not be broken.
 This is why two separate \textit{Key Lists} are maintained; $KL_{AL}$ is used to encrypt the backwards-chaining link and transaction timestamp, while $KL_{AT}$ encrypts the transaction data.
-For example, if node $B$ doesn't want to reveal transaction $T_{Bm-1}$, he would reveal the following key packet:
+For example, if node $B$ does not want to reveal transaction $T_{Bm-1}$, it would use the following key packet:
 \\
@@
 In this case, $KL_{BT}[m-1]$ has not been included with $KL_{BL}[m-1]$, in order to protect the privacy of this transaction.
-This means that a node who received this key packet will not be able to decrypt $B$'s transaction $T_{Bm-1}$, but can still prove that a transaction exists at that time and in the correct sequence, as $B$ will still provide $KL_{BL}[m-1]$.
-This may be needed, for example, if node $B$ doesn't want to allow anyone to decrypt any transactions he has created within 5km of his home, in order to protect his privacy.
+This means that a node who receives this key packet will not be able to decrypt $B$'s transaction $T_{Bm-1}$, but can still prove that a transaction exists at that time and in the correct sequence, as $B$ will still provide $KL_{BL}[m-1]$ (see figure \ref{fig:link}).
+This may be needed, for example, if a user does not want to allow anyone to decrypt any transactions it has created within 5km of its home, in order to protect its privacy.
+
+\begin{figure}[H]
+\begin{center}
+\resizebox {\columnwidth} {!} {\input{diagrams/link.tex}}
+\caption{A proof chain with transaction $T_{m-1}$ hidden}
+\label{fig:link}
+\end{center}
+\end{figure}
 
@@
 A node may decide to abort an exchange if it thinks it is in contact with a malicious node.
-In figure \ref{fig:aborted_transaction}, node $A$ encounters a malicious node $M$, who tries to spoof its identity with $A$.
-Node $A$ will abort the exchange once it notices that $|ts_A-ts_M| \geq \epsilon_{ts}$, or $|loc_A-loc_M| \geq \epsilon_{loc}$.
+In figure \ref{fig:aborted_transaction}, node $A$ encounters a malicious node $M$, who tries to spoof its location to node $A$.
+Node $A$ will abort the exchange once it notices that $|loc_A-loc_M| \geq \epsilon_{loc}$.
 
-To abort the exchange, $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain.
-This means that even if $M$ fabricates some data from $A$ and publishes a transaction onto the blockchain, the matching transaction from $A$ will not be present, so $M$'s transaction will be disregarded by any verifiers.
+To abort the exchange, node $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain.
+This means that even if node $M$ fabricates some data from node $A$ and publishes a transaction onto the blockchain, the matching transaction from node $A$ will not be present, so node $M$'s transaction will be disregarded by any Verifiers.
 
@@
 \section{Verification} \label{ssec:verification}
-In the verification stage, a mobile node tries to prove its location to a Verifier node, e.g.
+In the verification stage, a mobile node attempts to prove its location to a Verifier node, e.g.
 a bank.
@@
 \begin{itemize}[noitemsep,topsep=0pt]
-	\item[] $\mathbf{ID_{A}[n-1]}$ is the ID of $A$'s most recently published transaction.
-	\item[] $\mathbf{KP_{An-1}}$ is $A$'s key packet up to transaction $n-1$, and includes keys for as many transactions as $A$ feels is appropriate in order to receive verification.
-	\item[] $\mathbf{loc}$ is $A$'s current claimed GPS coordinates for which it is seeking verification.
-	\item[] $\mathbf{NP_{An-1}}$ is $A$'s \textit{Nonce Packet}, a subset of its \textit{Nonce List} (section \ref{sssec:nonce_list}).
-A Nonce Packet is the list of the nonces used to generate $A$'s most recent IDs, up to $n-1$, that $A$ is willing to share with the Verifier.
+	\item[] $\mathbf{ID_{A}[n-1]}$ is the ID of node $A$'s most recently published transaction.
+Note that $ID_A[n]$ has already been generated, but hasn't been used in a transaction yet.
+Node $A$ has generated it so that it is ready to be used in the next transaction.
+	\item[] $\mathbf{KP_{An-1}}$ is node $A$'s key packet up to transaction $n-1$, and includes keys for as many transactions as node $A$ feels is appropriate in order to receive verification.
+	\item[] $\mathbf{loc}$ is node $A$'s current claimed GPS coordinates for which it is seeking verification.
+	\item[] $\mathbf{NP_{An-1}}$ is node $A$'s \textit{Nonce Packet}, a subset of its \textit{Nonce List} (section \ref{sssec:nonce_list}).
+A Nonce Packet is the list of the nonces used to generate node $A$'s most recent IDs, up to $n-1$, that node $A$ is willing to share with the Verifier.
 \end{itemize}
@@
 The goal of the verification stage is for the Verifier to either accept or reject the location that the user is claiming.
-Given $ID_{A}[n-1]$ and $KP_{An-1}$, a Verifier is able to retrieve $A$'s previous transactions, and the transactions of all of its alibi's.
-This will allow the Verifier to recursively inspect the transactions of all alibi's used in a nodes transactions, until it is satisfied that the location can be verified or rejected.
+Given $ID_{A}[n-1]$ and $KP_{An-1}$, a Verifier is able to retrieve node $A$'s previous transactions, and the transactions of all of its alibis.
+This will allow the Verifier to recursively inspect the transactions of all alibis used in a node's transactions, until it is satisfied that the location can be verified or rejected.
 This recursive inspection can be visualised as a tree, as shown in figure \ref{fig:tree}.
@@
 If the verifier wishes to recurse more, it could inspect the black node's alibis' transaction chains.
-Note that this is a simple example, and $n = 3$, the length of the transaction chain subset provided for verification.
+Note that the example in figure \ref{fig:tree} is a simple one, with $n = 3$ being the length of the transaction chain subset provided for verification.
 In reality $n$ should be much larger.
 
-The Verifier uses $NP_{An-1}$ and $K^{+}_A$ to prove that node $A$ was the author of all of the transactions he claims to be.
-This prevents a collusion attack whereby nodes could share common transactions between different proof chains.
-When walking chronologically backwards along $A$'s proof chain, the 3rd party will ensure that the ID used in transaction $m$ on the proof chain matches $K^{+}_A(NP_{An-1}[m])$.
-
-There are a huge number of possible factors involved in reaching a conclusion from the data on the blockchain; some of these factors will likely be unique to certain Verifiers, and kept secret to improve reliability and avoid gaming.
-Some simple example factors may include:
+There are a huge number of possible factors involved in reaching a conclusion on the verifiability of a user from the data in the blockchain; some of these factors will likely be unique to certain Verifiers, and kept secret to improve reliability and avoid gaming by malicious users.
+Some simple example factors include:
 \begin{itemize}
-	\item \textbf{Alibi credibility:} if each of the node’s alibi’s have little or no alibi’s themselves, they won't be considered credible alibis, and the Verifier will reject his verification request.
-	\item \textbf{Transaction relevance:} if the Verifier considers the transactions it receives to be out of date, they will be rejected on the grounds that they are no longer relevant.
-	\item \textbf{Alibi reuse:} if the Verifier can prove that alibi’s are being reused frequently, then it will reject the verification request.
-	\begin{itemize}
-		\item Due to transaction anonymity, the Verifier may not always be able to tell if two alibi's are the same person or not.
+	\item \textbf{Alibi credibility:} if each of the node’s alibis have little or no alibis themselves, they will not be considered credible alibis, and a Verifier will reject the verification request (see figure \ref{fig:uncredible_tree}).
+	\item \textbf{Transaction relevance:} if a Verifier considers the transactions it receives to be out of date, the request will be rejected on the grounds that the transactions are no longer relevant.
+	\item \textbf{Alibi reuse:} if a Verifier can prove that alibis are being reused frequently, then it will reject the verification request.
+Due to transaction anonymity, a Verifier may not always be able to tell if two alibis are the same person or not.
 e.g.
-node $A$ could use node $B$ as an alibi, then wait for $B$ to complete $n$ more transactions, then use node $B$ again.
-		\item This is not a viable attack on the verification system.
-Depending on the size of $n$, enough time may pass between both uses of node $B$ as an alibi that the transactions are no longer relevant.
+node $A$ could use node $B$ as an alibi, then wait for node $B$ to complete $n$ more transactions, then use node $B$ again.
+	This is not a viable attack on the verification system. Depending on the size of $n$, enough time may pass between both uses of node $B$ as an alibi that the transactions are no longer relevant.
 \end{itemize}
-\end{itemize}

### 2016-04-18 thesis/diagrams/uncredible_tree.tex
updating after (another) proofread

@@
 
-\node[fill=white,label=right:Requesting node's transactions] (L1) at (-3,-1) {};
-\node[fill=gray,label=right:Requesting node's alibis transactions] (L2) at (-3,-1.5) {};
+\node[fill=white,label=right:Requesting node's transaction chain] (L1) at (-3.5,-1) {};
+\node[fill=gray,label=right:Requesting node's alibis transaction chains] (L2) at (-3.5,-1.5) {};
 

### 2016-04-18 thesis/evaluation.tex
updating after (another) proofread

@@
 \section{OTIT conformance}
-As explained in section \ref{ssec:otit}, the OTIT model \cite{otit} defines 8 desirable properties of a lcoation proof system.
+As explained in section \ref{ssec:otit}, the OTIT model \cite{otit} defines 8 desirable properties of a location proof system.
 The model introduced in chapter \ref{ch:design} is evaluated with respect to OTIT below.
@@
 Instead, the Chronological property is enforced at the time of verification.
-The chronological link created by adding $KL_{AT}(ID_{A}[n-1]|ts_A)$ to the published transaction will allow Verifier nodes to prove that the transaction is chronologically ordered.
+The chronological link created by adding $KL_{AT}(ID_{A}[n-1]|ts_A)$ to the published transaction allows Verifier nodes to prove that the transaction is chronologically ordered.
 Therefore the system preserves OTIT's ``Chronological'' property.
@@
 \subsection{Order preserving}
-This property states that the order in which location proofs were entered into the proof chain should be maintained.
+This property states that the order in which location proofs are entered into the proof chain should be maintained.
 
@@
 \subsection{Verifiable}
-This states that a Verifier should be able to verify or reject the claim by the user that he has visited the given location(s).
+This states that a Verifier should be able to verify or reject the claim by the user that it has visited the given location(s).
 
@@
 These Verifiers can verify or reject a mobile nodes claimed location by examining the nodes chronological link of transactions (as shown in figure \ref{fig:tree}).
-The Verifier will revursively generate and examine this tree until it can conclude whether the transaction chain is valid or not.
+The Verifier will recursively generate and examine this tree until it can conclude whether or not the transaction chain is valid.
 
 \subsection{Tamper evident}
-The system is tamper evident, meaning the Verifier is able to detect if the proof chain has been tampered with or modified.
+The system is tamper evident, meaning that a Verifier is able to detect if the proof chain has been tampered with or modified.
 If a malicious node creates a successful transaction with an honest node, but modifies the transaction data before publishing, a Verifier node will reject the malicious transaction.
@@
 
-The design assumes the underlying security of the blockchain, so any malicious miner nodes will not be able to tamper with existing transaction data providing that the majority of CPU power in the mining system is owned by honest miners \cite{bitcoin}.
+The design assumes the underlying security of the blockchain, so any malicious miner nodes will not be able to tamper with existing transaction data providing that the majority of CPU power in the miner network is owned by honest miners \cite{bitcoin}.
 Therefore the tamper evident property is satisfied.
@@
 
-In the system, privacy is preserved using \textit{Key Lists} \ref{ssec:key_lists}.
-Two keys are used for each transaction; $KL_{AT}[n]$ is used to encrypt the \textit{transaction data} for $A$'s $nth$ transaction, and $KL_{AL}[n]$ is used to encrypt the \textit{backwards chronological link} between $A$'s $nth$ transaction and transaction $n-1$.
+In the system, privacy is preserved using \textit{Key Lists} (See section \ref{ssec:key_lists}).
+Two keys are used for each transaction; $KL_{AT}[n]$ is used to encrypt the \textit{transaction data} for node $A$'s $nth$ transaction, and $KL_{AL}[n]$ is used to encrypt the \textit{backwards chronological link} between node $A$'s $nth$ transaction and transaction $n-1$.
 
-To control his privacy, a user can choose only to reveal $KL_{AL}[n]$ for a specific transaction $n$.
-This may be useful if a user does not wish to reveal transaction data for transactions created within a certain distance of his house, for example.
-Hiding $KL_{AT}[n]$ while revealing $KL_{AL}[n]$ has the advantage of preserving the user's privacy while maintaining a clear backwards chronological link of transactions for the Verifier to follow.
-This simulatneously preserves both privacy and chronological integrity.
+To control its privacy, a user can choose only to reveal $KL_{AL}[n]$ for a specific transaction $n$.
+This may be useful if a user does not wish to reveal transaction data for transactions created within a certain distance of its house, for example.
+Hiding $KL_{AT}[n]$ while revealing $KL_{AL}[n]$ has the advantage of preserving the user's privacy while maintaining a clear backwards chronological link of transactions for a Verifier to follow.
+This simultaneously preserves both privacy and chronological integrity.
 
@@
 
-A \textit{sub-set} of size $m$ of a node $A$'s proof chain, beginning at proof $n$, contains all proofs in the sequence $ID_{A}[n-m] - ID_{A}[n]$.
-Every transaction in this chain is split into two parts (a transaction data and link data part), and separately encrypted.
-If a node reveals keys for a verifier decrypt all transactions in the sequence $ID_{A}[n-m] - ID_{A}[n]$, it will not be possible for the verifier to discover transaction $ID_{A}[n-m-1]$, or any transaction outside the sequence $ID_{A}[n-m] - ID_{A}[n]$.
+A \textit{sub-set} of size $m$ of a node $A$'s proof chain, beginning at proof $n$, contains all proofs in the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$.
+Every transaction in this chain is split into two parts, a transaction data and link data part, and separately encrypted.
+If a node reveals keys for a Verifier to decrypt all transactions in the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$, it will not be possible for the Verifier to discover transaction $ID_{A}[n-m-1]$, or any transaction outside the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$.
 
@@
 
-In this system, any dishonest user attempting to obtain a location proof with an honest alibi will not succeed, as the honest alibi will abort the exchange (see section \ref{ssec:aborting_exchanges}).
+In this system, any dishonest user attempting to obtain a false location proof with an honest alibi will not succeed, as the honest alibi will abort the exchange (see section \ref{ssec:aborting_exchanges}).
 A dishonest user who publishes a transaction onto the blockchain with a fabricated alibi will also not succeed, as the transaction will be rejected during verification if a Verifier can't find the matching alibi transaction.
@@
 \subsection{Malicious intruders}
-A malicious intruder offers to help another user to prove a false location, but doesn't prove a false location for himself.
+A malicious intruder offers to help another user to prove a false location, but doesn't prove a false location for itself.
 
@@
 These transactions will be successfully published onto the blockchain.
-However, if this user attempts to have his transaction chain verified, a Verifier will quickly notice the lack of credible alibis in the proof chain, indicating malicious activity, and reject the proof request.
+However, if this user attempts to have its transaction chain verified, a Verifier will quickly notice the lack of credible alibis in the proof chain, indicating malicious activity, and reject the proof request.
 A sample tree of a node with uncredible alibis is shown in figure \ref{fig:uncredible_tree}.
@@
 \begin{center}
-\resizebox {0.5\columnwidth} {!} {\input{diagrams/uncredible_tree.tex}}
-\vspace{-3cm}
+\resizebox {0.6\columnwidth} {!} {\input{diagrams/uncredible_tree.tex}}
+\vspace{-3.25cm}
 \caption{A proof chain with uncredible alibis}
@@
 
-Identity discovery is impossible by design in this sytem.
+Identity discovery is impossible by design in this system.
 By using a different, seemingly random identity for each transaction, it is impossible for a curious user to determine if two transactions belong to the same user or not.
-It is therefore impossible for a curious user to learn another users identity by monitoring location proofs.
+It is therefore impossible for a curious user to learn another user's identity by monitoring location proofs.
 
 \subsection{Malicious applications}
-A malicious application is one that tries to take advantage of a users information as the user seeks verification.
+A malicious application is one that tries to take advantage of a user's information as the user seeks verification.
 
-This attack does not affect this system, as a user will only seek verification from applications (verifiers) it deems trustworthy.
+This attack does not affect this system, as a user will only seek verification from applications (Verifiers) it deems trustworthy.
 Verifiers, such as banks or employers, will be known to the user, and therefore trusted.
-The user also has complete control over which verifiers it chooses to seek verification from, it is not obliged to send verification requests to any verifier.
+The user also has complete control over which Verifiers it chooses to seek verification from, it is not obliged to send verification requests to any Verifier.
 
@@
 
-\subsection{Weak identities}.
-In a weak identity attack, a user gives his public key or identity to another colluding user in order to create a location proof.
+\subsection{Weak identities}
+In a weak identity attack, a user gives its public key or identity to another colluding user in order to create a location proof.
 
@@
 Exchanging public keys or identities between colluding users offers no advantage.
-This is because the Verifier will ensure that any users requesting verification own the private key corresponding to the public key transferred during the verification request (see section \ref{ssec:verification}).
+This is because a Verifier will ensure that any users requesting verification own the private key corresponding to the public key transferred during the verification request (see section \ref{ssec:verification}).
 
@@
 
-It is therefore impossible to implicate an honest user in a location proof, without finding vulnerabilities outside the location proof system (for example by compromising their device).
+It is therefore impossible to implicate an honest user in a location proof, without exploiting vulnerabilities outside the location proof system (for example by compromising the underlying assumed security of the device).
 
 \subsection{False assertion}
-In a false assertion attack, two malicious users collude to create false location proofs for themselves.
+In a false assertion attack, two malicious users collude to create false location proofs for each other.
 
@@
 Providing that the system is comprised of a majority of honest nodes, this attack will not succeed.
-It will be obvious to a Verifier after construcing a graph of the nodes alibi transaction (as shown in section \ref{ssec:verification}) that the graph lacks alibi credibility, and therefore two malicious users are likely colluding to create location proofs for themselves.
+It will be obvious to a Verifier after constructing a graph of the node's alibi transaction (as shown in section \ref{ssec:verification}) that the graph lacks alibi credibility, and therefore two malicious users are likely colluding to create location proofs for themselves.
 Therefore the system is not vulnerable to this attack.
@@
 
-If the proof has not been added to the blockchain yet, then it is possible for the malicous user to modify it to attempt to spoof a false location.
+If the proof has not been added to the blockchain yet, then it is possible for the malicious user to modify it to attempt to spoof a false location.
 However this attack will not work on this system.
@@
 
-This system is resilient against a most relay attacks.
+This system is resilient against most relay attacks.
 This is because proofs created using a proxy user will be inconsistent with the other proofs in a users proof chain.
@@
 Its only purpose is to proxy exchange data between honest nodes and the other malicious node, the \textit{attacker}.
+The attacker will never request a proof by itself, it will always route its requests through the proxy user.
 
@@
 
-While some studies have been done on Sybil attacks in decentralised systems \cite{sybil}.
-There are various methods of mitigating against a subil attack, however a solution for the Sybil attack in a decentralised system is considered an open problem.
+Previous work has shown that preventing a Sybil attack is impossible in a fully decentralised system \cite{sybil}.
 This system is therefore vulnerable to a highly targeted Sybil attack.
+However, there are various possible methods of mitigating against such an attack.
+
+Introducing a penalty for identity creation would mitigate against an attempted large-scale Sybil attack.
+For example, if a node is required to solve a proof-of-work puzzle before creating an identity, a large-scale Sybil attack would prove extremely computationally expensive for the attacker.
+This is an impractical mitigation however, as this system is designed to operate on mobile phones.
+Mobile phones should not be forced to complete proof-of-work puzzles, as computational resources and power supply is very limited when compared with miner nodes, which are servers.
+
+Another possible mitigation involves using a web of trust, which  allows users of a system to express their trust of other users \cite{weboftrust}.
+Users of the system build a large network of trust relationships, allowing other users to assess the trustworthiness of a potential alibi before creating an exchange with it.
+This technique of mitigating against the Sybil attack would involve a trade-off with the privacy protecting features currently present in the system, because a web of trust requires globally unique, static user identification to operate.
+This system uses non-unique, dynamic user identification in order to preserve privacy.
+
+Previous research \cite{sybil} has concluded that the only provably correct way of preventing a Sybil attack in a decentralised system is to use a \textit{centralised} name system to coordinate the distribution of identities.
+Therefore a Sybil attack vulnerability must be taken out of the scope of this system, as this system is focused on a decentralised approach to location verification.

### 2016-04-18 thesis/introduction.tex
updating after (another) proofread

@@
-\section{Project and Motivation}
+\section{Project and motivation}
 Location verification is the process of verifying whether a \textit{node} (computer) is physically present at a location it claims to be.
-Existing location proof systems attept to use centralised, trusted ``authoritive'' nodes to provide proof of another node's location.
+There are two general categories of location verification; \textit{observation} and \textit{proof}.
+In location observation, a user's location is determined by observing certain properties of the user, its IP address for example.
+This is a cheap but very unreliable method of location verification.
+In location proof, a user's location can be proven reliably.
+
+Existing location proof systems attempt to use centralised, trusted ``authoritative'' nodes to provide proof of another node's location.
 These approaches require investment in infrastructure, and are subject to privacy violation and denial of service attacks.
 This project aims to present a \textit{decentralised} solution to this problem.
-A decentralised location proof system is a system in which there is no ``authoritive source'' trusted and relied upon to provide and store sensitive location information.
+A decentralised location proof system is a system in which there is no ``authoritative source'' trusted and relied upon to provide and store sensitive location information.
 
 This project describes a decentralised location proof system that is capable of operating on \textit{mobile nodes} (mobile devices).
-I propose a design in which location proofs are obtained using other untrusted mobile nodes as \textit{alibi's}.
+I propose a design in which location proofs are obtained using other untrusted mobile nodes as \textit{alibis}.
 Proofs will be created as two mobile nodes communicate over an ad-hoc bluetooth network, transfer encrypted location information, and publish it on a public append-only bulletin board, known as a \textit{blockchain}.
@@
 \section{Report outline}
-This report consists of four additional chapters, listed biefly below.
+This report consists of four additional chapters, listed briefly below.
 
 \subsection{Background}
-Chapter 2 begins with a brief introduction to the problem space.
+Chapter 2 begins with an introduction to the problem space.
 A brief explanation of decentralised and distributed networks, as well as the blockchain is then presented, in the context of location proof systems.
@@
 
-\subsection{Future work}
+\subsection{Conclusion and Future Work}
 Chapter 5 presents the conclusions of the project, and details interesting areas for possible future work relating to the project.

### 2016-04-18 thesis/thesis.tex
Updates after proofreading Introduction and Design chapters
Adding evaluation chapter
updating after (another) proofread

@@
 \usepackage{tikz}
-\usetikzlibrary{calc,arrows}
+\usetikzlibrary{matrix,positioning,arrows.meta,arrows,calc}
 \usepackage{enumitem}
@@
 \begin{document}
+\pagenumbering{roman}
 \maketitle
@@
 
-\chapter{Introduction}
+\pagenumbering{arabic}
+\chapter{Introduction} \label{ch:introduction}
 \input{introduction.tex}
 
-\chapter{Background}
+\chapter{Background} \label{ch:background}
 \input{background.tex}
 
-\chapter{Design}
+\chapter{Design} \label{ch:design}
 \input{design.tex}
 
-\chapter{Evaluation}
+\chapter{Evaluation} \label{ch:evaluation}
 \input{evaluation.tex}
 
-\chapter{Future work}
+\chapter{Conclusion and Future Work} \label{ch:conclusion}
+\input{conclusion.tex}
 
@@
 \bibitem{sybil}
-  J.R. Douceur,
-  ``The sybil attack'',
-  Druschel, P., Kaashoek, M.F., Rowstron, A. (eds.) IPTPS 2002. LNCS, vol. 2429, pp. 251–260,
-  Springer, Heidelberg (2002).
+  J. Douceur,
+  ``The Sybil Attack'',
+  In First IPTPS,
+  March 2002.
 
@@
 
+\bibitem{weboftrust}
+  R. V. Guha, R. Kumar, P. Raghavan, and A. Tomkins,
+  ``Propagation of trust and distrust'',
+  in Proceedings of WWW, pp. 403–412,
+  2004.
+
 \end{thebibliography}

### 2016-04-23 thesis/background.tex
Adding final updates

@@
 \section{Proving location}
-As an increasing amount of personal information is accessible on the internet and therefore on mobile devices, the security that previously existed by requiring physical interaction between humans to transfer sensitive data is lost.
+An increasing amount of personal information is accessible on the internet, and therefore on mobile devices.
+Hence the security that previously existed by requiring physical interaction between humans to transfer sensitive data is lost.
 
@@
 There is currently no ubiquitous method of \textit{proving} a mobile user's location at a given time over the internet.
+This problem will become increasingly pronounced as the amount of personal information accessible on the internet increases.
+For example, banks wishing to reduce fraud may soon benefit from requiring a user to prove its location before logging in to their mobile banking application.
+A feature like this is impossible without an underlying ubiquitous location proof system.
+
 Many companies, such as Netflix, use GeoIP databases such as MaxMind \cite{maxmind} to estimate a user's location based on its IP address.
@@
 
-Better solutions to this problem exist.
+However, more rigorous solutions to the problem of determining a user's location exist.
 \textit{Location proof systems} allow users of the system to \textit{prove} their location to another user, by creating \textit{location proofs}.
@@
 \section{Distributed and decentralised systems}
-A \textit{distributed} system is a system which distributes the computation of a task across multiple nodes (computers) connected over a network.
-These nodes are assigned a task from a central node, and then work together and communicate to complete the task by passing messages to each other over the network \cite{distributed}.
+A \textit{distributed} system is a system which distributes the computation of a task across multiple nodes connected over a network.
+These nodes are assigned a task from a central node, then proceed to work together and communicate to complete the task by passing messages to each other over the network \cite{distributed}.
 
-For example, Google search indexes are not computed on just one node, rather on a network of nodes that communicate by sending messages to each other.
+For example, Google search indexes are not computed on just one node, but rather on a network of nodes that communicate by sending messages to each other.
 Google therefore \textit{distributes} the task of calculating search indexes across multiple nodes.
-This has two main advantages; It is less time consuming, because different index calculations can be computed on different nodes at the same time, and it is scalable, because nodes can be added or removed from the network dynamically, to meet demand.
+This has two main advantages: It is less time consuming, because different index calculations can be computed on different nodes at the same time, and it is scalable, because nodes can be added or removed from the network dynamically, to meet demand.
 
-A \textit{decentralised} system is similar to a distributed system, except no node is in charge.
-Nodes in a decentralised network still communicate by passing messages to each other over the network, but unlike a distributed system, they are not assigned tasks by a central or master node.
-Bitcoin \cite{bitcoin} is a good example of a large-scale decentralised system.
+A \textit{decentralised} system is similar to a distributed system, except there is no central node.
+Nodes in a decentralised network still communicate by passing messages to each other over the network but, unlike a distributed system, they are not assigned tasks by a central or master node.
+A well-known example of a large-scale decentralised system is Bitcoin \cite{bitcoin}.
 Two nodes in the Bitcoin network can choose to send money between themselves, creating a transaction.
-They make the details of that transaction public.
+The transaction details are then made public.
 The two nodes therefore create and publish the transaction without coordination from a central node.
 
-In the context of this project, a distributed location proof system is considered to be a proof system where the task of facilitating user proof request and creation is distributed across multiple \textit{worker nodes}, which are controlled and coordinated by a central node.
+In the context of this project, a distributed location proof system is considered to be a proof system where the task of facilitating user proof request and creation is distributed across multiple \textit{worker nodes}.
+These are controlled and coordinated by a central node.
 This allows a higher volume of proofs to be created concurrently compared with using a single node, while maintaining centralised and simple control over the system.
@@
 
-A decentralised location proof system is considered to be one where no node is in charge of controlling or coordinating the system.
+A decentralised location proof system is considered to be one where no central node controls or coordinates the system.
 Nodes can create and publish location proofs between themselves, without the need for a central third party to coordinate their interaction (figure \ref{fig:decentralised_location}).
-This makes coordination more complex, but means that no node is considered to be ``in charge'' of the system.
+This makes coordination more complex, but removes the threats associated with using a central node to store and issue location proofs.
 
@@
 A femtocell \cite{femtocell} is a small cellular antenna that connects to a mobile network operator (such as Vodafone) via the Internet, which allows mobile networks (e.g.
-networks used for calls and texts) to be extended on demand.
+networks used for calls and SMS messages) to be extended on demand.
 Location verification over the internet is made possible by determining which femtocell a mobile node is connected to as it transfers data over Wi-Fi.
@@
 
-This solution requires investment in additional hardware to supplement existing Wi-Fi access points, and requires access to mobile providers' user databases to identify users' locations (see figure \ref{fig:hp_labs}).
-Note that the two lines between the user and the AP in figure \ref{fig:hp_labs} indicates that the user is connected to the AP \textit{and} its attached femtocell.
+However, this solution requires investment in additional hardware to supplement existing Wi-Fi access points, and requires access to mobile providers' user databases to identify users' locations (see figure \ref{fig:hp_labs}).
 
@@
 \resizebox {0.45\columnwidth} {!} {\includegraphics{diagrams/hp_paper.png}}
-\caption{Hardware-based proof system (Adapted from Brassil et al. \cite{brassil})}
+\caption[Hardware-based proof system]{Hardware-based proof system (Adapted from Brassil et al.
+\cite{brassil}).
+Note that the two lines between the user and the AP indicates that the user is connected to the AP \textit{and} its attached femtocell.}
 \label{fig:hp_labs}
@@
 The use of a centralised system, as described in figure \ref{fig:hp_labs}, creates security, privacy and vulnerability issues.
-An attacker who succeeds in compromising the security of the central server can create unlimited false location proofs for itself, or violate the privacy of the users of the system, and potentially track their location.
+An attacker who succeeds in compromising the security of the central server can create unlimited false location proofs for itself, or it can violate the privacy of the users of the system, and potentially track their location.
 This is because in this system, location proof data resides with the central server.
-This means that the user has no control over the security of their proofs, and an attacker could seize them.
-The central system architecture is also vulnerable, in the sense that a resource availability attack such as a DDoS attack \cite{ddos} could render the central architecture unavailable, making location verification unavailable.
+Thus the user has no control over the security of their proofs, and an attacker could seize them.
+The central system architecture is vulnerable to other problems, such as central node hardware failure, or resource availability attacks.
+For example, a DDoS attack \cite{ddos} could render the central architecture unavailable, making location verification unavailable.
 \\
 
-Luo et al.
-propose a system that uses software installed on Wi-Fi access points to allow users to create location proofs \cite{luo}.
+Another approach by Luo et al.
+proposes a system that uses software installed on Wi-Fi access points to allow users to create location proofs \cite{luo}.
 In their system, each access point is given a \textit{group signature} by a central server, and can sign location proofs for users (figure \ref{fig:luo_diagram}).
@@
 \resizebox {0.5\columnwidth} {!} {\includegraphics{diagrams/ap_paper.png}}
-\caption{Distributed proof system on access points (Adapted from Luo et al. \cite{luo})}
+\caption[Distributed proof system on access points]{Distributed proof system on access points (Adapted from Luo et al. \cite{luo})}
 \label{fig:luo_diagram}
@@
 \resizebox {0.65\columnwidth} {!} {\input{diagrams/luo_transaction.tex}}
-\caption{Proof request with group signature (Adapted from Luo et al. \cite{luo})}
+\caption[Proof request with group signature]{Proof request with group signature (Adapted from Luo et al. \cite{luo})}
 \label{fig:luo_transaction}
@@
 
-This system creates \textit{proactive} location proofs.
+Unlike the system proposed by Brassil et al., this system creates \textit{proactive} location proofs.
 A proactive location proof is one which is created before it is needed.
 The user creates application-independent location proofs, and can use them at a later time with any application(s) it chooses.
+This is essential in a decentralised proof system, where proofs \textit{cannot} be application dependent by definition.
+
+Using a group signature allows the system to be very easily distributed, while still coordinated by a central node.
+However, a malicious user who attacks the central server and discovers the group signature can create unlimited false proofs for itself.
 \\
@@
 takes a different approach, by using other users as witnesses to a location claim \cite{khan}.
-In this system, a \textit{witness} physically located near the user is used by the central server to verify the user's location claim (figure \ref{fig:witness_paper}).
+In this system, a \textit{witness} who is physically located near the user is used by the central server to verify the user's location claim (figure \ref{fig:witness_paper}).
 Like the model proposed by Luo et al., this system allows the user to have control over their own privacy, as the user owns the location proof.
@@
 \section{Blockchain}
-In Bitcoin \cite{bitcoin}, the entire transaction history is stored in the \textit{blockchain}.
-This is a decentralised, append-only ledger (database) \cite{blueprint}.
-The blockchain is maintained by a network of \textit{miner} nodes competing to collect transactions into a new block, sign that block by solving a difficult puzzle known as a \textit{proof-of-work}, and append it to the ledger.
+In a decentralised location proof system, location proofs cannot reside solely with the owner, as it would be difficult to detect proof tampering.
+Instead, existing decentralised systems such as Bitcoin \cite{bitcoin} store data publicly, but encrypt it with a key known only to the owner.
+In Bitcoin, this is made possible using a \textit{blockchain}, which provides a public, tamper-proof database for the transaction data.
+A decentralised location proof system can use a blockchain to store location proofs publicly, encrypted with a key known only to the user who created the proofs.
+
+The blockchain is a decentralised, append-only ledger (database) \cite{blueprint}.
+It is maintained by a network of \textit{miner} nodes competing to collect transactions into a new block, sign that block by solving a difficult puzzle known as a \textit{proof-of-work}, and append it to the ledger.
 It is used in Bitcoin to enforce consensus; every miner in the network agrees that all blocks in the blockchain are valid, due to the presence of their associated proof-of-work.
@@
 \section{Design goals} \label{sec:design_goals}
-Before designing the system, a number of goals must be defined and an attempt made to satisfy them in the design. The design goals of this project are listed below.
+Before designing the system, a number of goals must be defined and an attempt made to satisfy them in the system design.
+The goals for this project were determined by examining the design goals of previous work \cite{brassil, luo, khan} discussed in section \ref{ssec:proof_systems}, which is considered to be the state of the art.
+This system must satisfy the same goals as these centralised proof systems, along with an additional goal of decentralisation.
 
 \begin{enumerate}
-	\item The system must be \textit{privacy preserving}.
-It must not be possible for a malicious user to obtain any additional information from an honest user other than the information the honest user intended to release.
-	\item False location proofs must be detectable. It must be possible to detect any location proofs attempting to prove false information.
 	\item The system must be decentralised, and cannot rely on any central nodes. This is discussed in section \ref{ssec:centralised}.
 	\item The design must conform to the desirable properties defined in OTIT (discussed in section \ref{ssec:otit}).
-	\item The system must not be vulnerable to any known threats (section \ref{ssec:threats}).
+	\item The system must not be vulnerable to any known threats.
+Threats are identified in previous publications \cite{luo,khan}, which outline potential attacks on location proof systems (section \ref{ssec:threats}).
 \end{enumerate}
@@
 These systems assume that the central node is honest, always available, and cannot be compromised by an attacker.
-Since the central node is in charge of coordinating the system, compromising it allows an attacker potentially unlimited control over the system.
-This completely violates a user's privacy, as the central node may contain sensitive information about users and their location, or a means of retrieving sensitive information, such as decryption keys.
-Users of the system also have to assume that the central node is available at all times, otherwise the system is considered unavailable, or ``down''.
+Since the central node is in charge of coordinating the system, compromising it allows an attacker to potentially take complete control over the system.
+This destroys the privacy of each user, as the central node may contain sensitive information about users and their location, or a means of retrieving sensitive information, such as decryption keys.
+Users of the system also have to trust that the central node is always available which, in reality, may not be true.
 
-These problems do not occur in a decentralised location proof system, because no node is considered to be ``in charge''.
-If no node is in charge, any node(s) can join or leave the network without altering the state of the network, or making any services unavailable.
+These problems do not occur in a decentralised location proof system, because all nodes have an equal level of authority.
+Any node(s) can join or leave the network without altering the state of the network, or without making any services unavailable.
 This lack of authority prevents privacy breaches, but presents other issues.
@@
 \subsection{OTIT} \label{ssec:otit}
-Khan et al. present the \textit{OTIT} model, a ``model for designing secure location provenance'' \cite{otit}. It defines the following 8 desirable properties of a location proof system:
+Khan et al.
+present the \textit{OTIT} model, a ``model for designing secure location provenance'' \cite{otit}.
+It defines the 8 properties that all location proof systems should satisfy.
+This project will also aim to satisfy each of these properties, which are defined below.
 \begin{itemize}
@@
 	\item[] \textbf{Privacy preserved}: When the proof chain is verified for specific location proofs, privacy is preserved for the other location proofs within the chain.
-	\item[] \textbf{Selective In-sequence privacy}: The user should be able to choose not to reveal some location proofs within the proof chain when seeking verification.
+	\item[] \textbf{Selective in-sequence privacy}: The user should be able to choose not to reveal some location proofs within the proof chain when seeking verification.
 	\item[] \textbf{Privacy protected chronology}: The system should ensure that the user does not hide important information from the items within the subset of the proof chain.
@@
 \subsection{Threats} \label{ssec:threats}
-A number of related publications \cite{luo,khan} have identified various potential threats (or attacks) on location verification systems. These are outlined below.
+A number of related publications \cite{luo,khan} have identified various potential threats (or attacks) on location proof systems.
+A threat on a location proof system is a potential vulnerability.
+Threats allow a malicious user (an attacker) to gain an advantage over other users by exploiting weaknesses in the system.
+In a location proof system, a threat could potentially allow a malicious user to create false proofs for itself, or violate another user's privacy.
+
+This project will first introduce the threats being considered by defining them, then it will describe the proposed model of a decentralised location proof system, and finally analyse the model with respect to each defined threat.
+The threats considered in this project are a combination of all threats considered by Luo et al.
+\cite{luo} and Khan et al.
+\cite{khan} in their centralised location proof system models.
+These are defined below.
 
@@
 \end{itemize}
+
+This project aims to design a decentralised location proof system which satisfies the aforementioned requirements as well as addressing and mitigating the threats posed by malicious users to such a system.

### 2016-04-23 thesis/conclusion.tex
Adding final updates

@@
 There are many worthwhile areas for future work, because to the best of the author's knowledge, this is the first attempted design of a fully decentralised location proof system.
+These are mentioned briefly below.
 
 \subsection{Verification techniques}
-Section \ref{ssec:verification} outlined a number of simple verification techniques that a Verifier node could use to analyse the a proof chain.
+Section \ref{ssec:verification} outlined a number of simple verification techniques that a Verifier node could use to analyse a proof chain.
 There is potential for further research on advanced techniques of analysing proof chain trees to determine the validity of a user's proof request.
@@
 \section{Conclusion}
-This project presented the design of a decentralised location proof system.
 The aim of the project was to design a system that satisfied the design goals, as defined in section \ref{sec:design_goals}.
-This system satisfies all of the requirements of OTIT \cite{otit}, and all but one of the threats defined in section \ref{ssec:threats}.
+This system satisfies all eight of the desirable properties of a location proof system as defined by OTIT \cite{otit}, and all but one of the threats defined in section \ref{ssec:threats}.
 However, chapter \ref{ch:evaluation} concluded that this Sybil attack threat must be highly targeted to be effective.
+Most Sybil attacks can be mitigated against using various techniques, and many simple Sybil attacks will be clearly visible to Verifiers without any mitigation whatsoever.
 
-In conclusion, the model presented in this project is a viable design of a decentralised location proof system, providing that the Sybil attack vulnerability can be heavily mitigated against or prevented outright.
+It is interesting to compare this system to existing centralised location proof systems by Khan et al.
+\cite{khan} and Luo et al.
+\cite{luo}.
+As discussed throughout this project, a decentralised solution to location proof generation is more resilient to attack than these centralised systems by design.
+However, when compared to both of these systems, the model presented in this project is more resilient against attacks such as wormhole attacks, weak identities and false assertion attacks.
+This resilience is not due purely to the decentralised nature of the model, but also to interesting properties of the design, such as identity generation.
+
+This project has explained the shortcomings of centralised location proof systems, and it has presented a viable design of a decentralised location proof system, which is to the author's knowledge the first system design of its kind.
+This decentralised location proof system retains all of the desirable properties of current centralised location proof systems, and is more resilient to attack, as demonstrated during evaluation.
+
+It can therefore be concluded that the advantages of this decentralised location proof system, along with its resilience to attack, make it an excellent candidate for a secure, ubiquitous location proof system.

### 2016-04-23 thesis/design.tex
Adding final updates

@@
+This chapter details the design of a decentralised location proof system.
+It starts with a general overview of the proposed system, before explaining in detail the three major components: Identities (section \ref{sec:identities}), Transactions (section \ref{sec:transactions}), and Verification (section \ref{ssec:verification}).
+
 The location proof system proposed in this project allows \textit{mobile nodes} to create location proofs by initiating an \textit{exchange} with another anonymous mobile node.
@@
 
-\section{Identities}
+\section{Identities} \label{sec:identities}
 In order to preserve users' privacy, a user will only ever use an identity for one transaction, before generating a new one.
@@
 It is therefore possible that during verification, a Verifier node may find multiple transactions with the same ID while searching the blockchain.
-Verifiers are provided with decryption key from the requesting node for the transactions they are searching for, which will only successfully decrypt one of the transactions with the duplicate ID.
+Verifiers are provided with decryption keys from the requesting node for the transactions they are searching for, which will only successfully decrypt one of the transactions with the duplicate ID.
 A Verifier will try to decrypt each one until it finds the one that can be decrypted successfully.
 
-\newpage
 \section{Transactions} \label{sec:transactions}
@@
 
-To abort the exchange, node $A$ terminates the ad-hoc network with node $M$, and won't publish anything onto the blockchain.
+To abort the exchange, node $A$ terminates the ad-hoc network with node $M$, and will not publish anything onto the blockchain.
 This means that even if node $M$ fabricates some data from node $A$ and publishes a transaction onto the blockchain, the matching transaction from node $A$ will not be present, so node $M$'s transaction will be disregarded by any Verifiers.
 
-\begin{figure}
+\begin{figure}[H]
 \resizebox {\columnwidth} {!} {\input{diagrams/aborted_transaction.tex}}
@@
 \begin{center}
-\resizebox {0.8\columnwidth} {!} {\input{diagrams/verify_request.tex}}
+\resizebox {0.75\columnwidth} {!} {\input{diagrams/verify_request.tex}}
 \caption{Verification request}
@@
 	\item[] $\mathbf{ID_{A}[n-1]}$ is the ID of node $A$'s most recently published transaction.
-Note that $ID_A[n]$ has already been generated, but hasn't been used in a transaction yet.
+Note that $ID_A[n]$ has already been generated, but has not been used in a transaction yet.
 Node $A$ has generated it so that it is ready to be used in the next transaction.
@@
 The goal of the verification stage is for the Verifier to either accept or reject the location that the user is claiming.
-Given $ID_{A}[n-1]$ and $KP_{An-1}$, a Verifier is able to retrieve node $A$'s previous transactions, and the transactions of all of its alibis.
+Given $ID_{A}[n-1]$ and $KP_{An-1}$, a Verifier is able to retrieve node $A$'s previous transactions, and the transactions of all its alibis.
 This will allow the Verifier to recursively inspect the transactions of all alibis used in a node's transactions, until it is satisfied that the location can be verified or rejected.

### 2016-04-23 thesis/evaluation.tex
Adding final updates

@@
 The previous chapter introduced a model for a decentralised location proof system.
-This chapter will present an evaluation of the model with respect to the design goals defined in section \ref{sec:design_goals}.
+This chapter will present a case-based evaluation of the model with respect to the design goals defined in section \ref{sec:design_goals}.
+
+In a case-based evaluation, the response of the system model to each \textit{case} (property or threat) is reasoned about.
+A conclusion is then reached as to the effectiveness of the model in satisfying or defending against each property-based or threat-based case, respectively.
+Evidence is shown in the form of logical arguments (reasoning) deriving from the definition of each case.
+This kind of evaluation contrasts a benchmark-based evaluation, where a system implementation is benchmarked against a test suite, because this system is a model rather than an implementation.
 
@@
 
-The sytem described in chapter \ref{ch:design} inherently satisfies this property of OTIT.
+The system described in chapter \ref{ch:design} inherently satisfies this property of OTIT.
 Verifier nodes may be operated by banks, employers, or other parties who have a vested interest in allowing their customers or employees to be able to prove their location.
@@
 A \textit{sub-set} of size $m$ of a node $A$'s proof chain, beginning at proof $n$, contains all proofs in the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$.
-Every transaction in this chain is split into two parts, a transaction data and link data part, and separately encrypted.
+Every transaction in this chain is split into two parts, a transaction data and link data part, which are separately encrypted.
 If a node reveals keys for a Verifier to decrypt all transactions in the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$, it will not be possible for the Verifier to discover transaction $ID_{A}[n-m-1]$, or any transaction outside the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$.
@@
 
-In this system, the data is stored in a central blockchain that the Verifier has access to, and the user provides the Verifier  with decryption keys and indexes into just a sub-section of this data.
-Therefore the data sent to from the user to the Verifier, $KP_{An}$, is quite small in size.
+In this system, the data is stored in a central blockchain that the Verifier has access to.
+A user provides a Verifier  with decryption keys and indexes for a sub-section of this data.
+Therefore the data sent from the user to the Verifier, $KP_{An}$, is quite small in size.
 
-The Verifier has the freedom to decide how comprehensively to investigate the users data; It can decide how far to recurse while investigating the tree of alibi relationships.
-This property of OTIT is therefore satisfied by allowing the Verifier to decide how complex the verification process needs to be.
+Verifiers have the freedom to decide how comprehensively to investigate a user's data; They can decide how far to recurse while investigating the tree of alibi relationships.
+This property of OTIT is therefore satisfied by allowing Verifiers to decide how complex the verification process needs to be.
 
 \section{Threat analysis}
+Section \ref{ssec:threats} defined a number of threats being considered for this project, which were gathered from existing publications \cite{luo,khan}.
+The system presented in this project is evaluated against these threats below.
+
 \subsection{False presence}
@@
 In this system, any dishonest user attempting to obtain a false location proof with an honest alibi will not succeed, as the honest alibi will abort the exchange (see section \ref{ssec:aborting_exchanges}).
-A dishonest user who publishes a transaction onto the blockchain with a fabricated alibi will also not succeed, as the transaction will be rejected during verification if a Verifier can't find the matching alibi transaction.
+A dishonest user who publishes a transaction onto the blockchain with a fabricated alibi will also not succeed, as the transaction will be rejected during verification if a Verifier cannot find the matching alibi transaction.
 The system is therefore not vulnerable to a false presence attack.
@@
 \subsection{Malicious intruders}
-A malicious intruder offers to help another user to prove a false location, but doesn't prove a false location for itself.
+A malicious intruder offers to help another user to prove a false location, but does not prove a false location for itself.
 
@@
 Identity discovery is impossible by design in this system.
-By using a different, seemingly random identity for each transaction, it is impossible for a curious user to determine if two transactions belong to the same user or not.
+By using a different, seemingly random identity for each transaction, it is impossible for a curious user to determine if two transactions belong to the same user.
 It is therefore impossible for a curious user to learn another user's identity by monitoring location proofs.
@@
 
+This result highlights another advantage of modeling a location proof system in a decentralised manner.
+Luo et al.
+\cite{luo}, in their model of a centralised location proof system, identified a wormhole attack as a vulnerability of their model, and removed it from scope.
+Due to the lack of a central authority to fool, the decentralised system proposed in this project is not vulnerable to a wormhole attack by design.
+
 \subsection{Weak identities}
@@
 A weak identity attack will not affect this system.
-Exchanging public keys or identities between colluding users offers no advantage.
-This is because a Verifier will ensure that any users requesting verification own the private key corresponding to the public key transferred during the verification request (see section \ref{ssec:verification}).
+Exchanging public keys or identities between colluding users offers no advantage, as this system does not use fixed identifiers to identify users, rather it uses a seemingly random identity generation technique, as explained in section \ref{sec:identities}.
+A user will exchange its constant (unchanging) public key when requesting verification, however, a Verifier will check that all requesting users own the private key corresponding to their claimed public key (see section \ref{ssec:verification}).
+Malicious users attempting a weak identity attack will be unable to spoof a valid private key, assuming the security of the underlying cryptography system.
+
+Luo et al.
+\cite{luo} identified a weak identity attack as a further weakness in their model.
+The evaluation above shows that by using a technique for seemingly random identity generation, this system remains invulnerable to a weak identity attack, even in a decentralised setting.
 
@@
 
+This is an especially interesting result.
+The publication that presented this threat case \cite{khan} identified a false assertion attack as a vulnerability in their system, and took it out of scope.
+This proves that in the case of false assertion, the decentralised model presented in this paper outperforms existing centralised models.
+
 \subsection{Proof switching}
@@
 However this attack will not work on this system.
-Any Verifier will reject the transaction on the grounds that it contains contradictory information to the alibis transaction, which has not been modified.
+Any Verifier will reject the transaction on the grounds that it contains contradictory information to the alibi's transaction, which has not been modified.
 
@@
 Therefore a Sybil attack vulnerability must be taken out of the scope of this system, as this system is focused on a decentralised approach to location verification.
+However, a Sybil attack would have to be highly targeted in order to fool a Verifier into verifying a false location proof chain, due to multiple strong options of mitigation against such an attack.
+
+\null
+The evaluation presented in this chapter shows that despite the current vulnerability to a Sybil attack, this model is a viable design of a decentralised location proof system.
+This is especially interesting because the model was evaluated against cases used to evaluate centralised proof systems, outperforming them in certain cases.

### 2016-04-23 thesis/introduction.tex
Adding final updates

@@
 
-This project describes a decentralised location proof system that is capable of operating on \textit{mobile nodes} (mobile devices).
-I propose a design in which location proofs are obtained using other untrusted mobile nodes as \textit{alibis}.
-Proofs will be created as two mobile nodes communicate over an ad-hoc bluetooth network, transfer encrypted location information, and publish it on a public append-only bulletin board, known as a \textit{blockchain}.
+This project describes a decentralised location proof system that is capable of operating on \textit{mobile nodes} (mobile devices), and is designed such that location proofs are obtained using other untrusted mobile nodes as \textit{alibis}.
+Proofs will be created as two mobile nodes communicate over an ad-hoc bluetooth network, transfer encrypted location information, and then publish it onto a public append-only bulletin board, known as a \textit{blockchain}.
 The decentralised nature of the system means that there is no single point of failure, no entity controlling the security of every node's location proofs, and no entity capable of violating another node's privacy.
-This is because in a decentralised system, no node is ``in charge'', and no node has more authority in the system than any other node.
+This is because in a decentralised system, all nodes have an equal level of authority.
+
+Evaluation of the project is presented using case-based analysis.
+Desirable properties of location proof systems are identified from the state of the art, along with common threats (attacks) in such systems.
+These are known as cases.
+The model described in this project is then evaluated against each case, by means of reasoning.
+Based on analysis of the state of the art, this is standard practice in the evaluation of such systems.
 
@@
 
-\subsection{Conclusion and Future Work}
+\subsection{Conclusion and future work}
 Chapter 5 presents the conclusions of the project, and details interesting areas for possible future work relating to the project.

### 2016-04-23 thesis/thesis.tex
Adding final updates

@@
 \usepackage{subcaption}
+\usepackage{setspace}
 
@@
 \begin{document}
+
+\onehalfspacing
+
 \pagenumbering{roman}
 \maketitle
+
+\renewcommand{\abstractname}{Abstract}
+\begin{abstract}
+Location proof systems are systems which allow a user to undeniably prove its location to another user.
+Existing systems have thus far been designed in a centralised manner, using a trusted central server to provide honest location proofs to users.
+This presents privacy and reliability issues, as these systems rely on the honesty and availability of the central server.
+This report presents the design and evaluation of a decentralised location proof system, which overcomes the shortcomings of existing centralised location proof systems.
+\end{abstract}
+
+\renewcommand{\abstractname}{Acknowledgements}
+\begin{abstract}
+I wish to thank my supervisor Stephen Barrett, for his continuous guidance and enthusiasm throughout this project.
+I would also like to thank Michael Clear for his excellent advice and suggestions, and Douglas Temple for his generous support.
+\end{abstract}
 
